### 2015-06-30 Report/ceec.tex
Added the start of the report

\documentclass{IEEEtran}

\author{Piers R. Williams, \and Joseph Walton-Rivers}

\title{MCTS Applied To Co-operative Problems}

\usepackage{graphicx}
\usepackage{glossaries}

\newacronym{mcts}{MCTS}{Monte-Carlo Tree Search}
\newacronym{uct}{UCT}{Uniform Cost applied to Trees}
\newacronym{ggp}{GGP}{General Game Playing}

\begin{document}
\maketitle
\begin{abstract}
An experiment to see how standard \gls{mcts} handles simple co-operative problems.	These problems are formed from a simple grid world that has a set of goals, doors and buttons as well as walls that cannot be walked through. Two agents have to each reach every goal present on the map. For a door to be open, an Agent must be present on at least one of the buttons that is linked to it.

When laid out correctly, the world requires each agent to do certain things at certain times in order to achieve the goal. With no modification to allow communication between the two Agents - \gls{mcts} performs well and performs very 'purposefully' when given enough computational time.
\end{abstract}

\section{Introduction}
Place decent literature review here covering:
\begin{itemize}
\item{Basic \gls{mcts}}
\item{Basic MAS}
\item{The problem itself}
\end{itemize}

\gls{mcts} has been applied to a wealth of domains and is one of the primary algorithms in use for \gls{ggp}. Primary advantages are that, when given a sufficient forward model, \gls{mcts} doesn't require any knowledge about the game itself in order to play.

Standard \gls{mcts} plays best when it is either able to search to the end of the game tree, or is given rewards frequently. \gls{mcts} tends to stumble when the time given to it isn't sufficient to allow it to locate any sequence of actions that provides a reward.

\section{The Experiment}
The main premise was to put \gls{mcts} in a situation where it would rely on other AI Agents in order to achieve its objectives, as well as provide a code base for further work with communication between Agents. In order to do this, a problem domain was created.
\subsection{The Problem Domain}
The problem domain is a simple grid world consisting of various objects:
\begin{itemize}
\item{\emph{Walls - } Walls are impassable, and are fixed in position. Rendered in Black.}
\item{\emph{Agents - } Agents are the moving objects that can activate buttons and the goal. \emph{Agents} are rendered in dark Yellow}
\item{\emph{Doors - } Doors are impassable, unless a linked \emph{Button} is currently activated. \emph{Doors} are rendered in Blue unless they are open}
\item{\emph{Buttons - } Buttons are passable, and when an \emph{Agent} is on the \emph{Button} it will activate and open the linked \emph{Door}. \emph{Buttons} are rendered in Red}
\item{\emph{Goals - } Goals are passable and reward all \emph{Agents} with a portion of the score. All \emph{Goals} are worth the same amount and the maximum score of $1$ is achieved when every \emph{Agent} has visited every \emph{Goal} at least once. Re-visiting a \emph{Goal} has no effect}
\end{itemize}

The starting positions for a simple problem is shown in Figure \ref{InitialState}
\begin{figure}[ht]
\includegraphics[scale=0.5]{InitialState}
\caption{Simple game state showing the different elements}
\label{InitialState}
\end{figure}

All levels are defined by a simple text file format.

The problems are designed to require Agents to co-operate in order to achieve their goals. Unlike other environments where \gls{mcts} can charge off achieving its own goals, this domain requires the agents to sometimes sit patiently on a button for another Agent to do something else.

\subsection{AI Controllers}
\subsubsection{Random}
The random controller simply chooses one of the possible 5 actions. This is one of the simplest to implement and run.
\subsubsection{Keyboard}
The keyboard controller takes input from the keyboard and translates that into a single Action. Once an action is polled, it is reset to the No Op action unless the keyboard is used again. 
\subsubsection{\gls{mcts}}
The \gls{mcts} controller is a simple implementation of \gls{uct} - with a fixed iteration, \gls{uct} Border and rollout border. No knowledge about the game is provided and the assumption is made that the other player will play randomly. The fixed rollout border makes a significant improvement in iterations per decision (On the machine from 1-3 to 500-600 in 40ms). This greatly improves the ability of \gls{mcts} to make informed decisions. The score at the end of a rollout is taken from the game state - so if \gls{mcts} doesn't see any player reach a goal, all branches will be equal.
\subsubsection{A Star}
An intelligent agent was required that could provide comparison to how the MCTS is performing. A Star was selected and written to view the problem as selecting the shortest path of actions that would result in reaching the goals.

\subsection{Methodology}
Initially, observations were made to see how \gls{mcts} handled the problem. At first, with a short computational budget it seemed like \gls{mcts} would perform poorly, with near random movement seeming to emerge.

This changed, when an agent (Agent 1 say) got near a \emph{Button} or \emph{Door}. When Agent 1 reached an item like this - Agent 2 would seemingly gain some purpose and typically head for the other items. When Agent 1 got on the \emph{Button}, Agent 2 would head straight through the open \emph{Door} and to the \emph{Goal}. Behaviour would then typically go back towards a more random approach, unless the Agent 1 got near the \emph{Door} - typically causing Agent 2 to head more purposefully towards the \emph{Button} that would allow Agent 1 to reach the \emph{Goal}.

With this observation made - the computational budget was increased ten-fold, and the \gls{mcts} agents performed significantly better. Typical behaviour would be near optimal with significantly less random sections of movement. This can likely be attributed to the increased rollout and uct border depths allowing more foresight on such a small puzzle.

\end{document}

### 2015-07-01 src/FastGame/RoundRobinMT.java
up the repeats and print the number of tasks

@@ -16,7 +16,7 @@ import java.util.concurrent.*;
  * Created by jwalto on 01/07/2015.
  */
 public class RoundRobinMT {
-    private final static Integer REPEATS = 5;
+    private final static Integer REPEATS = 10;
     private final static Integer MAX_TICKS = 2000;
 
     public static void main(String[] args) throws FileNotFoundException, InterruptedException, ExecutionException {
@@ -57,7 +57,7 @@ public class RoundRobinMT {
             }
         }
 
-        System.out.println("calculating results");
+        System.out.println("calculating results ("+tasks.size()+" tasks)");
         List<Future<Result>> results = service.invokeAll(tasks);
 
         System.out.println("Processing results");

### 2015-07-01 src/Controllers/VariGA/VariGA.java
Work on new GA + ignore for this project altered

@@ -1,0 +1,72 @@
+package Controllers.VariGA;
+
+import Controllers.Controller;
+import FastGame.Action;
+
+import java.util.Random;
+
+/**
+ * Created by Piers on 01/07/2015.
+ */
+public class VariGA extends Controller {
+
+
+}
+
+class ActionSequence {
+    private static Random random = new Random();
+    int numberOfActions;
+    // length of each action
+    int[] lengths;
+    // Indicies of Action.allActions
+    int[] actions;
+
+    int minLength;
+    int maxLength;
+    int minNum;
+    int maxNum;
+
+    // New random sequence
+    public ActionSequence(int minNum, int maxNum, int minLength, int maxLength) {
+        this.minLength = minLength;
+        this.maxLength = maxLength;
+        this.minNum = minNum;
+        this.maxNum = maxNum;
+
+        randomize();
+    }
+
+    private void randomize() {
+        numberOfActions = random.nextInt(maxNum - minNum) + minNum;
+        lengths = new int[numberOfActions];
+        actions = new int[numberOfActions];
+
+        for (int i = 0; i < numberOfActions; i++) {
+            lengths[i] = random.nextInt(maxLength - minLength) + minLength;
+            actions = new int[random.nextInt(Action.allActions.length)];
+        }
+    }
+
+    /**
+     * Mutate the item as gently as you like
+     *
+     * @param numChance    - Chance that the number of action pieces will be increased or decreased by 1 within the limits
+     * @param lengthChance - Chance that the individual length of each parameter will be increased or decreased by 1 within the limits
+     * @param actionChance - Chance that the individual action of each parameter will be randomly changed
+     */
+    private void mutate(double numChance, double lengthChance, double actionChance) {
+        double test = random.nextDouble();
+        if (test > numChance) {
+            if(numberOfActions == maxLength){
+                // shrink
+            }else if (numberOfActions == minLength){
+                // grow
+            }else{
+                // grow or shrink
+            }
+        }
+    }
+
+
+
+}

### 2015-07-02 src/Controllers/VariGA/VariGA.java
Implemented cloning of GA

@@ -28,6 +28,11 @@ public class VariGA extends Controller {
         this.iterations = iterations;
     }
 
+    public VariGA getClone(){
+        VariGA other = new VariGA(this.first, this.iterations);
+        return other;
+    }
+
     @Override
     public Action get(CoopGame game) {
         if (currentBest == null || currentUsage >= currentBest.getTotalLength()) {

### 2015-07-02 src/Controllers/ga/GAController.java
round robin and mt use clones to avoid issues

@@ -38,9 +38,8 @@ public class GAController extends Controller {
             nextAction = currentAction;
             reset = true;
             macroPos = GAConstants.MACRO_ACTION_LENGTH-1;
-            startOfGame = false; //TODO need to reliably detect the start of the next game
+            startOfGame = false;
         } else {
-            //TODO handle start of game
             if (macroPos > 0) {
                 if (reset) {
                     ga.init(game, first);
@@ -57,7 +56,7 @@ public class GAController extends Controller {
                 if (currentAction != null) {
                     macroPos = GAConstants.MACRO_ACTION_LENGTH - 1;
                 }
-
+                reset = true;
             }
         }
 

### 2015-07-02 src/FastGame/RoundRobin.java

@@ -59,8 +59,11 @@ public class RoundRobin {
         }
     }
 
-    private static Result runTrial(Controller p1, Controller p2, String map, int tid) {
+    private static Result runTrial(Controller player1, Controller player2, String map, int tid) {
         CoopGame game = new CoopGame(map);
+
+        Controller p1 = player1.getClone();
+        Controller p2 = player2.getClone();
 
         int ticksTaken = 0;
         while (ticksTaken < MAX_TICKS && !game.hasWon()) {

### 2015-07-02 src/FastGame/RoundRobinMT.java

@@ -76,8 +76,8 @@ public class RoundRobinMT {
         int trialID;
 
         Matchup(Controller p1, Controller p2, String map, int trialID) {
-            this.p1 = p1;
-            this.p2 = p2;
+            this.p1 = p1.getClone();
+            this.p2 = p2.getClone();
             this.map = map;
             this.trialID = trialID;
             count++;
@@ -85,26 +85,38 @@ public class RoundRobinMT {
 
         @Override
         public Result call() throws Exception {
-            System.out.println("Running game");
-            CoopGame game = new CoopGame(map);
+            try {
+                CoopGame game = new CoopGame(map);
 
-            int ticksTaken = 0;
-            while (ticksTaken < MAX_TICKS && !game.hasWon()) {
-                game.update(p1.get(game.getClone()), p2.get(game.getClone()));
-                ticksTaken++;
+                int ticksTaken = 0;
+                while (ticksTaken < MAX_TICKS && !game.hasWon()) {
+                    game.update(p1.get(game.getClone()), p2.get(game.getClone()));
+                    ticksTaken++;
+                }
+
+                Result r = new Result();
+                r.p1 = p1;
+                r.p2 = p2;
+                r.map = map;
+                r.trialID = trialID;
+                r.score = game.getScore();
+                r.timeTaken = ticksTaken;
+
+                count--;
+                System.out.println("game complete (" + count + " left)");
+                return r;
+            } catch (Exception ex) {
+                System.err.println("Error: "+ex);
+                count--;
+                Result r = new Result();
+                r.p1 = p1;
+                r.p2 = p2;
+                r.map = map;
+                r.trialID = trialID;
+                r.score = -1;
+                r.timeTaken = -1;
+                return r;
             }
-
-            Result r = new Result();
-            r.p1 = p1;
-            r.p2 = p2;
-            r.map = map;
-            r.trialID = trialID;
-            r.score = game.getScore();
-            r.timeTaken = ticksTaken;
-
-            count--;
-            System.out.println("game complete ("+count+" left)");
-            return r;
         }
     }
 

### 2015-07-02 src/Controllers/ga/GAController.java
Ga controller clone method

@@ -30,6 +30,12 @@ public class GAController extends Controller {
     }
 
     @Override
+    public Controller getClone() {
+        GAController other = new GAController(first);
+        return other;
+    }
+
+    @Override
     public Action get(CoopGame game) {
         MacroAction nextAction = NOOP;
 

### 2015-07-02 Report/ceec.tex
Work on the reports
Work on things

@@
 
-\title{MCTS Applied To Co-operative Problems}
+\title{MCTS Applied to Co-operative Problems}
 
@@
 \newacronym{ggp}{GGP}{General Game Playing}
+\newacronym{ga}{GA}{Genetic Algorithm}
 
@@
 The score at the end of a rollout is taken from the game state - so if \gls{mcts} doesn't see any player reach a goal, all branches will be equal.
-\subsubsection{A Star}
+\subsubsection{A*}
 An intelligent agent was required that could provide comparison to how the MCTS is performing.
 A Star was selected and written to view the problem as selecting the shortest path of actions that would result in reaching the goals.
+\subsubsection{Macro Action Genetic Algorithm}
+The \gls{ga} algorithm was selected for its simplicity and had Macro Actions added in order to improve the forward search capability.
+\subsubsection{Variable Macro Action Genetic Algorithm}
 

### 2015-07-02 src/Controllers/VariGA/VariGA.java

@@ -59,7 +59,7 @@ public class VariGA extends Controller {
     private void calculate(CoopGame game) {
 //        System.out.println("Gets here");
         if (parent == null) {
-            parent = new ActionSequence(3, 6, 1, 5);
+            parent = new ActionSequence(5, 10, 1, 5);
             parentFitness = parent.evaluate(fastForwardedGame.getClone(), first);
         }
         for (int i = 0; i < iterations; i++) {

### 2015-07-02 src/FastGame/FastGameMain.java

@@ -1,10 +1,7 @@
 package FastGame;
 
-import Controllers.ArrowController;
-import Controllers.Controller;
-import Controllers.MCTS;
+import Controllers.*;
 import Controllers.VariGA.VariGA;
-import Controllers.WASDController;
 import Controllers.ga.GAController;
 
 import javax.swing.*;
@@ -22,17 +19,17 @@ public class FastGameMain {
         ArrowController arrows = new ArrowController();
 
 //        Controller c1 = new GAController(true);
-        Controller c1 = new MCTS(true, 500);
-//        Controller c1 = new RandomController();
+//        Controller c1 = new VariGA(true, 500);
+        Controller c1 = new RandomController();
 //        Controller c1 = wasd;
-//        Controller c2 = new AStar(false);
+        Controller c2 = new AStar(false);
 //        Controller c2 = new GAController(false);
-        Controller c2 = new VariGA(false, 20);
+//        Controller c2 = new VariGA(false, 500);
 
 //        Controller c2 = new RandomController();
 //        Controller c2 = arrows;
 
-        CoopGame game = new CoopGame("data/maps/level1.txt");
+        CoopGame game = new CoopGame("data/maps/level1E.txt");
 
         Viewer viewer = new Viewer(game);
         viewer.addKeyListener(wasd);

### 2015-07-02 Report/ceec.tex
Fixed MCTS

@@
 \newacronym{ga}{GA}{Genetic Algorithm}
+\newacronym{mas}{MAS}{Multi-Agent Systems}
 
@@
 \begin{abstract}
-An experiment to see how standard \gls{mcts} handles simple co-operative problems.	These problems are formed from a simple grid world that has a set of goals, doors and buttons as well as walls that cannot be walked through.
+This paper highlights an experiment to see how standard \gls{mcts} handles simple co-operative problems.	These problems are formed from a simple grid world that has a set of goals, doors and buttons as well as walls that cannot be walked through.
 Two agents have to each reach every goal present on the map.
@@
 \section{Introduction}
-Place decent literature review here covering:
-\begin{itemize}
-\item{Basic \gls{mcts}}
-\item{Basic MAS}
-\item{The problem itself}
-\end{itemize}
 
-\gls{mcts} has been applied to a wealth of domains and is one of the primary algorithms in use for \gls{ggp}.
+\gls{mcts} has been applied to a wealth of domains and is one of the primary algorithms in use for \gls{ggp}\cite{finnsson2008simulation}.
 Primary advantages are that, when given a sufficient forward model, \gls{mcts} doesn't require any knowledge about the game itself in order to play.
@@
 Standard \gls{mcts} plays best when it is either able to search to the end of the game tree, or is given rewards frequently.
-\gls{mcts} tends to stumble when the time given to it isn't sufficient to allow it to locate any sequence of actions that provides a reward.
+\gls{mcts} tends to stumble when the time given to it isn't sufficient to allow it to locate any sequence of actions that provides a reward in order to differentiate the root's children.
 
+Traditional \gls{mas} would be the logical choice for solving this type of problem, however they were left out in order to work towards a co-operative \gls{ggp} agent.
+
+Creating \gls{ggp} agents that can co-operate with other players would open the door for more flexible agents in games that can work together with human players. 
 \section{The Experiment}
@@
 \begin{itemize}
-\item{\emph{Walls - } Walls are impassable, and are fixed in position. Rendered in Black.}
-\item{\emph{Agents - } Agents are the moving objects that can activate buttons and the goal. \emph{Agents} are rendered in dark Yellow}
-\item{\emph{Doors - } Doors are impassable, unless a linked \emph{Button} is currently activated. \emph{Doors} are rendered in Blue unless they are open}
-\item{\emph{Buttons - } Buttons are passable, and when an \emph{Agent} is on the \emph{Button} it will activate and open the linked \emph{Door}. \emph{Buttons} are rendered in Red}
-\item{\emph{Goals - } Goals are passable and reward all \emph{Agents} with a portion of the score.
+\item{\emph{Walls -} Walls are impassable, and are fixed in position. \emph{Doors} are rendered in Black.}
+\item{\emph{Agents -} Agents are the moving objects that can activate buttons and the goal. \emph{Agents} are rendered in dark Yellow}
+\item{\emph{Doors -} Doors are impassable, unless a linked \emph{Button} is currently activated. \emph{Doors} are rendered in Blue unless they are open}
+\item{\emph{Buttons -} Buttons are passable, and when an \emph{Agent} is on the \emph{Button} it will activate and open the linked \emph{Door}. \emph{Buttons} are rendered in Red}
+\item{\emph{Goals -} Goals are passable and reward all \emph{Agents} with a portion of the score.
 All \emph{Goals} are worth the same amount and the maximum score of $1$ is achieved when every \emph{Agent} has visited every \emph{Goal} at least once.
-Re-visiting a \emph{Goal} has no effect}
+Re-visiting a \emph{Goal} has no effect.
+\emph{Goals} are rendered in Yellow}
 \end{itemize}
@@
 Initially, observations were made to see how \gls{mcts} handled the problem.
-At first, with a short computational budget it seemed like \gls{mcts} would perform poorly, with near random movement seeming to emerge.
+At first, with a small computational budget it seemed like \gls{mcts} would perform poorly, with near random movement seeming to emerge.
 
@@
 This can likely be attributed to the increased rollout and uct border depths allowing more foresight on such a small puzzle.
+\bibliographystyle{IEEEtran}
+\bibliography{ceec}
 

### 2015-07-02 src/Controllers/MCTS.java

@@ -11,13 +11,20 @@ import java.util.Random;
 public class MCTS extends Controller {
 
     protected Random random = new Random();
-    private int maxUCTDepth = 3;
-    private int maxRolloutDepth = 20;
+    private int maxUCTDepth = 5;
+    private int maxRolloutDepth = 30;
     private int iterationLimit = 0;
 
     private boolean first;
 
-    public MCTS(boolean first, int iterationLimit) {
+    public MCTS(boolean first, int iterationLimit, int maxUCTDepth, int maxRolloutDepth) {
+        this.first = first;
+        this.iterationLimit = iterationLimit;
+        this.maxUCTDepth = maxUCTDepth;
+        this.maxRolloutDepth = maxRolloutDepth;
+    }
+
+    public MCTS(boolean first, int iterationLimit){
         this.first = first;
         this.iterationLimit = iterationLimit;
     }

### 2015-07-02 src/FastGame/FastGameMain.java

@@ -19,17 +19,17 @@ public class FastGameMain {
         ArrowController arrows = new ArrowController();
 
 //        Controller c1 = new GAController(true);
-//        Controller c1 = new VariGA(true, 500);
-        Controller c1 = new RandomController();
+        Controller c1 = new MCTS(true, 500);
+//        Controller c1 = new RandomController();
 //        Controller c1 = wasd;
-        Controller c2 = new AStar(false);
+//        Controller c2 = new AStar(false);
 //        Controller c2 = new GAController(false);
-//        Controller c2 = new VariGA(false, 500);
+        Controller c2 = new MCTS(false, 500);
 
 //        Controller c2 = new RandomController();
 //        Controller c2 = arrows;
 
-        CoopGame game = new CoopGame("data/maps/level1E.txt");
+        CoopGame game = new CoopGame("data/maps/level3.txt");
 
         Viewer viewer = new Viewer(game);
         viewer.addKeyListener(wasd);

### 2015-07-02 Report/ceec.tex

@@
 \subsection{AI Controllers}
+A small set of AI Controllers were created in order to attempt to solve the problem domain. None of the agents have the ability to communicate with another agent.
 \subsubsection{Random}
@@
 
-\subsection{Methodology}
+\subsection{Initial Testing}
 Initially, observations were made to see how \gls{mcts} handled the problem.
@@
 This can likely be attributed to the increased rollout and uct border depths allowing more foresight on such a small puzzle.
+\subsection{Tournament}
+A round robin tournament with three maps and the assembled Agents with various parameters was run - allowing each Agent to be paired with every other Agent (including itself) and play the game ten times per level.
 \bibliographystyle{IEEEtran}

### 2015-07-02 src/FastGame/RoundRobinMT.java
round robin enable AIs

@@ -41,12 +41,12 @@ public class RoundRobinMT {
 
         Controller[] player2List = new Controller[] {
                 new MCTS(false, 500, 5, 30),
-               // new MCTS(false, 200),
-               // new GAController(false),
+                new MCTS(false, 200),
+                new GAController(false),
                 //new AStar(false),
-              //  new VariGA(false, 500),
+                new VariGA(false, 500),
               //  new VariGA(false, 200)
-               //new RandomController()
+                new RandomController()
         };
 
         while(!Thread.interrupted()) {

### 2015-07-02 src/FastGame/RoundRobinMT.java
round robin changes

@@ -17,7 +17,7 @@ import java.util.concurrent.*;
  * Created by jwalto on 01/07/2015.
  */
 public class RoundRobinMT {
-    private final static Integer REPEATS = 1;
+    private final static Integer REPEATS = 3;
     private final static Integer MAX_TICKS = 2000;
 
     public static void main(String[] args) throws FileNotFoundException, InterruptedException, ExecutionException {

### 2015-07-02 src/Controllers/VariGA/VariGA.java
Change to fastgame

@@ -14,9 +14,9 @@ public class VariGA extends Controller {
 
     boolean first;
     private int iterations;
-    private double numChance = 0.1;
-    private double lengthChance = 0.3;
-    private double actionChance = 0.1;
+    private double numChance = 0.25;
+    private double lengthChance = 0.8;
+    private double actionChance = 0.75;
     private ActionSequence currentBest;
     private int currentUsage = 0;
     private ActionSequence parent = getNewParent();
@@ -32,19 +32,19 @@ public class VariGA extends Controller {
         VariGA other = new VariGA(this.first, this.iterations);
         return other;
     }
-
+    // int minNum, int maxNum, int minLength, int maxLength
     private ActionSequence getNewParent(){
-        return new ActionSequence(5, 10, 1, 5);
+        return new ActionSequence(3, 10, 1, 5);
     }
 
     @Override
     public Action get(CoopGame game) {
-        if (currentBest == null || currentUsage >= currentBest.getTotalLength()) {
+        if (currentBest == null || currentUsage >= currentBest.getFirstActionLength()) {
             currentBest = parent;
             parent = null;
             // Fast forward the fast forward to the right place
             fastForwardedGame = game.getClone();
-            for(int i = 0 ;!fastForwardedGame.hasWon() &&  i < currentBest.getTotalLength(); i++){
+            for(int i = 0 ;!fastForwardedGame.hasWon() &&  i < currentBest.getFirstActionLength(); i++){
                 if(first){
                     fastForwardedGame.update(currentBest.getActionAt(i), Action.getRandom());
                 }else{
@@ -71,7 +71,7 @@ public class VariGA extends Controller {
             ActionSequence child = parent.getClone();
             child.mutate(numChance, lengthChance, actionChance);
             double childFitness = child.evaluate(fastForwardedGame.getClone(), first);
-            if (childFitness > parentFitness) {
+            if (childFitness > parentFitness || (childFitness == parentFitness && Math.random() > 0.75)) {
                 parent = child;
                 parentFitness = childFitness;
             }
@@ -148,15 +148,21 @@ class ActionSequence {
     }
 
     public double evaluate(CoopGame state, boolean first) {
+        int totalScore = 0;
         int totalLength = getTotalLength();
-        for (int i = 0; !state.hasWon() && i < totalLength; i++) {
-            if (first) {
-                state.update(getActionAt(i), Action.getRandom());
-            } else {
-                state.update(Action.getRandom(), getActionAt(i));
+
[…]

### 2015-07-02 src/FastGame/FastGameMain.java

@@ -19,17 +19,18 @@ public class FastGameMain {
         ArrowController arrows = new ArrowController();
 
 //        Controller c1 = new GAController(true);
-        Controller c1 = new MCTS(true, 500);
-//        Controller c1 = new RandomController();
+//        Controller c1 = new MCTS(true, 1000, 10, 45);
+//        Controller c1 = new VariGA(true, 2000);
+        Controller c1 = new RandomController();
 //        Controller c1 = wasd;
 //        Controller c2 = new AStar(false);
 //        Controller c2 = new GAController(false);
-        Controller c2 = new MCTS(false, 500);
-
-//        Controller c2 = new RandomController();
+//        Controller c2 = new MCTS(false, 1000, 10, 45);
+//            Controller c2 = new VariGA(false, 2000);
+        Controller c2 = new RandomController();
 //        Controller c2 = arrows;
 
-        CoopGame game = new CoopGame("data/maps/level3.txt");
+        CoopGame game = new CoopGame("data/maps/level6.txt");
 
         Viewer viewer = new Viewer(game);
         viewer.addKeyListener(wasd);
@@ -41,10 +42,13 @@ public class FastGameMain {
         frame.pack();
         frame.setVisible(true);
 
+        int ticks = 0;
         while (!game.hasWon()) {
             game.update(c1.get(game.getClone()), c2.get(game.getClone()));
+            ticks++;
 //            Thread.sleep(40);
             viewer.repaint();
         }
+        System.out.println(ticks);
     }
 }

### 2015-07-02 src/FastGame/RoundRobinMT.java
setup RR

@@ -27,25 +27,28 @@ public class RoundRobinMT {
         String[] maps = {
                 "data/maps/level1.txt",
                 "data/maps/level2.txt",
-                "data/maps/level3.txt"
+                "data/maps/level3.txt",
+                "data/maps/level4.txt",
+                "data/maps/level5.txt",
+                "data/maps/level6.txt",
+                "data/maps/level1E.txt"
         };
 
         Controller[] player1List = new Controller[]{
-                new MCTS(true, 500, 5, 30),
+                new MCTS(true, 500, 10, 45),
+                new MCTS(true, 75, 3, 15),
                 new MCTS(true, 200),
+                new VariGA(true, 500),
                 new GAController(true),
-                //new AStar(true),
-                new RandomController(),
-                new VariGA(true, 500)
+                new RandomController()
         };
 
         Controller[] player2List = new Controller[] {
-                new MCTS(false, 500, 5, 30),
+                new MCTS(false, 500, 10, 45),
+                new MCTS(false, 75, 3, 15),
                 new MCTS(false, 200),
-                new GAController(false),
-                //new AStar(false),
                 new VariGA(false, 500),
-              //  new VariGA(false, 200)
+                new GAController(true),
                 new RandomController()
         };
 

### 2015-07-03 Report/ceec.tex
Literature review expanded

--- 2015-07-02 Report/ceec.tex
@@
 \newacronym{mas}{MAS}{Multi-Agent Systems}
+\newacronym{maga}{MAGA}{Macro Action Genetic Algorithm}
+\newacronym{ai}{AI}{Artificial Intelligence}
 
@@
 \begin{abstract}
-This paper highlights an experiment to see how standard \gls{mcts} handles simple co-operative problems.	These problems are formed from a simple grid world that has a set of goals, doors and buttons as well as walls that cannot be walked through.
+This paper highlights an experiment to see how standard \gls{mcts} handles simple co-operative problems with no prior or provided knowledge.	These problems are formed from a simple grid world that has a set of goals, doors and buttons as well as walls that cannot be walked through.
 Two agents have to each reach every goal present on the map.
@@
 \section{Introduction}
+\gls{ggp} is the field of writing \gls{ai} agents that can play a multitude of games without being written specifically for each one individually.
+\gls{ggp} in real time video games is a popular competition \cite{perez2014}
 
-\gls{mcts} has been applied to a wealth of domains and is one of the primary algorithms in use for \gls{ggp}\cite{finnsson2008simulation}.
+Creating \gls{ggp} agents that can co-operate with other players would open the door for more flexible agents in games that can work together with human players.
+This experiment tests how well current techniques can cope without specifically co-operating with each other.
+Agents that communicate slowly using a form of Natural Language, should in theory be able to work with human players equally well as they do with other Agents.
+
+\gls{mcts} \cite{browne2012survey} has been applied to a wealth of domains and is one of the primary algorithms in use for \gls{ggp}\cite{finnsson2008simulation}.
 Primary advantages are that, when given a sufficient forward model, \gls{mcts} doesn't require any knowledge about the game itself in order to play.
@@
 Standard \gls{mcts} plays best when it is either able to search to the end of the game tree, or is given rewards frequently.
-\gls{mcts} tends to stumble when the time given to it isn't sufficient to allow it to locate any sequence of actions that provides a reward in order to differentiate the root's children.
+\gls{mcts} tends to stumble when the time given to it isn't sufficient to allow it to locate any sequence of actions that provides a reward in order to differentiate the root's children \cite{perez2012monte}.
 
-Traditional \gls{mas} would be the logical choice for solving this type of problem, however they were left out in order to work towards a co-operative \gls{ggp} agent.
-
-Creating \gls{ggp} agents that can co-operate with other players would open the door for more flexible agents in games that can work together with human players. 
 \section{The Experiment}
@@
 \begin{figure}[ht]
+\centering
 \includegraphics[scale=0.5]{InitialState}
-\caption{Simple game state showing the different elements}
+\caption{Simple game state showing the different elements\protect\footnotemark }
 \label{InitialState}
@@
 
+\footnotetext{Displayed numbers are the ID numbers - \emph{Button} ID 0 will open \emph{Door} ID 0 but not \emph{Door} ID 1}
 All levels are defined by a simple text file format.
@@
 
-\subsection{AI Controllers}
-\subsubsection{Random}
-The random controller simply chooses one of the possible 5 actions. This is one of the simplest to implement and run.
-\subsubsection{Keyboard}
-The keyboard controller takes input from the keyboard and translates that into a single Action. Once an action is polled, it is reset to the No Op action unless the keyboard is used again. 
-\subsubsection{\gls{mcts}}
-The \gls{mcts} controller is a simple implementation of \gls{uct} - with a fixed iteration, \gls{uct} Border and rollout border.
-No knowledge about the game is provided and the assumption is made that the other player will play randomly.
-The fixed rollout border makes a significant improvement in iterations per decision (On the machine from 1-3 to 500-600 in 40ms).
-This greatly improves the ability of \gls{mcts} to make informed decisions.
-The score at the end of a rollout is taken from the game state - so if \gls{mcts} doesn't see any player reach a goal, all branches will be equal.
-\subsubsection{A*}
-An intelligent agent was required that could provide comparison to how the MCTS is performing.
-A Star was selected and written to view the problem as selecting the shortest path of actions that would result in reaching the goals.
-\subsubsection{Macro Action Genetic Algorithm}
-The \gls{ga} algorithm was selected for its simplicity and had Macro Actions added in order to improve the forward search capability.
-\subsubsection{Variable Macro Action Genetic Algorithm}
-
-\subsection{Methodology}
+\subsection{Initial Testing}
 Initially, observations were made to see how \gls{mcts} handled the problem.
@@
 This can likely be attributed to the increased rollout and uct border depths allowing more foresight on such a small puzzle.
+\subsection{Tournament}
+For the main data collection, we ran a round robin tournament of maps and Agents.
+
+The 7 maps that were included in the tournament were as follows:
+\begin{itemize}
+\item{\emph{level1.txt} This map is the same as the map in \ref{InitialState}}
+\item{\emph{level1E.txt} This map is the same as level1.txt but without the \emph{Doors} and \emph{Buttons}. This was to test the \emph{Agent's} ability to solve the simplest problem.}
+\item{\emph{level2.txt} This map was a modification of the level1.txt - making the map more symmetric and the action parts closer together.}
+\item{\emph{level3.txt} This map was an extension of level1.txt with a second \emph{Goal} and some extra walls in the game.
+Spreading the action parts away from the door and buttons was the main purpose of this one}
+\item{\emph{level4.txt} This map was a modification of level1.txt - putting a second \emph{Goal} in and making the map partly mirrored.
+Each \emph{Agent} began in a separate room to each other instead of together.}
+\item{\emph{level5.txt} This map was a new map, designed to give wildly different roles to each AI - the top Agent would have to travel through two doors that the bottom agent had access to the linked \emph{Buttons}.
+Then the top \emph{Agent} could collect the reward and allow the bottom \emph{Agent} access to the \emph{Goal}.}
+\item{\emph{level6.txt} This map was a new map - with two rooms each with a \emph{Goal} and a door.This was designed to force each \emph{Agent} to be let into the \emph{Goal} room, and out of it again.}
+\end{itemize}
+
+\subsubsection{\gls{ai} Controllers}
+A small set of \gls{ai} Controllers were created in order to attempt to solve the problem domain. None of the agents have the ability to communicate with another agent.
+\subsubsection*{Random}
+The random controller simply chooses one of the possible 5 actions. This is one of the simplest to implement and run.
+\subsubsection*{Keyboard}
+The keyboard controller takes input from the keyboard and translates that into a single Action. Once an action is polled, it is reset to the No Op action unless the keyboard is used again. 
+\subsubsection*{\gls{mcts}}
+The \gls{mcts} controller is a simple implementation of \gls{uct} - with a fixed iteration, \gls{uct} Border and rollout border.
+No knowledge about the game is provided and the assumption is made that the other player will play randomly.
+The fixed rollout border makes a significant improvement in iterations per decision (On the machine from 1-3 to 500-600 in 40ms).
+This greatly improves the ability of \gls{mcts} to make informed decisions.
+The score at the end of a rollout is taken from the game state - so if \gls{mcts} doesn't see any player reach a goal, all branches will be equal.
+
+For the tournament, three parameter sets were chosen for comparison and are shown in Figure \ref{mctsTable}.
+\begin{figure}[h]
+\centering
+\begin{tabular}{| l | c | c | c |}
+\hline
+\textbf{Budget} & \textbf{Iterations} & \textbf{Max UCT} & \textbf{Max Rollout} \\
+\hline
+Small & 75 & 3 & 15 \\
+Medium & 200 & 5 & 30 \\
+High & 500 & 10 & 45 \\
+\hline
+\end{tabular}
+\caption{Table of parameters for the 3 \gls{mcts} players}
+\label{mctsTable}
+\end{figure}
+
+\subsubsection*{Macro Action Genetic Algorithm}
+The \gls{ga} algorithm was selected for its simplicity and had Macro Actions added in order to improve the forward search capability.
+The \gls{maga} used a population size of 10 and tournament selection of 3.
+Each candidate was a string of 15 actions - with each action performed 3 times in a row.
+This meant the \gls{maga} could "see" 45 ticks in the future.
+\subsubsection*{Variable Macro Action Genetic Algorithm}
+The Variable Macro Action \gls{ga} was created to try to solve the shortcomings of \gls{maga}.
+The primary premise was to allow the \gls{ga} to evolve the individual macro action lengths and the length of the overall sequence (number of macro actions).
+The main technique used was a 1 + 1 ES.
+The algorithm was bounded by a number of parameters that are shown in Figure \ref{vmagaTable}.
+
+\begin{figure}[h]
+\centering
+\begin{tabular}{| l | l | l |}
+\hline
+\textbf{Param} & \textbf{Controls} & \textbf{Value} \\
+\hline
+minNum & Number of Macro Actions & 3 \\
+MaxNum & Number of Macro Actions & 10 \\
+minLength & Length of Macro Actions & 1 \\
+maxLength & Length of Macro Actions & 5 \\
+numChance & Chance of altering Number & 0.25 \\
+lengthChance & Chance of altering each length & 0.8 \\
+actionChance & Chance of altering each action & 0.75 \\
+\hline
+\end{tabular}
+\caption{Table of paramters for the Variable Macro Action Genetic Algorithm}
+\label{vmagaTable}
+\end{figure}
+These values need extensive tuning to realise the full potential of the algorithm and is a source of possible future work.
+
 \bibliographystyle{IEEEtran}

### 2015-07-03 src/FastGame/FastGameMain.java

@@ -27,16 +27,16 @@ public class FastGameMain {
 
 //        Controller c1 = new VariGA(true, 500);
         //Controller c1 = new RandomController();
-          Controller c1 = new NoOp();
+//          Controller c1 = new NoOp();
 
-//        Controller c1 = wasd;
+        Controller c1 = wasd;
 //        Controller c2 = new GAController(false);
 //        Controller c2 = new MCTS(false, 1000, 10, 45);
 //            Controller c2 = new VariGA(false, 2000);
-        Controller c2 = new RandomController();
-//        Controller c2 = arrows;
+//        Controller c2 = new RandomController();
+        Controller c2 = arrows;
 
-        CoopGame game = new CoopGame("data/maps/level6.txt");
+        CoopGame game = new CoopGame("data/maps/level1.txt");
 
         Viewer viewer = new Viewer(game);
         viewer.addKeyListener(wasd);

### 2015-07-03 src/FastGame/RoundRobinMT.java
single run per set

@@ -17,7 +17,7 @@ import java.util.concurrent.*;
  * Created by jwalto on 01/07/2015.
  */
 public class RoundRobinMT {
-    private final static Integer REPEATS = 3;
+    private final static Integer REPEATS = 1;
     private final static Integer MAX_TICKS = 2000;
 
     public static void main(String[] args) throws FileNotFoundException, InterruptedException, ExecutionException {
@@ -151,7 +151,7 @@ public class RoundRobinMT {
         }
 
         public String toString() {
-            return String.format("%s and %s (%d ticks, %f score)", p1.getSimpleName(), p2.getSimpleName(), timeTaken, score);
+            return String.format("%s and %s on %s (%d ticks, %f score)", p1.getSimpleName(), p2.getSimpleName(), map, timeTaken, score);
         }
     }
 }

### 2015-07-03 Report/ceec.tex
Much work

@@
 
+\subsubsection{Maps}
 The 7 maps that were included in the tournament were as follows:
@@
 A small set of \gls{ai} Controllers were created in order to attempt to solve the problem domain. None of the agents have the ability to communicate with another agent.
-\subsubsection*{Random}
+\paragraph{Random}
 The random controller simply chooses one of the possible 5 actions. This is one of the simplest to implement and run.
-\subsubsection*{Keyboard}
+\paragraph{Keyboard}
 The keyboard controller takes input from the keyboard and translates that into a single Action. Once an action is polled, it is reset to the No Op action unless the keyboard is used again. 
-\subsubsection*{\gls{mcts}}
+\paragraph{\gls{mcts}}
 The \gls{mcts} controller is a simple implementation of \gls{uct} - with a fixed iteration, \gls{uct} Border and rollout border.
@@
 
-\subsubsection*{Macro Action Genetic Algorithm}
+\paragraph{Macro Action Genetic Algorithm}
 The \gls{ga} algorithm was selected for its simplicity and had Macro Actions added in order to improve the forward search capability.
@@
 This meant the \gls{maga} could "see" 45 ticks in the future.
-\subsubsection*{Variable Macro Action Genetic Algorithm}
+\paragraph{Variable Macro Action Genetic Algorithm}
 The Variable Macro Action \gls{ga} was created to try to solve the shortcomings of \gls{maga}.
@@
 \end{tabular}
-\caption{Table of paramters for the Variable Macro Action Genetic Algorithm}
+\caption{Table of parameters for the Variable Macro Action Genetic Algorithm}
 \label{vmagaTable}
@@
 These values need extensive tuning to realise the full potential of the algorithm and is a source of possible future work.
+\pagebreak
+\section{Results}
 
+\begin{figure}[ht]
+\centering
+\includegraphics[width=\linewidth]{level1vsleve1e}
+\caption{Graph showing the average score obtained by each Agent across level 1(Blue) and level 1E (Orange)}
+\label{1v1eS}
+\end{figure}
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=\linewidth]{level1vsleve1eTicks}
+\caption{Graph showing the average ticks taken for each AI Agent across level 1(Blue) and level 1E (Orange)}
+\label{1v1eT}
+\end{figure}
+
+Figure \ref{1v1eS} shows the effect that having the complex \emph{Buttons} and \emph{Doors} in a level has on the score an Agent achieves.
+Figure \ref{1v1eT} demonstrates the vast improvement in pathfinding ability to a goal in the VariGA compared to the GAController.
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=\linewidth]{avgScoreOverAllMaps}
+\caption{Average score of each AI Agent over all the Maps}
+\label{avgScoreAllMaps}
+\end{figure}
+
+Figure \ref{avgScoreAllMaps} shows the average score that each AI Agent achieved over all the maps.
+The two more powerful \gls{mcts} Agents performed the best, doing much better than the competition.
+Figure \ref{avgTicksAllMaps} shows a similar result, with the more powerful Agents typically completing the maps in fewer ticks.
+\emph{RandomController} is the only deviant here - it outperformed the GA's in score but was worse in average ticks.
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=\linewidth]{avgTicksOverAllMaps}
+\caption{Average Ticks taken for each AI Agent over all the Maps}
+\label{avgTicksAllMaps}
+\end{figure}
+
+\pagebreak
+\begin{figure}[ht]
+\centering
+\includegraphics[scale=0.5]{level5}
+\caption{The initial starting state for level5.txt}
+\label{Level5State}
+\end{figure}
+Level 5 - shown in Figure \ref{Level5State} - poses a particular problem for many of the agents (see Figure \ref{avgScoreMap5}).
+The asymmetric nature of the level, and the delayed reward caused great difficulty for the Agents.
+Relying on two button presses and the other agent to get through the open doors - in order - greatly reduced performance.
+The top agent, High MCTS, only managed an average score of $0.44$ compared to its total average of just over 0.8.
+
+\begin{figure}[ht]
+\centering
+\includegraphics[trim=0cm 0cm 5cm 3cm, clip=true, width = \linewidth]{avgScoreOverMap5}
+\caption{Average Score for each AI agent over Map 5}
+\label{avgScoreMap5}
+\end{figure}
+
+\section{Conclusions}
+In this paper, we found that a strong MCTS player can solve simple cooperative problems without requiring communication between agents.
 \bibliographystyle{IEEEtran}

### 2015-07-03 Report/stats-processing/coop-process.R
stats-processing

@@ -1,0 +1,93 @@
+setwd("M:\\graphs")
+library(ggplot2) 
+
+# custom functions
+alpha<-0.05 # for a (1.00-alpha)=95% confidence interval
+c <- function() rm(list=ls())
+se <- function(x) sd(x) / sqrt(length(x))
+
+build_summary_score <- function (x) {
+	s <- data.frame(
+    		agent1=levels(x$agent1),
+    		mean=tapply(x$score, x$agent1, mean),
+    		n=tapply(x$score, x$agent1, length),
+    		sd=tapply(x$score, x$agent1, sd),
+    		se=tapply(x$score, x$agent1, se)
+	)
+	# Precalculate standard error of the mean (SEM)
+	s$sem <- s$sd/sqrt(s$n)
+	# Precalculate margin of error for confidence interval
+	s$me <- qt(1-alpha/2, df=s$n)*s$sem
+	return(s)
+}
+
+build_summary_ticks <- function (x) {
+	s <- data.frame(
+    		agent1=levels(x$agent1),
+    		mean=tapply(x$ticks, x$agent1, mean),
+    		n=tapply(x$ticks, x$agent1, length),
+    		sd=tapply(x$ticks, x$agent1, sd),
+    		se=tapply(x$ticks, x$agent1, se)
+	)
+	# Precalculate standard error of the mean (SEM)
+	s$sem <- s$sd/sqrt(s$n)
+	# Precalculate margin of error for confidence interval
+	s$me <- qt(1-alpha/2, df=s$n)*s$sem
+	return(s)
+}
+
+build_graph <- function (filename, title, s) {
+	summary(s)
+	png(filename, width = 720, height = 480, units="px")
+	p = ggplot(s, aes(x = agent1, y = mean)) +  
+  	geom_bar(position = position_dodge(), stat="identity", fill="blue") + 
+  	geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem)) +
+  	ggtitle(title) + 
+  	theme_bw() +
+  	theme(panel.grid.major = element_blank())
+	print(p)
+	invisible(dev.off())
+}
+
+#read in our raw data
+games.raw <- read.csv(file="m:\\combined.csv", head=TRUE,sep=",")
+
+# build graphs of agent and it's self
+samePairs.raw = games.raw[games.raw$agent1==games.raw$agent2,]
+samePairs.scores <- build_summary_score(samePairs.raw)
[…]

### 2015-07-03 Report/ceec.tex

@@
 \begin{abstract}
-This paper highlights an experiment to see how standard \gls{mcts} handles simple co-operative problems with no prior or provided knowledge.	These problems are formed from a simple grid world that has a set of goals, doors and buttons as well as walls that cannot be walked through.
+This paper highlights an experiment to see how standard \gls{mcts} handles simple co-operative problems with no prior or provided knowledge.
+These problems are formed from a simple grid world that has a set of goals, doors and buttons as well as walls that cannot be walked through.
 Two agents have to each reach every goal present on the map.
@@
 
-The problems are designed to require Agents to co-operate in order to achieve their goals.
+The problems are designed to require \emph{Agents} to co-operate in order to achieve their goals.
 Unlike other environments where \gls{mcts} can charge off achieving its own goals, this domain requires the agents to sometimes sit patiently on a button for another Agent to do something else.
@@
 Typical behaviour would be near optimal with significantly less random sections of movement.
-This can likely be attributed to the increased rollout and uct border depths allowing more foresight on such a small puzzle.
+This can likely be attributed to the increased rollout and \gls{uct} border depths allowing more foresight on such a small puzzle.
 \subsection{Tournament}
@@
 No knowledge about the game is provided and the assumption is made that the other player will play randomly.
-The fixed rollout border makes a significant improvement in iterations per decision (On the machine from 1-3 to 500-600 in 40ms).
+The fixed rollout border makes a significant improvement in iterations per decision (from 1-3 to 500-600 in 40ms \footnote{Intel Core i5-3570, 8GB RAM, Windows 7 Enterprise 64bit}).
 This greatly improves the ability of \gls{mcts} to make informed decisions.
@@
 \includegraphics[width=\linewidth]{level1vsleve1e}
-\caption{Graph showing the average score obtained by each Agent across level 1(Blue) and level 1E (Orange)}
+\caption{Graph showing the average score obtained by each \emph{Agent} across level 1(Blue) and level 1E (Orange)}
 \label{1v1eS}
@@
 \includegraphics[width=\linewidth]{level1vsleve1eTicks}
-\caption{Graph showing the average ticks taken for each AI Agent across level 1(Blue) and level 1E (Orange)}
+\caption{Graph showing the average ticks taken for each \gls{ai} \emph{Agent} across level 1(Blue) and level 1E (Orange)}
 \label{1v1eT}
@@
 Figure \ref{1v1eS} shows the effect that having the complex \emph{Buttons} and \emph{Doors} in a level has on the score an Agent achieves.
-Figure \ref{1v1eT} demonstrates the vast improvement in pathfinding ability to a goal in the VariGA compared to the GAController.
+Figure \ref{1v1eT} demonstrates the vast improvement in path finding ability to a goal in the VariGA compared to the GAController.
+This is expected due to the ability to make individual actions as compared to the GAController which is only able to make 3 identical turns at a time leading to convoluted paths compared to optimum.
 
@@
 Relying on two button presses and the other agent to get through the open doors - in order - greatly reduced performance.
-The top agent, High MCTS, only managed an average score of $0.44$ compared to its total average of just over 0.8.
+The top agent, High MCTS, only managed an average score of $0.44$ compared to its total average of just over $0.8$.
 
@@
 \centering
-\includegraphics[trim=0cm 0cm 5cm 3cm, clip=true, width = \linewidth]{avgScoreOverMap5}
+\includegraphics[ width = \linewidth]{avgScoreOverMap5}
 \caption{Average Score for each AI agent over Map 5}
@@
 In this paper, we found that a strong MCTS player can solve simple cooperative problems without requiring communication between agents.
+We also found that a number of other \gls{ai} techniques experienced difficulty when the problem became cooperative.
+Further work is required in this area.
+
+\subsection{Further Work}
+There is scope for more work in a number of areas.
+More work can be conducted in the writing of AI's to use communication in order to complete these challenges better amongst themselves.
+A framework for communication would be devised - with the requirement for fairly \gls{ggp} restrictions in mind.
+
+More work can also be done on experimenting with the problem domain itself.
+Expanding the object types to include different techniques such as pickup-able objects that can be placed on \emph{Buttons}, \emph{Buttons} that remain active for a period of time after vacating them as well as potentially \emph{Doors} that will open permanently if all it's \emph{Buttons} are activated.
+The scope here is fairly limitless.
+
 \bibliographystyle{IEEEtran}

### 2015-07-03 Report/process-data.R
removed old R script

@@ -1,38 +1,0 @@
-setwd("M:\\graphs")
-
-library(ggplot2) 
-games <- read.csv(file="m:\\combined.csv", head=TRUE,sep=",")
-
-scores <- aggregate(games$score, list(agent1=games$agent1), mean)
-png(filename="scores-allmaps.png", width = 480, height = 480, units="px")
-mp <- barplot(scores$x, names.arg=scores$agent1, ylab="Scores", ylim=c(0,1),axisnames = FALSE)
-text(mp, par("usr")[3], labels = scores$agent1, srt = 45, adj = 1, xpd = TRUE)
-axis(2)
-invisible(dev.off())
-
-ticks <- aggregate(games$ticks, list(agent1=games$agent1), mean)
-png(filename="ticks-allmaps.png", width = 480, height = 480, units="px")
-mp <- barplot(ticks$x, names.arg=ticks$agent1, ylab="ticks", ylim=c(0,2000),axisnames = FALSE)
-text(mp, par("usr")[3], labels = ticks$agent1, srt = 45, adj = 1, xpd = TRUE)
-axis(2)
-invisible(dev.off())
-
-for (map in unique(games$maps)) {
-	filtered <- games[games$maps==map, ]
-	scores <- aggregate(filtered$scores, list(agent1=filtered$agent1), mean)
-	ticks <- aggregate(filtered$ticks, list(agent1=filtered$agent1), mean)
-
-	nameScores = paste(map,"-scores.png",sep="")
-	png(filename=nameScores, width = 480, height = 480, units="px")
-	mp <- barplot(scores$x, names.arg=scores$agent1, ylab="Scores", ylim=c(0,1), axisnames = FALSE)
-	text(mp, par("usr")[3], labels = scores$agent1, srt = 45, adj = 1, xpd = TRUE)
-	axis(2)
-	invisible(dev.off())
-
-	nameTicks  = paste(map,"-ticks.png",sep="")
-	png(filename=nameTicks, width = 480, height = 480, units="px")
-	mp <- barplot(ticks$x, names.arg=ticks$agent1, ylab="ticks", ylim=c(0,2000), axisnames = FALSE)
-	text(mp, par("usr")[3], labels = ticks$agent1, srt = 45, adj = 1, xpd = TRUE)
-	axis(2)
-	invisible(dev.off())
-}

### 2015-07-03 Report/stats-processing/coop-process.R
Reworked the R file for making graphs with filenames that can be read by latex

@@ -1,4 +1,4 @@
-setwd("M:\\graphs")
+setwd("D:\\graphs")
 library(ggplot2) 
 
 # custom functions
@@ -50,7 +50,7 @@ build_graph <- function (filename, title, s) {
 }
 
 #read in our raw data
-games.raw <- read.csv(file="m:\\combined.csv", head=TRUE,sep=",")
+games.raw <- read.csv(file="combined.csv", head=TRUE,sep=",")
 
 # build graphs of agent and it's self
 samePairs.raw = games.raw[games.raw$agent1==games.raw$agent2,]
@@ -76,9 +76,9 @@ for (map in unique(games.raw$maps)) {
 	filtered.raw <- games.raw[games.raw$maps==map, ]
 	filtered.scores <- build_summary_score(filtered.raw)
 	filtered.ticks <- build_summary_ticks(filtered.raw)
-
-	name.scores = paste(map,"-scores.png",sep="")
-	name.ticks = paste(map,"-ticks.png",sep="")
+	mapper <- gsub("[.]", "-", map)
+	name.scores = paste(mapper,"-scores.png",sep="")
+	name.ticks = paste(mapper,"-ticks.png",sep="")
 	build_graph(name.scores, "All agents across a single map", filtered.scores)
 	build_graph(name.ticks, "All agents across a single map", filtered.ticks)
 
@@ -86,8 +86,8 @@ for (map in unique(games.raw$maps)) {
 	samePairs.scores <- build_summary_score(samePairs.raw)
 	samePairs.ticks <- build_summary_ticks(samePairs.raw)
 
-	name.scores = paste(map,"-pairs-scores.png",sep="")
-	name.ticks = paste(map,"-pairs-ticks.png",sep="")
+	name.scores = paste(mapper,"-pairs-scores.png",sep="")
+	name.ticks = paste(mapper,"-pairs-ticks.png",sep="")
 	build_graph(name.scores, "All agents paired with themselves", samePairs.scores)
 	build_graph(name.ticks, "All agents paired with themselves", samePairs.ticks)
 }

### 2015-07-04 Report/ceec.tex
Reworked the R file for making graphs with filenames that can be read by latex
Worked latex to read from either of the maps directories
Changed the old graphs to a new file name so that latex gets the correct new ones
Widened the graphs a little - changed the csv file I was using to include VariGA instead of the really long name which fixed the graphs. Some minor extra writing in the document

@@
 \usepackage{glossaries}
+
+\graphicspath{{stats-processing/}{stats-processing/data/maps/}}
 
@@
 \centering
-\includegraphics[width=\linewidth]{level1vsleve1e}
-\caption{Graph showing the average score obtained by each \emph{Agent} across level 1(Blue) and level 1E (Orange)}
-\label{1v1eS}
+\includegraphics[width=\linewidth]{level1E-txt-pairs-ticks}
+\caption{Average ticks taken to complete level1E.txt when paired only with identical Agents}
+\label{1epairedTicks}
 \end{figure}
@@
 \centering
-\includegraphics[width=\linewidth]{level1vsleve1eTicks}
-\caption{Graph showing the average ticks taken for each \gls{ai} \emph{Agent} across level 1(Blue) and level 1E (Orange)}
-\label{1v1eT}
+\includegraphics[width=\linewidth]{level1-txt-pairs-ticks}
+\caption{Average ticks taken to complete level1.txt when paired only with identical Agents}
+\label{1pairedTicks}
 \end{figure}
 
-Figure \ref{1v1eS} shows the effect that having the complex \emph{Buttons} and \emph{Doors} in a level has on the score an Agent achieves.
-Figure \ref{1v1eT} demonstrates the vast improvement in path finding ability to a goal in the VariGA compared to the GAController.
-This is expected due to the ability to make individual actions as compared to the GAController which is only able to make 3 identical turns at a time leading to convoluted paths compared to optimum.
+Figure \ref{1epairedTicks} shows the ability of each Agent to solve a simple path finding problem.
+The \emph{GAcontroller}, with its macro actions, is hindered by its inability to make single step moves and has trouble actually walking straight to the target.
+The \emph{VariGA} does significantly better, due to its ability to perform single step moves.
+Figure \ref{1pairedTicks} shows that most of the controllers really struggle when the \emph{Door} and \emph{Buttons} are added.
+This proves that the challenge of the task is high, although perhaps remarkable that \gls{mcts} is able to solve the tasks.
 
@@
 \centering
-\includegraphics[width=\linewidth]{avgScoreOverAllMaps}
+\includegraphics[width=\linewidth]{scores-allmaps}
 \caption{Average score of each AI Agent over all the Maps}
 \label{avgScoreAllMaps}
+\end{figure}
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=\linewidth]{ticks-allmaps}
+\caption{Average Ticks taken for each AI Agent over all the Maps}
+\label{avgTicksAllMaps}
+\end{figure}
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=\linewidth]{scores-samepairs}
+\caption{Average Scores for each AI Agent paired with itself over all the Maps}
+\label{avgScorePairAllMaps}
+\end{figure}
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=\linewidth]{ticks-samepairs}
+\caption{Average Ticks taken for each AI Agent paired with itself over all the Maps}
+\label{avgTicksPairAllMaps}
 \end{figure}
@@
 \emph{RandomController} is the only deviant here - it outperformed the GA's in score but was worse in average ticks.
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=\linewidth]{avgTicksOverAllMaps}
-\caption{Average Ticks taken for each AI Agent over all the Maps}
-\label{avgTicksAllMaps}
-\end{figure}
+Comparing the \gls{ai} \emph{Agents} when paired only with themselves in Figure \ref{avgScorePairAllMaps} and Figure \ref{avgTicksPairAllMaps}.
+The shockingly good results for \emph{RandomController} are potentially due to the fact that the 3 \gls{mcts} controllers and 2 \gls{ga} algorithms all based their decisions on having Random as an accomplice.
 
@@
 \end{figure}
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width = \linewidth]{level5-txt-scores}
+\caption{Average Score for each AI agent over Map 5}
+\label{avgScoreMap5}
+\end{figure}
+
 Level 5 - shown in Figure \ref{Level5State} - poses a particular problem for many of the agents (see Figure \ref{avgScoreMap5}).
@@
 The top agent, High MCTS, only managed an average score of $0.44$ compared to its total average of just over $0.8$.
-
-\begin{figure}[ht]
-\centering
-\includegraphics[ width = \linewidth]{avgScoreOverMap5}
-\caption{Average Score for each AI agent over Map 5}
-\label{avgScoreMap5}
-\end{figure}
 
@@
 More work can be conducted in the writing of AI's to use communication in order to complete these challenges better amongst themselves.
-A framework for communication would be devised - with the requirement for fairly \gls{ggp} restrictions in mind.
+A framework for communication would be devised - with the requirement for fairly \gls{ggp} like restrictions in mind.
 

### 2015-07-04 Report/stats-processing/coop-process.R

@@ -38,7 +38,7 @@ build_summary_ticks <- function (x) {
 
 build_graph <- function (filename, title, s) {
 	summary(s)
-	png(filename, width = 720, height = 480, units="px")
+	png(filename, width = 900, height = 500, units="px")
 	p = ggplot(s, aes(x = agent1, y = mean)) +  
   	geom_bar(position = position_dodge(), stat="identity", fill="blue") + 
   	geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem)) +

### 2015-07-04 Report/ceec.tex
Work

@@
 
-\author{Piers R. Williams, \and Joseph Walton-Rivers}
+%\author{Piers R. Williams, \and Joseph Walton-Rivers}
 
@@
 \includegraphics[width = \linewidth]{level5-txt-scores}
-\caption{Average Score for each AI agent over Map 5}
+\caption{Average Score for each AI Agent over Map 5}
 \label{avgScoreMap5}
@@
 Relying on two button presses and the other agent to get through the open doors - in order - greatly reduced performance.
-The top agent, High MCTS, only managed an average score of $0.44$ compared to its total average of just over $0.8$.
+The top agent, \emph{High MCTS}, only managed an average score of $0.44$ compared to its total average of just over $0.8$.
 
@@
 There is scope for more work in a number of areas.
+
+\subsubsection{Communication}
 More work can be conducted in the writing of AI's to use communication in order to complete these challenges better amongst themselves.
@@
 
+\subsubsection{Optimisations}
+Future work should also include some work to ensure that the \gls{ai} Agents have their parameters set correctly.
+The \emph{High MCTS} performed well - showing the power of having the correct parameters compared to the \emph{Low MCTS}.
+The \emph{VariGA} has 7 parameters that we simply didn't have time to correctly optimise for this experiment.
+
+\subsubsection{Problem Domain}
 More work can also be done on experimenting with the problem domain itself.

### 2015-08-01 Report/response.tex
Oops - named it wrong. also made it have some structure

\documentclass{article}
\title{Response}

\begin{document}
\maketitle
\section{Letters to the reviewers}
\subsection{Review 1 (Reviewer )}
\subsection{Review 2 (Reviewer )}
\subsection{Review 3 (Reviewer )}
\subsection{Review 4 (Reviewer )}
\subsection{Review 5 (Reviewer )}
\end{document}

### 2015-08-01 Report/response.tex
Fixed the typo for the walls

@@
 \subsection{Review 1 (Reviewer )}
+We have corrected the typo in the definition of Walls in the problem domain section.
 \subsection{Review 2 (Reviewer )}
 \subsection{Review 3 (Reviewer )}
+We have corrected the incorrect definition of UCT from Uniform Cost over Trees to Upper Confidence bound applied to Trees.
+
+We have corrected the typo in the definition of Walls in the problem domain section.
 \subsection{Review 4 (Reviewer )}

### 2015-08-01 Report/response.tex
Fixed the description of doors to show what they look like when open

@@
 \subsection{Review 1 (Reviewer )}
-We have corrected the typo in the definition of Walls in the problem domain section.
+We have corrected the typo in the definition of \emph{Walls} in the problem domain section.
+
+We have changed the description of \emph{Doors} to better reflect what they look like when open.
 \subsection{Review 2 (Reviewer )}
@@
 
-We have corrected the typo in the definition of Walls in the problem domain section.
+We have corrected the typo in the definition of \emph{Walls} in the problem domain section.
 \subsection{Review 4 (Reviewer )}

### 2015-08-01 Report/ceec.tex
Fixed the UCT Definition error
Fixed the typo for the walls
Fixed the description of doors to show what they look like when open
Added definition for the floor

@@
 \newacronym{mcts}{MCTS}{Monte-Carlo Tree Search}
-\newacronym{uct}{UCT}{Uniform Cost applied to Trees}
+\newacronym{uct}{UCT}{Upper Confidence bound applied to Trees}
 \newacronym{ggp}{GGP}{General Game Playing}
@@
 \begin{itemize}
-\item{\emph{Walls -} Walls are impassable, and are fixed in position. \emph{Doors} are rendered in Black.}
+\item{\emph{Floor - } Floors are passable, and are rendered in Grey.}
+\item{\emph{Walls -} Walls are impassable, and are fixed in position. \emph{Walls} are rendered in Black.}
 \item{\emph{Agents -} Agents are the moving objects that can activate buttons and the goal. \emph{Agents} are rendered in dark Yellow}
-\item{\emph{Doors -} Doors are impassable, unless a linked \emph{Button} is currently activated. \emph{Doors} are rendered in Blue unless they are open}
+\item{\emph{Doors -} Doors are impassable, unless a linked \emph{Button} is currently activated. \emph{Doors} are rendered in Blue whilst closed, and are invisible when open}
 \item{\emph{Buttons -} Buttons are passable, and when an \emph{Agent} is on the \emph{Button} it will activate and open the linked \emph{Door}. \emph{Buttons} are rendered in Red}

### 2015-08-01 Report/ceec.tex
Fixed up the door definition to be clearer

@@
 \item{\emph{Agents -} Agents are the moving objects that can activate buttons and the goal. \emph{Agents} are rendered in dark Yellow}
-\item{\emph{Doors -} Doors are impassable, unless a linked \emph{Button} is currently activated. \emph{Doors} are rendered in Blue whilst closed, and are invisible when open}
+\item{\emph{Doors -} Doors can either be open or closed.
+When open, the door is passable.
+When closed, the door is impassable.
+Doors are open whilst an \emph{Agent} is activating a linked \emph{Button}.
+If the \emph{Agent} stops activating the \emph{Button} the \emph{Door} will close.
+\emph{Doors} are rendered in Blue when closed, and are invisible when open.}
 \item{\emph{Buttons -} Buttons are passable, and when an \emph{Agent} is on the \emph{Button} it will activate and open the linked \emph{Door}. \emph{Buttons} are rendered in Red}

### 2015-08-01 Report/response.tex
Added definition for the floor
Fixed up the door definition to be clearer
Bright yellow goals instead of Yellow

@@
 We have changed the description of \emph{Doors} to better reflect what they look like when open.
+
+We have added a definition for the \emph{Floor}.
+
+We have improved the definition for \emph{Door} in order to make it clearer that the \emph{Door} closes again when the \emph{Buttons} are no longer activated.
+
+We have reworded the definition of \emph{Goal} to better describe the colour in relation to \emph{Agents}.
 \subsection{Review 2 (Reviewer )}

### 2015-08-01 Report/ceec.tex
Bright yellow goals instead of Yellow
Removed explanation of MCTS from abstract

@@
 \begin{abstract}
-This paper highlights an experiment to see how standard \gls{mcts} handles simple co-operative problems with no prior or provided knowledge.
+This paper highlights an experiment to see how standard MCTS handles simple co-operative problems with no prior or provided knowledge.
 These problems are formed from a simple grid world that has a set of goals, doors and buttons as well as walls that cannot be walked through.
@@
 When laid out correctly, the world requires each agent to do certain things at certain times in order to achieve the goal.
-With no modification to allow communication between the two Agents - \gls{mcts} performs well and performs very 'purposefully' when given enough computational time.
+With no modification to allow communication between the two Agents - MCTS performs well and performs very 'purposefully' when given enough computational time.
 \end{abstract}
@@
 Re-visiting a \emph{Goal} has no effect.
-\emph{Goals} are rendered in Yellow}
+\emph{Goals} are rendered in Bright Yellow}
 \end{itemize}

### 2015-08-01 Report/response.tex
Added section on the action cycle

@@
 \subsection{Review 2 (Reviewer )}
-\subsection{Review 3 (Reviewer )}
+\subsection{Review 3 (Reviewer G)}
 We have corrected the incorrect definition of UCT from Uniform Cost over Trees to Upper Confidence bound applied to Trees.
@@
 We have corrected the typo in the definition of \emph{Walls} in the problem domain section.
+
+The definition of the problem domain has been improved with a section describing the particular way that actions are collected and executed as well as a list of each possible action that can be chosen.
 \subsection{Review 4 (Reviewer )}

### 2015-08-01 Report/ceec.tex
Added section on the action cycle

@@
 \emph{Goals} are rendered in Bright Yellow}
+\end{itemize}
+
+Each \emph{Agent} is able to make a single action in each game tick.
+The actions are polled from each \emph{Agent} that is given the state of the game.
+When every \emph{Agent} has returned an action, the game is updated with these actions.
+The actions are implemented sequentially, if two \emph{Agents} return actions that result in occupying the same space, the \emph{Agent} with the lowest ID number will succeed while the other \emph{Agent} will fail and execute a \emph{No-Op}.
+The available 5 actions are:
+\begin{itemize}
+\item{\emph{Left} - This will move the \emph{Agent} one grid square to the left. (-1, 0)}
+\item{\emph{Right} - This will move the \emph{Agent} one grid square to the right. (1, 0)}
+\item{\emph{Up} - This will move the \emph{Agent} one grid square up. (0, -1)}
+\item{\emph{Down} - This will move the \emph{Agent} one grid square down. (0, 1)}
+\item{\emph{No-Op} - This will not move the \emph{Agent}. It will remain in the same location as the previous game state.}
 \end{itemize}

### 2015-08-01 Report/response.tex
Added the correct Reviewer letter for each review
Clarified the goal knowledge thing

@@
 \section{Letters to the reviewers}
-\subsection{Review 1 (Reviewer )}
+\subsection{Review 1 (Reviewer A)}
 We have corrected the typo in the definition of \emph{Walls} in the problem domain section.
@@
 We have reworded the definition of \emph{Goal} to better describe the colour in relation to \emph{Agents}.
-\subsection{Review 2 (Reviewer )}
+\subsection{Review 2 (Reviewer D)}
 \subsection{Review 3 (Reviewer G)}
@@
 The definition of the problem domain has been improved with a section describing the particular way that actions are collected and executed as well as a list of each possible action that can be chosen.
-\subsection{Review 4 (Reviewer )}
-\subsection{Review 5 (Reviewer )}
+
+We have clarified whether the \emph{Agents} are aware that other \emph{Agents} reach a \emph{Goal}.
+\subsection{Review 4 (Reviewer B)}
+\subsection{Review 5 (Reviewer F)}
 \end{document}

### 2015-08-01 Report/ceec.tex
Clarified the goal knowledge thing
Dealt with the observability problem

@@
 \section{The Experiment}
-The main premise was to put \gls{mcts} in a situation where it would rely on other AI Agents in order to achieve its objectives, as well as provide a code base for further work with communication between Agents.
+The main premise was to put \gls{mcts} in a situation where it would rely on other AI Agents in order to achieve its objectives, as well as provide a code base for further work with communication between \emph{Agents}.
 In order to do this, a problem domain was created.
@@
 Re-visiting a \emph{Goal} has no effect.
+All \emph{Agents} are aware of the current score achieved, and therefore can calculate if a \emph{Goal} is reached.
 \emph{Goals} are rendered in Bright Yellow}
 \end{itemize}
+
+The \emph{Agents} are provided with a forward model, that allows simulation of potential moves up to the end of the game.
+The \emph{Agents} are not allowed to directly query any information about the game state other than the score at any given state (current or simulated).
 

### 2015-08-01 Report/response.tex
Dealt with the observability problem
Restyled bits to better fit a suggestion from Diego for the response thing

@@
 \maketitle
-\section{Letters to the reviewers}
+\section{Response to the reviewers}
+We have placed the reviewers comments in \textit{\textbf{Italics and Bold}} and our response to those comments in plain text.
+
 \subsection{Review 1 (Reviewer A)}
+\paragraph*{\textit{When listing objects in  II.A the default gray empty square should also be mentioned.}}
+We have added a definition for the \emph{Floor}.
+\paragraph*{\textit{In the definition of 'Walls' the word 'Walls' appears instead of 'Doors'.}}
 We have corrected the typo in the definition of \emph{Walls} in the problem domain section.
-
+\paragraph*{\textit{When specifying that closed 'Doors' are blue there should be mention of the color of open 'Doors' (I assume gray).}}
 We have changed the description of \emph{Doors} to better reflect what they look like when open.
-
-We have added a definition for the \emph{Floor}.
-
+\paragraph*{\textit{It is unclear if 'Door' closes again when agent on button moves on (or, alternatively, if walking onto a 'Button' effectively destroy the 'Door').}}
 We have improved the definition for \emph{Door} in order to make it clearer that the \emph{Door} closes again when the \emph{Buttons} are no longer activated.
-
+\paragraph*{\textit{Since 'Agents' are described as dark yellow, and since there are only two shades of yellow used, it would be wiser to describe a 'Goal' as rendered in bright yellow.}}
 We have reworded the definition of \emph{Goal} to better describe the colour in relation to \emph{Agents}.
@@
 We have clarified whether the \emph{Agents} are aware that other \emph{Agents} reach a \emph{Goal}.
+
+We have clarified how the problem domain handles observability and what information the \emph{Agents} have access to.
+
+We have clarified who created the problem domain.
 \subsection{Review 4 (Reviewer B)}

### 2015-08-01 Report/response.tex
Updated R3 to new format

@@
 \subsection{Review 3 (Reviewer G)}
+\paragraph*{\textit{What is "Uniform Cost applied to Trees"? Is it something similar to the famous "Upper Confidence bound applied to Trees"? If not, please cite something.}}
 We have corrected the incorrect definition of UCT from Uniform Cost over Trees to Upper Confidence bound applied to Trees.
-
+\paragraph*{\textit{Is the problem domain a real time problem? How long is a tick? 40ms? Do all agents return an action within a tick?}}
+The definition of the problem domain has been improved with a section describing the particular way that actions are collected and executed as well as a list of each possible action that can be chosen.
+\paragraph*{\textit{If an agent reaches a goal, is it known to the other agents?}}
+We have clarified whether the \emph{Agents} are aware that other \emph{Agents} reach a \emph{Goal}.
+\paragraph*{\textit{Do agents see all areas of the problem?}}
+We have clarified how the problem domain handles observability and what information the \emph{Agents} have access to.
+\paragraph*{\textit{Who created this problem domain?}}
+We have clarified who created the problem domain.
+\paragraph*{\textit{"Doors are rendered in Black." -> "Walls are rendered in Black."}}
 We have corrected the typo in the definition of \emph{Walls} in the problem domain section.
-
-The definition of the problem domain has been improved with a section describing the particular way that actions are collected and executed as well as a list of each possible action that can be chosen.
-
-We have clarified whether the \emph{Agents} are aware that other \emph{Agents} reach a \emph{Goal}.
-
-We have clarified how the problem domain handles observability and what information the \emph{Agents} have access to.
-
-We have clarified who created the problem domain.
 \subsection{Review 4 (Reviewer B)}

### 2015-08-01 Report/response.tex
Added the comments for R4 and R5, which just await our responses

@@
 \subsection{Review 4 (Reviewer B)}
+\paragraph*{\textit{there is some mixup with agents being labeled 0 and 1 in the figures, but 1 and 2 in the text.}}
+
+\paragraph*{\textit{I did not understand the terms "UCT border" and "rollout border". Explain them. Are they related to "Max UCT" and "Max Rollout" in Fig. 2 ?}}
+\paragraph*{\textit{What does 1+1 ES mean?}}
+\paragraph*{\textit{I did not quite understand how your MCTS works with multiple agents. Are you running independent simulations for each agent (I assume yes but it was not clear)? }}
+\paragraph*{\textit{I would like to see results for mixed agent teams.}}
+\paragraph*{\textit{The issue of communication, especially learning communication, is very important and I suggest you focus on this for future research.}}
 \subsection{Review 5 (Reviewer F)}
+\paragraph*{\textit{The early segments fail to really discuss the MCTS algorithm.  The abbreviation for this is also found in the abstract and should really be in the introductory paragraph.}}
+\paragraph*{\textit{Section II covering preliminary tests is light on technical details and seem ill placed when you consider the subsequent studies later on in the paper.}}
+\paragraph*{\textit{The third page could do with being structured better.  The charts are ill-placed, do not help the flow of the authors argument and need better captions.}}
+\paragraph*{\textit{The paper would benefit from showing the actual levels used as part of the testing.
+Given it makes it harder to understand the impact of later levels.
+Figure 10 should be shown much earlier in the paper.}}
+\paragraph*{\textit{The selection of controller types does strike me as odd.
+With a random selected and a Variable MAGA that is introduced to resolve shortcoming of the other.
+What about a simple 1+1 ES without the macro's?
+Or the likes of an A* bot?
+Could these not be implemented?}}
+\paragraph*{\textit{More than once the idea of a language through which to communicate is discussed, but it has no real impact on this paper and should really be saved for when it is explored}}
 \end{document}

### 2015-08-01 Report/response.tex
Added R2

@@
 \subsection{Review 2 (Reviewer D)}
+\paragraph*{\textit{The writing is generally good, I only noticed one actual error "GGP[3]", but the tone is casual and a lot of inappropriately subjective comments are made}}
+\paragraph*{\textit{The authors make a few dubious claims in the Introduction.
+GGP is not exactly "the field of writing Artificial Intelligence (AI) agents", and it is wrong to say that "MCTS doesn't requuire any knowledge about the game itself in order to play", as it needs to know starting position, legal moves, terminal states, etc.
+Perhaps the authors means "strategic knowledge".
+}}
+\paragraph*{\textit{The authors claim that MCTS works best when it is given rewards frequently. What is the evidence for this claim?}}
+\paragraph*{\textit{The research problem is stated, but should be stated more clearly in the Introduction.}}
+\paragraph*{\textit{"MCTS can charge off achieving its own goals": it seems odd to describe an algorithm as "charging off".}}
+\paragraph*{\textit{"This proves that the challenge...": no it doesn't, it indicates it.}}
+\paragraph*{\textit{"The shockingly good results...": too casual and subjective, overstating the case.}}
+\paragraph*{\textit{There is no Discussion as such, rather there are subjective appraisals of the algorithm's performance at each task scattered throughout the results.
+The paper would be better structures with a Discussion section that summarised the results and their implications, and then recapped this in the Conclusion.
+At the moment, the exact contributions are a bit hard to see.}}
+\paragraph*{\textit{The list of references is short (four) and does not include any references to work on cooperative agents, swarm behaviour, etc.}}
+\paragraph*{\textit{Despite these concerns with the presentation, I liked the idea and the authors' approach to investigating the problem.
+The paper could be improved greatly with a little bit of work.}}
 \subsection{Review 3 (Reviewer G)}

### 2015-08-02 Report/response.tex
Removed the initial testing section

@@
 \paragraph*{\textit{Section II covering preliminary tests is light on technical details and seem ill placed when you consider the subsequent studies later on in the paper.}}
+We have removed this section to make way for more detailed results
 \paragraph*{\textit{The third page could do with being structured better.  The charts are ill-placed, do not help the flow of the authors argument and need better captions.}}

### 2015-08-02 Report/ceec.tex
Restyled bits to better fit a suggestion from Diego for the response thing
Removed the initial testing section
Shockingly good

@@
 \usepackage{glossaries}
+\usepackage{verbatim}
 
@@
 \subsection{The Problem Domain}
-The problem domain is a simple grid world consisting of various objects:
+We created the following problem domain that is a simple grid world consisting of various objects:
 \begin{itemize}
@@
 Unlike other environments where \gls{mcts} can charge off achieving its own goals, this domain requires the agents to sometimes sit patiently on a button for another Agent to do something else.
-
+\begin{comment}
 \subsection{Initial Testing}
@@
 This can likely be attributed to the increased rollout and \gls{uct} border depths allowing more foresight on such a small puzzle.
+\end{comment}
 \subsection{Tournament}
@@
 Comparing the \gls{ai} \emph{Agents} when paired only with themselves in Figure \ref{avgScorePairAllMaps} and Figure \ref{avgTicksPairAllMaps}.
-The shockingly good results for \emph{RandomController} are potentially due to the fact that the 3 \gls{mcts} controllers and 2 \gls{ga} algorithms all based their decisions on having Random as an accomplice.
+The good results for \emph{RandomController} are potentially due to the fact that the 3 \gls{mcts} controllers and 2 \gls{ga} algorithms all based their decisions on having Random as an accomplice.
 

### 2015-08-02 Report/ceec.tex
Fixed the issue with proves and indicates
Reworded the research problem

@@
 \section{Introduction}
+This research problem that this paper will asses is how \gls{ggp} agents perform when trying to solve a simple co-operative problem, with a focus on \gls{mcts}.
+
 \gls{ggp} is the field of writing \gls{ai} agents that can play a multitude of games without being written specifically for each one individually.
@@
 Figure \ref{1pairedTicks} shows that most of the controllers really struggle when the \emph{Door} and \emph{Buttons} are added.
-This proves that the challenge of the task is high, although perhaps remarkable that \gls{mcts} is able to solve the tasks.
+This indicates that the challenge of the task is high, although perhaps remarkable that \gls{mcts} is able to solve the task.
 

### 2015-08-04 Report/ceec.tex
Dealt with comment on GGP and MCTS

@@
 
-\gls{ggp} is the field of writing \gls{ai} agents that can play a multitude of games without being written specifically for each one individually.
+\gls{ggp} is the field of writing \gls{ai} agents that can play a multitude of games without being written specifically for each one individually \cite{genesereth2005general}.
 \gls{ggp} in real time video games is a popular competition \cite{perez2014}
@@
 \gls{mcts} \cite{browne2012survey} has been applied to a wealth of domains and is one of the primary algorithms in use for \gls{ggp}\cite{finnsson2008simulation}.
-Primary advantages are that, when given a sufficient forward model, \gls{mcts} doesn't require any knowledge about the game itself in order to play.
+Primary advantages are that, when given a sufficient forward model, \gls{mcts} doesn't require any strategic knowledge about the game itself in order to play.
 

### 2015-08-04 Report/response.tex
Shockingly good
Fixed the issue with proves and indicates
Dealt with comment on GGP and MCTS
Clarified the frequent rewards issue

@@
 }}
+Have clarified the definition of GGP with reference to this paper\cite{genesereth2005general} and the terminology used to define MCTS use of knowledge. 
 \paragraph*{\textit{The authors claim that MCTS works best when it is given rewards frequently. What is the evidence for this claim?}}
+Have rewritten this to point out that MCTS can't provide anything but random if it isn't given enough time or depth to search to a state that provides a reward.
 \paragraph*{\textit{The research problem is stated, but should be stated more clearly in the Introduction.}}
@@
 \paragraph*{\textit{"This proves that the challenge...": no it doesn't, it indicates it.}}
+Reworded to indicates.
 \paragraph*{\textit{"The shockingly good results...": too casual and subjective, overstating the case.}}
+Reworded. 
 \paragraph*{\textit{There is no Discussion as such, rather there are subjective appraisals of the algorithm's performance at each task scattered throughout the results.
@@
 \paragraph*{\textit{More than once the idea of a language through which to communicate is discussed, but it has no real impact on this paper and should really be saved for when it is explored}}
+
+\bibliographystyle{IEEEtran}
+\bibliography{ceec}
 \end{document}

### 2015-08-04 Report/ceec.tex
Clarified the frequent rewards issue

@@
 
-Standard \gls{mcts} plays best when it is either able to search to the end of the game tree, or is given rewards frequently.
-\gls{mcts} tends to stumble when the time given to it isn't sufficient to allow it to locate any sequence of actions that provides a reward in order to differentiate the root's children \cite{perez2012monte}.
+Standard \gls{mcts} plays best when it is able to search far enough to locate states that provide a reward.
+\gls{mcts} tends to stumble when the time or search depth limit given to it isn't sufficient to allow it to locate any sequence of actions that provides a reward in order to differentiate the root's children \cite{perez2012monte}.
+When \gls{mcts} can't find any single state that contained a reward, all children of the node will contain identical values and the algorithm will be forced to make a random choice.
 

### 2015-08-04 Report/ceec.tex
Fixed the charging off issue

@@
 The problems are designed to require \emph{Agents} to co-operate in order to achieve their goals.
-Unlike other environments where \gls{mcts} can charge off achieving its own goals, this domain requires the agents to sometimes sit patiently on a button for another Agent to do something else.
+Unlike other domains where \gls{mcts} can solve tasks at its own pace and by itself, this domain requires the agents to sometimes sit patiently on a button for another \emph{Agent} to do something else.
 \begin{comment}

### 2015-08-04 Report/response.tex
Fixed the charging off issue
Sorted out R3 and put the missing comments in ready for being answered

@@
 \paragraph*{\textit{The research problem is stated, but should be stated more clearly in the Introduction.}}
+Added at the beginning of the introduction a clear statement of the research problem.
 \paragraph*{\textit{"MCTS can charge off achieving its own goals": it seems odd to describe an algorithm as "charging off".}}
+Reworded.
 \paragraph*{\textit{"This proves that the challenge...": no it doesn't, it indicates it.}}
@@
 \subsection{Review 3 (Reviewer G)}
+\paragraph*{\textit{Who created this problem domain?}}
+We have clarified who created the problem domain.
+\paragraph*{\textit{The agents move simultaneously or alternately?}}
+Added a section to highlight this.
+\paragraph*{\textit{Do agents see all areas of the problem?}}
+We have clarified how the problem domain handles observability and what information the \emph{Agents} have access to.
+\paragraph*{\textit{If an agent reaches a goal, is it known to the other agents?}}
+We have clarified whether the \emph{Agents} are aware that other \emph{Agents} reach a \emph{Goal}.
+
+\paragraph*{\textit{In what sense this domain interesting compared to other domains?}}
+
+\paragraph*{\textit{Is the problem domain a real time problem?
+How long is a tick?
+40ms?
+Do all agents return an action within a tick?
+Possible 5 actions mean up, down left, right and stay where it is?}}
+The definition of the problem domain has been improved with a section describing the particular way that actions are collected and executed as well as a list of each possible action that can be chosen.
+
 \paragraph*{\textit{What is "Uniform Cost applied to Trees"? Is it something similar to the famous "Upper Confidence bound applied to Trees"? If not, please cite something.}}
 We have corrected the incorrect definition of UCT from Uniform Cost over Trees to Upper Confidence bound applied to Trees.
-\paragraph*{\textit{Is the problem domain a real time problem? How long is a tick? 40ms? Do all agents return an action within a tick?}}
-The definition of the problem domain has been improved with a section describing the particular way that actions are collected and executed as well as a list of each possible action that can be chosen.
-\paragraph*{\textit{If an agent reaches a goal, is it known to the other agents?}}
-We have clarified whether the \emph{Agents} are aware that other \emph{Agents} reach a \emph{Goal}.
-\paragraph*{\textit{Do agents see all areas of the problem?}}
-We have clarified how the problem domain handles observability and what information the \emph{Agents} have access to.
-\paragraph*{\textit{Who created this problem domain?}}
-We have clarified who created the problem domain.
+\paragraph*{\textit{About MCTS, what are "iteration", "UCT Border", and "rollout border"?
+My guess is iteration means the number of rollouts,
+UCT border means the UCT tree search depth limit, and
+rollout border means the length of the sequence of rollout.
+Am I correct?
+These phrases are different from normal terminology used in MCTS.}}
+\paragraph*{\textit{What is the reward of the rollout? Maybe the raw score?}}
+\paragraph*{\textit{About the results, what is averaged?
+How many runs are averaged?
+All agents play in cooperation with other agents including the "keyboard AI"?
+Is the keyboard AI controlled by human beings?
+Can we assume it plays perfectly well?}}
+\paragraph*{\textit{Please cite something about (1+1)-ES}}
+\paragraph*{\textit{If all information is visible to the agents,
+this problem domain seems not so interesting especially if
+both agents are the same.}}
+\paragraph*{\textit{I don't think GA is suitable for this domain.
+Comparing against A* search with a simple evaluation function would be more interesting.}}
+
 \paragraph*{\textit{"Doors are rendered in Black." -> "Walls are rendered in Black."}}

### 2015-08-04 Report/ceec.tex
Dealt with the MCTS terminology issues

@@
 \paragraph{\gls{mcts}}
-The \gls{mcts} controller is a simple implementation of \gls{uct} - with a fixed iteration, \gls{uct} Border and rollout border.
+The \gls{mcts} controller is a simple implementation of \gls{uct} - with a fixed number of rollouts, \gls{uct} tree search depth limit and rollout border.
+The rollout border is how far in total, the forward model will be allowed to progress before the game is evaluated.
 No knowledge about the game is provided and the assumption is made that the other player will play randomly.
@@
 \hline
-\textbf{Budget} & \textbf{Iterations} & \textbf{Max UCT} & \textbf{Max Rollout} \\
+\textbf{Budget} & \textbf{Rollouts} & \textbf{UCT Search Limit} & \textbf{Rollout Border} \\
 \hline

### 2015-08-05 Report/response.tex
Dealt with the MCTS terminology issues
Added all of R1 comments

@@
 \subsection{Review 1 (Reviewer A)}
+\paragraph*{\textit{Introduction: The introduction is well written but oddly doesn't contain discussion about cooperative games.
+The introduction starts by discussing general game playing (which is not a main topic of the paper) and then presents MCTS (which is) but the discussion of cooperative games is missing.}}
+
 \paragraph*{\textit{When listing objects in  II.A the default gray empty square should also be mentioned.}}
@@
 We have reworded the definition of \emph{Goal} to better describe the colour in relation to \emph{Agents}.
+\paragraph*{\textit{the sentence "Agent 1 reached an item like this -Agent 2 would seemingly gain some purpose and typically head for the other items." is poorly worded and not very informative.
+It is better explained in the sentences below.
+Either remove this sentence or reword it.}}
+
+\paragraph*{\textit{it would be a good idea to give the maps meaningful names.}}
+\paragraph*{\textit{The MAGA is not explained very well and seems hastily put together.
+I would say explain this better but given how poorly it does and how badly optimized it seems to be, maybe the authors should get rid of this player altogether.
+If this work is resubmitted in future I would recommend creating a better thought out version of this player.
+For now the better VMAGA should stand alone.
+}}
+\paragraph*{\textit{There should be a separate subsection for the results.s}}
+\paragraph*{\textit{In figures 4--9 the 3 MCTS players are ordered in an odd order Meduin-Large-Small.
+This order makes no sense and should be changed.
+GA-Controller is presented separately from Var-GA inexplicably.
+If this player is kept (and it shouldn't be.
+Unless changed and improved for submission somewhere else) then both GA players should be together.
+It seems that columns are organized automatically in alphabetical order they should be ordered in a way that makes sense.}}
+\paragraph*{\textit{Regarding the fact that players were trained assuming a random strategy was controlling the other player: This is mentioned again in the section, but a reasoning for this decision is not given.
+Why not use self play?
+Wouldn't it do better?
+Doesn't it make sense to assume a better than random strategy for the other player?}}
+
 \subsection{Review 2 (Reviewer D)}
@@
 We have corrected the incorrect definition of UCT from Uniform Cost over Trees to Upper Confidence bound applied to Trees.
-\paragraph*{\textit{About MCTS, what are "iteration", "UCT Border", and "rollout border"?
-My guess is iteration means the number of rollouts,
-UCT border means the UCT tree search depth limit, and
-rollout border means the length of the sequence of rollout.
-Am I correct?
-These phrases are different from normal terminology used in MCTS.}}
+\paragraph*{\textit{About MCTS, what are "iteration", "UCT Border", and "rollout border"? My guess is iteration means the number of rollouts,
+UCT border means the UCT tree search depth limit, and rollout border means the length of the sequence of rollout. Am I correct? These phrases are different from normal terminology used in MCTS.}}
+Reworded to more used terminology.
 \paragraph*{\textit{What is the reward of the rollout? Maybe the raw score?}}
@@
 \paragraph*{\textit{I did not understand the terms "UCT border" and "rollout border". Explain them. Are they related to "Max UCT" and "Max Rollout" in Fig. 2 ?}}
+Both have been reworded to a more used set of terminology.
 \paragraph*{\textit{What does 1+1 ES mean?}}

### 2015-08-05 Report/response.tex
Dealt with idea that we shouldn't have GA in

@@
 }}
-\paragraph*{\textit{There should be a separate subsection for the results.s}}
+\paragraph*{\textit{There should be a separate subsection for the results.}}
 \paragraph*{\textit{In figures 4--9 the 3 MCTS players are ordered in an odd order Meduin-Large-Small.
@@
 \paragraph*{\textit{The list of references is short (four) and does not include any references to work on cooperative agents, swarm behaviour, etc.}}
-\paragraph*{\textit{Despite these concerns with the presentation, I liked the idea and the authors' approach to investigating the problem.
-The paper could be improved greatly with a little bit of work.}}
 \subsection{Review 3 (Reviewer G)}
@@
 Comparing against A* search with a simple evaluation function would be more interesting.}}
+Referenced the design of the GA that shows validity in its theoretical ability to perform in real time general video game domains.
 

### 2015-08-05 Report/ceec.tex
Dealt with idea that we shouldn't have GA in

@@
 This meant the \gls{maga} could "see" 45 ticks in the future.
+The design of the \gls{maga} algorithm was inspired by \textit{Perez et al} \cite{perez2013rolling}
 \paragraph{Variable Macro Action Genetic Algorithm}
@@
 
-\begin{figure}[ht]
+\begin{figure}[!ht]
 \centering
@@
 \pagebreak
-\begin{figure}[ht]
+\begin{figure}[!ht]
 \centering
@@
 
+\subsection{Discussion}
+\subsubsection{MCTS}
+\gls{mcts} performed very well in this problem domain.
+
+As seen above, in Figure \ref{avgTicksPairAllMaps}, the medium and high budget implementations provided the two quickest completion times across all maps.
+The differences shown were significant as well as being the only two agents to complete on average in under 1000 ticks.
+Figure \ref{avgScorePairAllMaps} showed that the medium and high budget implementations scored significantly better than all other agents.
+\subsubsection{GA}
+The two \gls{ga} algorithms did not perform very well in this problem domain.
+
+As seen in Figure \ref{avgScorePairAllMaps} and Figure \ref{avgTicksPairAllMaps}, when tasked with solving the problem domain with another identical agent, neither the \emph{GAController} or \emph{VariGA} performed well at all.
+The \emph{VariGA} only performed significantly better than either \emph{RandomController} or \emph{GAController} in \emph{level1E.txt}.
+In all other cases, \emph{VariGA} performed similarly to the standard \emph{GAController}.
+The ability to mutate the lengths of individual action sequences made the \emph{VariGA} a more flexible pathfinder that the \emph{GAController} but did not aid its ability to solve the co-operative problems present elsewhere in the experiment.
+\subsubsection{Random}
+The \emph{RandomController} performed poorly in this problem domain. On average, the \emph{RandomController} finished under the 2000 tick limit and scored less than half the maximum on average.
 \section{Conclusions}

### 2015-08-05 Report/response.tex
Handled why we didn't do A* or ES non macro

@@
 Comparing against A* search with a simple evaluation function would be more interesting.}}
-Referenced the design of the GA that shows validity in its theoretical ability to perform in real time general video game domains.
+Referenced the design of the GA that shows validity in its theoretical to perform in real time general video game domains.
+The production of the \emph{VariGA} was to better adapt GA to the grid based world after observing the GA struggling to navigate.
+Whilst neither AI proved able to solve the puzzle element of the domain, this served to show differences between MCTS and the GA techniques.
+A* was considered to have too high a branching factor in this problem but was decided to be investigated in future work.
 
@@
 Could these not be implemented?}}
+A simple 1+1 ES would not be able to find a good solution within the time limits of real time video games.
+Macro Actions has been proven to vastly improve the ability of GA's to solve complex real time problems such as in Perez et al \cite{perez2013rolling}.
+A* was considered to have too high a branching factor in this problem but was decided to be investigated in future work.
 \paragraph*{\textit{More than once the idea of a language through which to communicate is discussed, but it has no real impact on this paper and should really be saved for when it is explored}}

### 2015-08-05 Report/response.tex
Removed bit about 1+1 ES as wasn't in the paper

@@
 \paragraph*{\textit{there is some mixup with agents being labeled 0 and 1 in the figures, but 1 and 2 in the text.}}
+That section has been removed due to another comment that we received and so the mixup is gone.
 

### 2015-08-05 Report/ceec.tex
Removed bit about 1+1 ES as wasn't in the paper

@@
 \paragraph{Macro Action Genetic Algorithm}
-The \gls{ga} algorithm was selected for its simplicity and had Macro Actions added in order to improve the forward search capability.
+The \gls{ga} algorithm was selected for its simplicity and had Macro Actions added in order to improve the forward search capability as well as the amount of computation time per decision available to it.
 The \gls{maga} used a population size of 10 and tournament selection of 3.
@@
 The primary premise was to allow the \gls{ga} to evolve the individual macro action lengths and the length of the overall sequence (number of macro actions).
-The main technique used was a 1 + 1 ES.
+The main technique used was a 1 + 1 Evolutionary Strategy.
+A 1 + 1 ES is a very simple \gls{ga} that maintains a single candidate, and in each iteration a mutation is made and if it is an improvement it is saved as the new best candidate.
+It is discarded if it is not an improvement.
+ES's are often much simpler than full gls{ga} algorithms to create, often require much less memory and due to performing less within each iteration is able to use more of the available time budget than a full gls{ga}.
 The algorithm was bounded by a number of parameters that are shown in Figure \ref{vmagaTable}.

### 2015-08-05 Report/stats-processing/coop-process.R
re-ordered columns to make reviewers happy

@@ -1,4 +1,4 @@
-setwd("C:\\Users\\joseph\\Documents\\GitHub\\TinyCoop\\Report\\stats-processing")
+setwd("/home/webpigeon/Documents/TinyCoop/Report/stats-processing")
 library(ggplot2)
 require(data.frame)
 
@@ -52,11 +52,18 @@ build_summary_map_score <- function (x) {
 build_graph <- function (filename, title, s) {
 	summary(s)
 	png(filename, width = 900, height = 500, units="px")
+	order <- c("GAController",
+	                      "VariGA",
+	                      "MCTS: (75;3;15)",
+	                      "MCTS: (200;5;30)",
+	                      "MCTS: (500;10;45)",
+	                      "RandomController")
 	p = ggplot(s, aes(x = agent1, y = mean)) +  
   	geom_bar(position = position_dodge(), stat="identity", fill="blue") + 
   	geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem)) +
   	ggtitle(title) + 
   	theme_bw() +
+	  scale_x_discrete(limits = order) +
   	theme(panel.grid.major = element_blank())
 	print(p)
 	invisible(dev.off())

### 2015-08-05 Report/response.tex

@@
 \paragraph*{\textit{What does 1+1 ES mean?}}
+The paper has been expanded to include a brief description of the 1+1 ES technique.
 \paragraph*{\textit{I did not quite understand how your MCTS works with multiple agents. Are you running independent simulations for each agent (I assume yes but it was not clear)? }}
+Yes, each agent was running independent simulations.
+It has been made clearer in the paper that none of the agents have the ability to communicate with another agent, and that each agent is controlled by a single controller.
 \paragraph*{\textit{I would like to see results for mixed agent teams.}}

### 2015-08-05 Report/ceec.tex

@@
 Then the top \emph{Agent} could collect the reward and allow the bottom \emph{Agent} access to the \emph{Goal}.}
-\item{\emph{level6.txt} This map was a new map - with two rooms each with a \emph{Goal} and a door.This was designed to force each \emph{Agent} to be let into the \emph{Goal} room, and out of it again.}
+\item{\emph{level6.txt} This map was a new map - with two rooms each with a \emph{Goal} and a door.
+This was designed to force each \emph{Agent} to be let into the \emph{Goal} room, and out of it again.}
 \end{itemize}
@@
 \subsubsection{\gls{ai} Controllers}
-A small set of \gls{ai} Controllers were created in order to attempt to solve the problem domain. None of the agents have the ability to communicate with another agent.
+A small set of \gls{ai} Controllers were created in order to attempt to solve the problem domain.
+None of the agents have the ability to communicate with another agent and each agent has a single controller.
 \paragraph{Random}

### 2015-08-05 Report/ceec.tex
Many changes

@@
 \gls{ggp} is the field of writing \gls{ai} agents that can play a multitude of games without being written specifically for each one individually \cite{genesereth2005general}.
-\gls{ggp} in real time video games is a popular competition \cite{perez2014}
+\gls{ggp} in real time video games is a popular competition \cite{perez2014}.
 
@@
 
-\gls{mcts} \cite{browne2012survey} has been applied to a wealth of domains and is one of the primary algorithms in use for \gls{ggp}\cite{finnsson2008simulation}.
+\gls{mcts} is a tree search algorithm originally designed by R{\'e}mi Coulom \cite{coulom2007efficient} and the major modification of \gls{uct} was defined by Kocsis and Szepesv{\'a}ri \cite{kocsis2006bandit} and improved by Kocsis et al \cite{kocsis2006improved}.
+
+\gls{mcts} \cite{browne2012survey} has been applied to a wealth of domains and is one of the primary algorithms in use for \gls{ggp} \cite{finnsson2008simulation}.
 Primary advantages are that, when given a sufficient forward model, \gls{mcts} doesn't require any strategic knowledge about the game itself in order to play.
@@
 A framework for communication would be devised - with the requirement for fairly \gls{ggp} like restrictions in mind.
+Use of the communication framework would need to likely be learned by the \emph{Agents} during play, posing a particular challenge for the future.
 

### 2015-08-05 Report/stats-processing/coop-process.R
agent1 -> agent in axis

@@ -63,7 +63,7 @@ build_graph <- function (filename, title, s) {
   	geom_errorbar(aes(ymin=mean-sem, ymax=mean+sem)) +
   	ggtitle(title) + 
   	theme_bw() +
-	  scale_x_discrete(limits = order) +
+	  scale_x_discrete(limits = order, name="Agent") +
   	theme(panel.grid.major = element_blank())
 	print(p)
 	invisible(dev.off())
@@ -76,14 +76,14 @@ games.raw <- read.csv(file="combined.csv", head=TRUE,sep=",")
 samePairs.raw = games.raw[games.raw$agent1==games.raw$agent2,]
 samePairs.scores <- build_summary_score(samePairs.raw)
 samePairs.ticks <- build_summary_ticks(samePairs.raw)
-build_graph("scores-samepairs.png", "All agents paired with themselves", samePairs.scores)
-build_graph("ticks-samepairs.png", "All agents paired with themselves", samePairs.ticks)
+build_graph("scores-samepairs.png", "Scores for all agents paired with themselves across all maps", samePairs.scores)
+build_graph("ticks-samepairs.png", "Ticks for all agents paired with themselves across all maps", samePairs.ticks)
 
 # build RR graphs for all agents
 games.scores <- build_summary_score(games.raw)
 games.ticks <- build_summary_ticks(games.raw)
-build_graph("scores-allmaps.png", "Scores across all maps for all agents", games.scores)
-build_graph("ticks-allmaps.png", "Ticks across all maps for all agents", games.ticks)
+build_graph("scores-allmaps.png", "Scores across all maps for each agent paired with all agents", games.scores)
+build_graph("ticks-allmaps.png", "Ticks across all maps for each agent paired with all agents", games.ticks)
 
 # build RR graphs for all agents with the maps as a 2nd dimention
 #games.maps.scores <- build_summary_map_score(games.raw)

### 2015-08-05 Report/response.tex

@@
 \paragraph*{\textit{The issue of communication, especially learning communication, is very important and I suggest you focus on this for future research.}}
+Have expanded the section in future work on communication to better reflect this.
 \subsection{Review 5 (Reviewer F)}
 \paragraph*{\textit{The early segments fail to really discuss the MCTS algorithm.  The abbreviation for this is also found in the abstract and should really be in the introductory paragraph.}}
+The MCTS algorithm was given some background in the literature as to its previous applications and a summary of its typical behaviour.
+Have added a small section describing its creation and referenced the key papers for that.
+Have removed the abbreviation for MCTS from the abstract.
 \paragraph*{\textit{Section II covering preliminary tests is light on technical details and seem ill placed when you consider the subsequent studies later on in the paper.}}

### 2015-08-05 Report/response.tex
Worked on the introduction with co-operative games

@@
 The introduction starts by discussing general game playing (which is not a main topic of the paper) and then presents MCTS (which is) but the discussion of cooperative games is missing.}}
+Added section on co-operative games.
 
@@
 \paragraph*{\textit{I would like to see results for mixed agent teams.}}
+Figures 6 and 7 have been retitled to better show that they were results for mixed agent teams.
 \paragraph*{\textit{The issue of communication, especially learning communication, is very important and I suggest you focus on this for future research.}}

### 2015-08-05 Report/ceec.tex
Worked on the introduction with co-operative games

@@
 \newacronym{ai}{AI}{Artificial Intelligence}
+\newacronym{fps}{FPS}{First-Person Shooter}
+\newacronym{rts}{RTS}{Real-Time Strategy}
+\newacronym{rpg}{RPG}{Role-Playing Game}
 
@@
 \gls{ggp} in real time video games is a popular competition \cite{perez2014}.
+
+Games that feature co-operation of some form between human players and \gls{ai} agents are commonplace.
+Most however feature very limited forms of co-operation that are typically scripted such as in most \gls{fps} games.
+Typically \gls{fps} games give the mere impression of co-operation, though any player that looks carefully at it will see the tell tale signs of scripting.
+Where \gls{fps} games typically excel at co-operation is in online modes that enable teams of humans to play against each other.
+Some games even provide squad structures and communication allowing direct command for the purpose of better co-ordination as in Battlefield 2142 \cite{battlefield2142}.
+\gls{rts} games also often have a small number of features designed to facilitate communication in a bid to facilitate co-operation.
+Two games that stand out for co-operation are Microsoft's Rise of Nations \cite{riseofnations} and Mad Doc Software's Empire Earth 2 \cite{empireEarth2}.
+Rise of Nations allowed a human and \gls{ai} player to operate the same set of units and buildings, though no communication was possible at all.
+This allowed a form of co-operation but the \gls{ai} operated to its own agenda.
+Empire Earth 2 allowed for humans and \gls{ai} agents to co-operate by letting plans be drawn up between them that could also be followed by both the human and \gls{ai} agent.
+These allowed a fairly complex set of instructions to be created, despite the simple interface.
+
+A highly popular game that had an entire mode designed for co-operation between humans was Valve's Portal 2 \cite{portal2}.
+This featured human sized lab test mazes with elements that required players to work together by activating buttons, moving cubes and using intra-dimensional portals to get to the end goal.
+Both players were required to reach the goal in order to complete the level.
 

### 2015-08-05 Report/response.tex
Answered many comments

@@
 Either remove this sentence or reword it.}}
+Removed.
 
@@
 }}
+The explanations behind the two agents have been improved, and proper optimisation is a potential candidate for future work in this problem domain.
 \paragraph*{\textit{There should be a separate subsection for the results.}}
+There is a separate section for results, with a sub-section of discussion about each AI agent's performance.
 \paragraph*{\textit{In figures 4--9 the 3 MCTS players are ordered in an odd order Meduin-Large-Small.
@@
 It seems that columns are organized automatically in alphabetical order they should be ordered in a way that makes sense.}}
+The graphs have been re-ordered to a more logical ordering.
 \paragraph*{\textit{Regarding the fact that players were trained assuming a random strategy was controlling the other player: This is mentioned again in the section, but a reasoning for this decision is not given.
@@
 Doesn't it make sense to assume a better than random strategy for the other player?}}
+Assuming a random strategy was chosen due to the availability only of agents that could play generally.
+Whilst nesting these could enhance play, it comes at a significant computational cost and must in the case of GGP feature a very simple or Random player at the base of the stack.
+Random is exceedingly fast to calculate, and provides the ability for techniques like MCTS to sample how its behaviour works almost regardless of what the other agent does.
+This gives it the ability to make moves that it believes would help a worst case scenario player - something that in this problem domain is likely to also help a more intelligent player.
 

### 2015-08-06 Report/response.tex
Added line in response about the reviewers

@@
 \section{Response to the reviewers}
+We would like to thank the reviewers for their insightful comments, that have truly enabled us to make many improvements to this paper.
+
 We have placed the reviewers comments in \textit{\textbf{Italics and Bold}} and our response to those comments in plain text.
@@
 \paragraph*{\textit{The writing is generally good, I only noticed one actual error "GGP[3]", but the tone is casual and a lot of inappropriately subjective comments are made}}
+Have placed a space between GGP and the reference.
 \paragraph*{\textit{The authors make a few dubious claims in the Introduction.
@@
 }}
-Have clarified the definition of GGP with reference to this paper\cite{genesereth2005general} and the terminology used to define MCTS use of knowledge. 
+Have clarified the definition of GGP with reference to this paper\cite{genesereth2005general} and the terminology used to define MCTS's use of knowledge.
 \paragraph*{\textit{The authors claim that MCTS works best when it is given rewards frequently. What is the evidence for this claim?}}
@@
 At the moment, the exact contributions are a bit hard to see.}}
+A discussion sub-section has been added to the Results section, and provides an analysis of the different AI techniques performance in general.
 \paragraph*{\textit{The list of references is short (four) and does not include any references to work on cooperative agents, swarm behaviour, etc.}}
+The references have been expanded, although not yet to cover co-operative agents.
+Swarm behaviour and co-operative agents are not possible in this domain due to the enforced lack of communication between \emph{Agents}, and was deemed outside of the scope for the Introduction.
+Future work mentions extensions of communication, which could allow a swarm technique or co-operative agents to be implemented.
+
 \subsection{Review 3 (Reviewer G)}
 \paragraph*{\textit{Who created this problem domain?}}
-We have clarified who created the problem domain.
+We have clarified who created the problem domain, it was the authors of the papers (Can't tell you who though just yet).
 \paragraph*{\textit{The agents move simultaneously or alternately?}}
@@
 \paragraph*{\textit{In what sense this domain interesting compared to other domains?}}
+We feel that this problem domain is interesting due to placing each agent that is typically designed to solve problems by themselves in an environment where they must rely on another agent performing certain sequences of actions.
+To quote the words of Reviewer F \textit{This proves to be an interesting reward space to explore, given that we are dealing with circumstances where players need to take action then await the outcome courtesy of another player}.
+The domain also gains an interesting aspect when we consider the ability to, in a slowed down pace, allow human players to potentially communicate with a more advanced AI in order to improve performance in the domain.
+Communication within computer games is something that we believe would improve the feelings of immersion that the player feels.
 
@@
 \paragraph*{\textit{What is the reward of the rollout? Maybe the raw score?}}
+The reward of the rollout was indeed the raw score that the game calculates. No additional heuristics were used as very little information was available to the agents from the forward model.
 \paragraph*{\textit{About the results, what is averaged?
@@
 Can we assume it plays perfectly well?}}
+The round robin tournament has been better explained, with numbers, at the beginning of the Tournament sub-section.
+We have removed the definition for the keyboard AI as it was never used in the experiment and was largely used for manual testing and investigation.
 \paragraph*{\textit{Please cite something about (1+1)-ES}}
@@
 both agents are the same.}}
+The forward model does only provide the ability to simulate an action pair(One for each agent) and get a true score based on that action pair.
+The forward model can be forwarded up to the tick limit or if the game is completed.
+There is no way to determine the presence of in-game objects other than potentially the \emph{Goal} due to its effect on score.
 \paragraph*{\textit{I don't think GA is suitable for this domain.

### 2015-08-06 Report/response.tex
Put most of the changed text into the responses

@@
 We have placed the reviewers comments in \textit{\textbf{Italics and Bold}} and our response to those comments in plain text.
+Quoted sections of text from the paper may include references to papers - these are listed at the end of this response.
 
@@
 We have added a definition for the \emph{Floor}.
+
+``\emph{Floor - } Floors are passable, and are rendered in Grey.''
 \paragraph*{\textit{In the definition of 'Walls' the word 'Walls' appears instead of 'Doors'.}}
 We have corrected the typo in the definition of \emph{Walls} in the problem domain section.
+
+``\emph{Walls -} Walls are impassable, and are fixed in position. \emph{Walls} are rendered in Black.''
 \paragraph*{\textit{When specifying that closed 'Doors' are blue there should be mention of the color of open 'Doors' (I assume gray).}}
 We have changed the description of \emph{Doors} to better reflect what they look like when open.
+
+``\emph{Doors} are rendered in Blue when closed, and are invisible when open.''
 \paragraph*{\textit{It is unclear if 'Door' closes again when agent on button moves on (or, alternatively, if walking onto a 'Button' effectively destroy the 'Door').}}
 We have improved the definition for \emph{Door} in order to make it clearer that the \emph{Door} closes again when the \emph{Buttons} are no longer activated.
+
+``\emph{Doors -} Doors can either be open or closed.
+When open, the door is passable.
+When closed, the door is impassable.
+Doors are open whilst an \emph{Agent} is activating a linked \emph{Button}.
+If the \emph{Agent} stops activating the \emph{Button} the \emph{Door} will close.''
 \paragraph*{\textit{Since 'Agents' are described as dark yellow, and since there are only two shades of yellow used, it would be wiser to describe a 'Goal' as rendered in bright yellow.}}
 We have reworded the definition of \emph{Goal} to better describe the colour in relation to \emph{Agents}.
+
+``\emph{Agents -} Agents are the moving objects that can activate buttons and the goal. \emph{Agents} are rendered in dark Yellow''
 \paragraph*{\textit{the sentence "Agent 1 reached an item like this -Agent 2 would seemingly gain some purpose and typically head for the other items." is poorly worded and not very informative.
@@
 The explanations behind the two agents have been improved, and proper optimisation is a potential candidate for future work in this problem domain.
+
+``The GA algorithm was selected for its simplicity and had Macro Actions added in order to improve the forward search capability as well as the amount of computation time per decision available to it.
+The MAGA used a population size of 10 and tournament selection of 3.
+Each candidate was a string of 15 actions - with each action performed 3 times in a row.
+This meant the MAGA could "see" 45 ticks in the future.
+The design of the MAGA algorithm was inspired by \textit{Perez et al} \cite{perez2013rolling}''
 \paragraph*{\textit{There should be a separate subsection for the results.}}
-There is a separate section for results, with a sub-section of discussion about each AI agent's performance.
+There is a separate section for results (Section III) , with a sub-section of discussion about each AI agent's performance.
 \paragraph*{\textit{In figures 4--9 the 3 MCTS players are ordered in an odd order Meduin-Large-Small.
@@
 Have rewritten this to point out that MCTS can't provide anything but random if it isn't given enough time or depth to search to a state that provides a reward.
+
+``Standard MCTS plays best when it is able to search far enough to locate states that provide a reward.
+MCTS tends to stumble when the time or search depth limit given to it isn't sufficient to allow it to locate any sequence of actions that provides a reward in order to differentiate the root's children \cite{perez2012monte}.
+When MCTS can't find any single state that contained a reward, all children of the node will contain identical values and the algorithm will be forced to make a random choice.''
 \paragraph*{\textit{The research problem is stated, but should be stated more clearly in the Introduction.}}
 Added at the beginning of the introduction a clear statement of the research problem.
+
+``This research problem that this paper will asses is how GGP agents perform when trying to solve a simple co-operative problem, with a focus on MCTS.''
 \paragraph*{\textit{"MCTS can charge off achieving its own goals": it seems odd to describe an algorithm as "charging off".}}
 Reworded.
+
+``Unlike other domains where MCTS can solve tasks at its own pace and by itself ...''
 \paragraph*{\textit{"This proves that the challenge...": no it doesn't, it indicates it.}}
 Reworded to indicates.
+
+11This indicates that the challenge of the task is high ...''
 \paragraph*{\textit{"The shockingly good results...": too casual and subjective, overstating the case.}}
 Reworded.
+
+``Figure \ref{avgScoreAllMaps} shows the average score that each AI Agent achieved over all the maps.
+The two more powerful MCTS Agents performed the best, doing much better than the competition.
+Figure \ref{avgTicksAllMaps} shows a similar result, with the more powerful Agents typically completing the maps in fewer ticks.
+\emph{RandomController} is the only deviant here - it outperformed the GA's in score but was worse in average ticks.
+Comparing the AI \emph{Agents} when paired only with themselves in Figure \ref{avgScorePairAllMaps} and Figure \ref{avgTicksPairAllMaps}.
+The good results for \emph{RandomController} are potentially due to the fact that the 3 MCTS controllers and 2 GA algorithms all based their decisions on having Random as an accomplice.''
+
 \paragraph*{\textit{There is no Discussion as such, rather there are subjective appraisals of the algorithm's performance at each task scattered throughout the results.
@@
 \paragraph*{\textit{The list of references is short (four) and does not include any references to work on cooperative agents, swarm behaviour, etc.}}
-The references have been expanded, although not yet to cover co-operative agents.
+The references have been expanded.
 Swarm behaviour and co-operative agents are not possible in this domain due to the enforced lack of communication between \emph{Agents}, and was deemed outside of the scope for the Introduction.
@@
 We have clarified who created the problem domain, it was the authors of the papers (Can't tell you who though just yet).
+
+``We created the following problem domain that is a simple grid world consisting of various objects:''
 \paragraph*{\textit{The agents move simultaneously or alternately?}}
 Added a section to highlight this.
+
+``Each \emph{Agent} is able to make a single action in each game tick.
+The actions are polled from each \emph{Agent} that is given the state of the game.
+When every \emph{Agent} has returned an action, the game is updated with these actions.
+The actions are implemented sequentially, if two \emph{Agents} return actions that result in occupying the same space, the \emph{Agent} with the lowest ID number will succeed while the other \emph{Agent} will fail and execute a \emph{No-Op}.''
 \paragraph*{\textit{Do agents see all areas of the problem?}}
 We have clarified how the problem domain handles observability and what information the \emph{Agents} have access to.
+
+``The \emph{Agents} are provided with a forward model, that allows simulation of potential moves up to the end of the game.
+The \emph{Agents} are not allowed to directly query any information about the game state other than the score at any given state (current or simulated).''
 \paragraph*{\textit{If an agent reaches a goal, is it known to the other agents?}}
@@
 
+``All \emph{Agents} are aware of the current score achieved, and therefore can calculate if a \emph{Goal} is reached.''
+
 \paragraph*{\textit{In what sense this domain interesting compared to other domains?}}
 We feel that this problem domain is interesting due to placing each agent that is typically designed to solve problems by themselves in an environment where they must rely on another agent performing certain sequences of actions.
-To quote the words of Reviewer F \textit{This proves to be an interesting reward space to explore, given that we are dealing with circumstances where players need to take action then await the outcome courtesy of another player}.
+To quote the words of Reviewer F ``\textit{This proves to be an interesting reward space to explore, given that we are dealing with circumstances where players need to take action then await the outcome courtesy of another player}''.
 The domain also gains an interesting aspect when we consider the ability to, in a slowed down pace, allow human players to potentially communicate with a more advanced AI in order to improve performance in the domain.
@@
 
+``\begin{itemize}
+\item{\emph{Left} - This will move the \emph{Agent} one grid square to the left. (-1, 0)}
+\item{\emph{Right} - This will move the \emph{Agent} one grid square to the right. (1, 0)}
+\item{\emph{Up} - This will move the \emph{Agent} one grid square up. (0, -1)}
+\item{\emph{Down} - This will move the \emph{Agent} one grid square down. (0, 1)}
+\item{\emph{No-Op} - This will not move the \emph{Agent}. It will remain in the same location as the previous game state.}
+\end{itemize}''
+
 \paragraph*{\textit{What is "Uniform Cost applied to Trees"? Is it something similar to the famous "Upper Confidence bound applied to Trees"? If not, please cite something.}}
@@
 Reworded to more used terminology.
+
+``The MCTS controller is a simple implementation of UCT - with a fixed number of rollouts, UCT tree search depth limit and rollout border.
+The rollout border is how far in total, the forward model will be allowed to progress before the game is evaluated.''
 \paragraph*{\textit{What is the reward of the rollout? Maybe the raw score?}}
@@
 We have corrected the typo in the definition of \emph{Walls} in the problem domain section.
+
+``\emph{Walls -} Walls are impassable, and are fixed in position. \emph{Walls} are rendered in Black.''
 \subsection{Review 4 (Reviewer B)}
@@
 \paragraph*{\textit{I did not understand the terms "UCT border" and "rollout border". Explain them. Are they related to "Max UCT" and "Max Rollout" in Fig. 2 ?}}
-Both have been reworded to a more used set of terminology.
+Both have been reworded to a more used set of terminology. The reworded section is shown above in R3's comments.
 \paragraph*{\textit{What does 1+1 ES mean?}}
@@
 It has been made clearer in the paper that none of the agents have the ability to communicate with another agent, and that each agent is controlled by a single controller.
+
+``None of the agents have the ability to communicate with another agent and each agent has a single controller.''
 \paragraph*{\textit{I would like to see results for mixed agent teams.}}
@@
 Have expanded the section in future work on communication to better reflect this.
+
+``More work can be conducted in the writing of AI's to use communication in order to complete these challenges better amongst themselves.
+A framework for communication would be devised - with the requirement for fairly GGP like restrictions in mind.
+Use of the communication framework would need to likely be learned by the \emph{Agents} during play, posing a particular challenge for the future.''
 \subsection{Review 5 (Reviewer F)}

### 2015-08-06 Report/ceec.tex
Added line in response about the reviewers
Put most of the changed text into the responses

@@
 \subsection{Tournament}
-For the main data collection, we ran a round robin tournament of maps and Agents.
+For the main data collection, we ran a round robin tournament of maps and Agents. Each Agent was paired with all 7 Agents (including a copy of itself) and played X games on each of the 7 maps.
 
@@
 \subsubsection{\gls{ai} Controllers}
-A small set of \gls{ai} Controllers were created in order to attempt to solve the problem domain.
+A set of \gls{ai} Controllers were created in order to attempt to solve the problem domain.
 None of the agents have the ability to communicate with another agent and each agent has a single controller.
@@
 The random controller simply chooses one of the possible 5 actions. This is one of the simplest to implement and run.
+\begin{comment}
 \paragraph{Keyboard}
 The keyboard controller takes input from the keyboard and translates that into a single Action. Once an action is polled, it is reset to the No Op action unless the keyboard is used again. 
+\end{comment}
 \paragraph{\gls{mcts}}

### 2015-08-06 Report/response.tex
Pictures made for each level

@@
 The explanations behind the two agents have been improved, and proper optimisation is a potential candidate for future work in this problem domain.
+We appreciate the reviewer's comment regarding the poor performance of the algorithm, and it could be possibly eliminated however, we have decided to keep this algorithm in the paper as a comparison, in order to show the improvements obtained when using variable macro-actions (VMAGA).
 
@@
 It seems that columns are organized automatically in alphabetical order they should be ordered in a way that makes sense.}}
-The graphs have been re-ordered to a more logical ordering.
+The graphs have been re-ordered to a more logical ordering. The new ordering is the two GA's, followed by the three MCTS algorithms in increasing order of budget and then finally random.
 \paragraph*{\textit{Regarding the fact that players were trained assuming a random strategy was controlling the other player: This is mentioned again in the section, but a reasoning for this decision is not given.
@@
 \paragraph*{\textit{Please cite something about (1+1)-ES}}
+We have added a citation:
+
+``The main technique used was a 1 + 1 Evolutionary Strategy \cite{t.back2000evolutionary-co}.''
+
 \paragraph*{\textit{If all information is visible to the agents,
@@
 \paragraph*{\textit{The third page could do with being structured better.  The charts are ill-placed, do not help the flow of the authors argument and need better captions.}}
+We have made efforts to improve the layout of the entire paper.
 \paragraph*{\textit{The paper would benefit from showing the actual levels used as part of the testing.

### 2015-08-06 Report/ceec.tex
Pictures made for each level

@@
 \usepackage{verbatim}
+\usepackage{array}
 
@@
 
+\subsection{MCTS}
+
 \gls{mcts} is a tree search algorithm originally designed by R{\'e}mi Coulom \cite{coulom2007efficient} and the major modification of \gls{uct} was defined by Kocsis and Szepesv{\'a}ri \cite{kocsis2006bandit} and improved by Kocsis et al \cite{kocsis2006improved}.
+
+\gls{mcts} is a tree search algorithm that in games is typically applied directly to the action space.
+\gls{mcts} requires the ability to simulate action sequences and retrieve at least some form of reward (or lack of) from the results of these simulations.
+The basic steps for \gls{mcts} are:
+
+\begin{enumerate}
+\item{\emph{Selection} - Selection is the stage where the algorithm navigates the search tree, selecting optimal nodes(Based on the tree policy) until it reaches a leaf node.}
+\item{\emph{Expansion} - Expansion is the stage whereby the leaf node is expanded by adding one of the remaining child states if it is not a terminal node.}
+\item{\emph{Simulation} - Simulation is the stage where the algorithm forwards the model until a result is achieved.
+Their is usually a policy that defines how the simulation is made, with the simplest being random possible moves.}
+\item{\emph{Backpropagation} - Backpropagation is the stage where the results of the simulation are propagated up the tree, so that they can influence the selection phase.}
+\end{enumerate}
 
@@
 Unlike other domains where \gls{mcts} can solve tasks at its own pace and by itself, this domain requires the agents to sometimes sit patiently on a button for another \emph{Agent} to do something else.
+
+We feel that this creates a very interesting problem domain, due to the reward space for each \emph{Agent} being tied to the activities of other \emph{Agents}.
 \begin{comment}
@@
 \subsection{Tournament}
-For the main data collection, we ran a round robin tournament of maps and Agents. Each Agent was paired with all 7 Agents (including a copy of itself) and played X games on each of the 7 maps.
+For the main data collection, we ran a round robin tournament of maps and Agents. Each Agent was paired with all 7 Agents (including a copy of itself) and played 47 games on each of the 7 maps.
 
@@
 For the tournament, three parameter sets were chosen for comparison and are shown in Figure \ref{mctsTable}.
-\begin{figure}[h]
-\centering
-\begin{tabular}{| l | c | c | c |}
+\begin{table}[!t]
+\begin{center}
+\begin{tabular}{|p{2.0cm}|p{2.0cm}|m{1.4cm}|m{1.4cm}|}
 \hline
@@
 \label{mctsTable}
-\end{figure}
+\end{center}
+\end{table}
 
@@
 The primary premise was to allow the \gls{ga} to evolve the individual macro action lengths and the length of the overall sequence (number of macro actions).
-The main technique used was a 1 + 1 Evolutionary Strategy.
+The main technique used was a 1 + 1 Evolutionary Strategy \cite{t.back2000evolutionary-co}.
 A 1 + 1 ES is a very simple \gls{ga} that maintains a single candidate, and in each iteration a mutation is made and if it is an improvement it is saved as the new best candidate.

### 2015-08-06 src/FastGame/FastGameMain.java

@@ -37,7 +37,7 @@ public class FastGameMain {
         Controller c2 = arrows;
 //        Controller c2 = new NoOp();
 
-        CoopGame game = new CoopGame("data/maps/level5.txt");
+        CoopGame game = new CoopGame("data/maps/level6.txt");
 
         Viewer viewer = new Viewer(game);
         viewer.addKeyListener(wasd);

### 2015-08-06 Report/response.tex
Expanded the discussion

@@
 \paragraph*{\textit{it would be a good idea to give the maps meaningful names.}}
+This has been done.
+
+``\begin{itemize}
+\item{\emph{SingleDoor} This map is the same as the map in \ref{InitialState}}
+\item{\emph{Pathfinding} This map is the same as level1.txt but without the \emph{Doors} and \emph{Buttons}. This was to test the \emph{Agent's} ability to solve the simplest problem.}
+\item{\emph{SymmetricSingleDoor} This map was a modification of the level1.txt - making the map more symmetric and the action parts closer together.}
+\item{\emph{ExtendedSide} This map was an extension of level1.txt with a second \emph{Goal} and some extra walls in the game.
+Spreading the action parts away from the door and buttons was the main purpose of this one}
+\item{\emph{SideBySide} This map was a modification of level1.txt - putting a second \emph{Goal} in and making the map partly mirrored.
+Each \emph{Agent} began in a separate room to each other instead of together.}
+\item{\emph{Airlock} This map was a new map, designed to give wildly different roles to each AI - the top Agent would have to travel through two doors (Like an airlock) that the bottom agent had access to the linked \emph{Buttons}.
+Then the top \emph{Agent} could collect the reward and allow the bottom \emph{Agent} access to the \emph{Goal}.}
+\item{\emph{Butterfly} This map was a new map - with two rooms each with a \emph{Goal} and a door.
+This was designed to force each \emph{Agent} to be let into the \emph{Goal} room, and out of it again.}
+\end{itemize}''
+
 \paragraph*{\textit{The MAGA is not explained very well and seems hastily put together.
@@
 We have removed the definition for the keyboard AI as it was never used in the experiment and was largely used for manual testing and investigation.
+
+``For the main data collection, we ran a round robin tournament of maps and Agents. Each Agent was paired with all 7 Agents (including a copy of itself) and played 47 games on each of the 7 maps.''
 \paragraph*{\textit{Please cite something about (1+1)-ES}}

### 2015-08-06 Report/ceec.tex
Expanded the discussion

@@
 \usepackage{array}
-
+\usepackage{caption}
+\captionsetup{belowskip=12pt,aboveskip=4pt}
 \graphicspath{{stats-processing/}{stats-processing/data/maps/}}
@@
 \begin{itemize}
-\item{\emph{level1.txt} This map is the same as the map in \ref{InitialState}}
-\item{\emph{level1E.txt} This map is the same as level1.txt but without the \emph{Doors} and \emph{Buttons}. This was to test the \emph{Agent's} ability to solve the simplest problem.}
-\item{\emph{level2.txt} This map was a modification of the level1.txt - making the map more symmetric and the action parts closer together.}
-\item{\emph{level3.txt} This map was an extension of level1.txt with a second \emph{Goal} and some extra walls in the game.
+\item{\emph{SingleDoor} This map is the same as the map in \ref{InitialState}}
+\item{\emph{Pathfinding} This map is the same as level1.txt but without the \emph{Doors} and \emph{Buttons}. This was to test the \emph{Agent's} ability to solve the simplest problem.}
+\item{\emph{SymmetricSingleDoor} This map was a modification of the level1.txt - making the map more symmetric and the action parts closer together.}
+\item{\emph{ExtendedSide} This map was an extension of level1.txt with a second \emph{Goal} and some extra walls in the game.
 Spreading the action parts away from the door and buttons was the main purpose of this one}
-\item{\emph{level4.txt} This map was a modification of level1.txt - putting a second \emph{Goal} in and making the map partly mirrored.
+\item{\emph{SideBySide} This map was a modification of level1.txt - putting a second \emph{Goal} in and making the map partly mirrored.
 Each \emph{Agent} began in a separate room to each other instead of together.}
-\item{\emph{level5.txt} This map was a new map, designed to give wildly different roles to each AI - the top Agent would have to travel through two doors that the bottom agent had access to the linked \emph{Buttons}.
+\item{\emph{Airlock} This map was a new map, designed to give wildly different roles to each AI - the top Agent would have to travel through two doors (Like an airlock) that the bottom agent had access to the linked \emph{Buttons}.
 Then the top \emph{Agent} could collect the reward and allow the bottom \emph{Agent} access to the \emph{Goal}.}
-\item{\emph{level6.txt} This map was a new map - with two rooms each with a \emph{Goal} and a door.
+\item{\emph{Butterfly} This map was a new map - with two rooms each with a \emph{Goal} and a door.
 This was designed to force each \emph{Agent} to be let into the \emph{Goal} room, and out of it again.}
@@
 
-For the tournament, three parameter sets were chosen for comparison and are shown in Figure \ref{mctsTable}.
+For the tournament, three parameter sets were chosen for comparison and are shown in Table \ref{mctsTable}.
 \begin{table}[!t]
@@
 It is discarded if it is not an improvement.
-ES's are often much simpler than full gls{ga} algorithms to create, often require much less memory and due to performing less within each iteration is able to use more of the available time budget than a full gls{ga}.
-The algorithm was bounded by a number of parameters that are shown in Figure \ref{vmagaTable}.
-
-\begin{figure}[h]
-\centering
+ES's are often much simpler than full gls{ga} algorithms to create, often require much less memory and due to performing less within each iteration is able to use more of the available time budget than a full \gls{ga}.
+The algorithm was bounded by a number of parameters that are shown in Table \ref{vmagaTable}.
+\begin{table}[!t]
+\begin{center}
 \begin{tabular}{| l | l | l |}
@@
 \label{vmagaTable}
-\end{figure}
+\end{center}
+\end{table}
 These values need extensive tuning to realise the full potential of the algorithm and is a source of possible future work.
-\pagebreak
 \section{Results}
@@
 \includegraphics[width=\linewidth]{level1E-txt-pairs-ticks}
-\caption{Average ticks taken to complete level1E.txt when paired only with identical Agents}
+\caption{Average ticks taken to complete \emph{Pathfinding} when paired only with identical Agents}
 \label{1epairedTicks}
@@
 \includegraphics[width=\linewidth]{level1-txt-pairs-ticks}
-\caption{Average ticks taken to complete level1.txt when paired only with identical Agents}
+\caption{Average ticks taken to complete \emph{SingleDoor} when paired only with identical Agents}
 \label{1pairedTicks}
@@
 
-\pagebreak
 \begin{figure}[!ht]
@@
 \includegraphics[scale=0.5]{level5}
-\caption{The initial starting state for level5.txt}
+\caption{The initial starting state for \emph{SideBySide}}
 \label{Level5State}
@@
 \includegraphics[width = \linewidth]{level5-txt-scores}
-\caption{Average Score for each AI Agent over Map 5}
+\caption{Average Score for each AI Agent over \emph{SideBySide}}
 \label{avgScoreMap5}
@@
 Figure \ref{avgScorePairAllMaps} showed that the medium and high budget implementations scored significantly better than all other agents.
+
+One possible reason for \gls{mcts} scoring so well in this problem domain is its use of statistics over hundreds and thousands of simulations to provide it with the ability to act in such a way that it handles all eventualities.
+Statistically,  in certain situations \gls{mcts} would only see rewards in the tree when it was situated on a \emph{Button}.
+This tended to cause the \gls{mcts} to travle towards \emph{Buttons}, increasing the likelihood that its own simulations would cause it to be situated on the button.
+Eventually, most other \gls{ai} \emph{Agents} would cross through the open door.
 \subsubsection{GA}
@@
 The ability to mutate the lengths of individual action sequences made the \emph{VariGA} a more flexible pathfinder that the \emph{GAController} but did not aid its ability to solve the co-operative problems present elsewhere in the experiment.
+
+The \gls{ga} algorithms don't have the stored tree structure of \gls{mcts} with which to gain the statistical model for what happens when they pursue certain actions.
+This leads to a seemingly poor performance for the \gls{ga} despite \gls{ga} and \gls{mcts} typically performing equally well in other domains.
 \subsubsection{Random}

### 2015-08-06 Report/response.tex
Addded images to the thing, answered question about random and createed experiment to do so

@@
 
+\paragraph*{\textit{Is there a time limit for solving the problem? I think, if given infinite time, random agent can always solve level1 and the average score should be 1.0.
+When and how do agents fail to solve a problem?}}
+The time limit for the problem was 2,000 ticks.
+Given infinite time, random agent can always solve any level.
+Some experiments (100,000 runs per level) showed a pair of random agents took on average this many ticks to complete each level:
+
+\begin{tabular}{|l|l|c|}
+\hline
+\textbf{Old Map Name} & \textbf{New Map Name} & \textbf{Avg Ticks to complete} \\
+\hline
+level1.txt & SingleDoor & 7250\\
+\hline
+level1E.txt & Pathfinder & 419\\
+\hline
+level2.txt & SymmetricSingleDoor & 7353\\
+\hline
+level3.txt & ExtendedSide& 13416\\
+\hline
+level4.txt & SideBySide & 7302\\
+\hline
+level5.txt & Airlock & \\
+\hline
+level6.txt & Butterfly & \\
+\hline
+\end{tabular}
+
 \paragraph*{\textit{Is the problem domain a real time problem?

### 2015-08-06 Report/ceec.tex
Addded images to the thing, answered question about random and createed experiment to do so

@@
 \usepackage{caption}
+\usepackage{float}
 \captionsetup{belowskip=12pt,aboveskip=4pt}
@@
 
-The starting positions for a simple problem is shown in Figure \ref{InitialState}
-\begin{figure}[ht]
-\centering
-\includegraphics[scale=0.5]{InitialState}
-\caption{Simple game state showing the different elements\protect\footnotemark }
-\label{InitialState}
-\end{figure}
-
-\footnotetext{Displayed numbers are the ID numbers - \emph{Button} ID 0 will open \emph{Door} ID 0 but not \emph{Door} ID 1}
 All levels are defined by a simple text file format.
@@
 The 7 maps that were included in the tournament were as follows:
-\begin{itemize}
-\item{\emph{SingleDoor} This map is the same as the map in \ref{InitialState}}
-\item{\emph{Pathfinding} This map is the same as level1.txt but without the \emph{Doors} and \emph{Buttons}. This was to test the \emph{Agent's} ability to solve the simplest problem.}
-\item{\emph{SymmetricSingleDoor} This map was a modification of the level1.txt - making the map more symmetric and the action parts closer together.}
-\item{\emph{ExtendedSide} This map was an extension of level1.txt with a second \emph{Goal} and some extra walls in the game.
-Spreading the action parts away from the door and buttons was the main purpose of this one}
-\item{\emph{SideBySide} This map was a modification of level1.txt - putting a second \emph{Goal} in and making the map partly mirrored.
-Each \emph{Agent} began in a separate room to each other instead of together.}
-\item{\emph{Airlock} This map was a new map, designed to give wildly different roles to each AI - the top Agent would have to travel through two doors (Like an airlock) that the bottom agent had access to the linked \emph{Buttons}.
-Then the top \emph{Agent} could collect the reward and allow the bottom \emph{Agent} access to the \emph{Goal}.}
-\item{\emph{Butterfly} This map was a new map - with two rooms each with a \emph{Goal} and a door.
-This was designed to force each \emph{Agent} to be let into the \emph{Goal} room, and out of it again.}
-\end{itemize}
+
+\paragraph{\emph{SingleDoor}} This map is a basic map with two rooms, single door and a button either side.
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.35]{InitialState}
+\caption{Single Door \protect\footnotemark}
+\label{SingleDoor}
+\end{figure}
+\footnotetext{Displayed numbers are the ID numbers - \emph{Button} ID 0 will open \emph{Door} ID 0 but not \emph{Door} ID 1}
+\paragraph{\emph{Pathfinding}} This map is the same as level1.txt but without the \emph{Doors} and \emph{Buttons}. This was to test the \emph{Agent's} ability to solve the simplest problem.
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.35]{level1e}
+\caption{Pathfinding}
+\label{Pathfinding}
+\end{figure}
+\paragraph{\emph{SymmetricSingleDoor}} This map was a modification of the level1.txt - making the map more symmetric and the action parts closer together.
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.35]{level2}
+\caption{Symmetric Single Door}
+\label{SymmetricSingleDoor}
+\end{figure}
+\paragraph{\emph{ExtendedSide}} This map was an extension of level1.txt with a second \emph{Goal} and some extra walls in the game.
+Spreading the action parts away from the door and buttons was the main purpose of this one.
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.35]{level3}
+\caption{Extended Side}
+\label{ExtendedSide}
+\end{figure}
+\paragraph{\emph{SideBySide}} This map was a modification of level1.txt - putting a second \emph{Goal} in and making the map partly mirrored.
+Each \emph{Agent} began in a separate room to each other instead of together.
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.35]{level4}
+\caption{Side By Side}
+\label{SideBySide}
+\end{figure}
+\paragraph{\emph{Airlock}} This map was a new map, designed to give wildly different roles to each AI - the top Agent would have to travel through two doors (Like an airlock) that the bottom agent had access to the linked \emph{Buttons}.
+Then the top \emph{Agent} could collect the reward and allow the bottom \emph{Agent} access to the \emph{Goal}.
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.35]{level5}
+\caption{Airlock}
+\label{Airlock}
+\end{figure}
+\paragraph{\emph{Butterfly}} This map was a new map - with two rooms each with a \emph{Goal} and a door.
+This was designed to force each \emph{Agent} to be let into the \emph{Goal} room, and out of it again.
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.35]{level6}
+\caption{Butterfly}
+\label{Butterfly}
+\end{figure}
 

### 2015-08-06 src/FastGame/FastGameMain.java

@@ -23,21 +23,21 @@ public class FastGameMain {
 
 //        Controller c1 = new MCTS(true, 1000, 10, 45);
 //        Controller c1 = new VariGA(true, 2000);
-//        Controller c1 = new RandomController();
+        Controller c1 = new RandomController();
 
 //        Controller c1 = new VariGA(true, 500);
-        //Controller c1 = new RandomController();
+//        Controller c1 = new RandomController();
 //          Controller c1 = new NoOp();
 
-        Controller c1 = wasd;
+//        Controller c1 = wasd;
 //        Controller c2 = new GAController(false);
 //        Controller c2 = new MCTS(false, 1000, 10, 45);
 //            Controller c2 = new VariGA(false, 2000);
-//        Controller c2 = new RandomController();
-        Controller c2 = arrows;
+        Controller c2 = new RandomController();
+//        Controller c2 = arrows;
 //        Controller c2 = new NoOp();
 
-        CoopGame game = new CoopGame("data/maps/level6.txt");
+        CoopGame game = new CoopGame("data/maps/level1.txt");
 
         Viewer viewer = new Viewer(game);
         viewer.addKeyListener(wasd);

### 2015-08-06 Report/response.tex
Added more data and repsonse for the random infinity
Finished loads

@@
 \section{Response to the reviewers}
+Dear Reviewers,
+
+Please find below our responses to your comments.
+
 We would like to thank the reviewers for their insightful comments, that have truly enabled us to make many improvements to this paper.
+We hope you will agree that the paper has matured into a quality that allows for publication.
 
@@
 Quoted sections of text from the paper may include references to papers - these are listed at the end of this response.
+
+Yours sincerely,
+
+The Authors.
 
@@
 Added section on co-operative games.
+
+``Games that feature co-operation of some form between human players and AI agents are commonplace.
+Most however feature very limited forms of co-operation that are typically scripted such as in most FPS games.
+Typically FPS games give the mere impression of co-operation, though any player that looks carefully at it will see the tell tale signs of scripting.
+Where FPS games typically excel at co-operation is in online modes that enable teams of humans to play against each other.
+Some games even provide squad structures and communication allowing direct command for the purpose of better co-ordination as in Battlefield 2142 \cite{battlefield2142}.
+RTS games also often have a small number of features designed to facilitate communication in a bid to facilitate co-operation.
+Two games that stand out for co-operation are Microsoft's Rise of Nations \cite{riseofnations} and Mad Doc Software's Empire Earth 2 \cite{empireEarth2}.
+Rise of Nations allowed a human and AI player to operate the same set of units and buildings, though no communication was possible at all.
+This allowed a form of co-operation but the AI operated to its own agenda.
+Empire Earth 2 allowed for humans and AI agents to co-operate by letting plans be drawn up between them that could also be followed by both the human and AI agent.
+These allowed a fairly complex set of instructions to be created, despite the simple interface.
+
+A highly popular game that had an entire mode designed for co-operation between humans was Valve's Portal 2 \cite{portal2}.
+This featured human sized lab test mazes with elements that required players to work together by activating buttons, moving cubes and using intra-dimensional portals to get to the end goal.
+Both players were required to reach the goal in order to complete the level.''
 
@@
 ``\begin{itemize}
-\item{\emph{SingleDoor} This map is the same as the map in \ref{InitialState}}
+\item{\emph{SingleDoor} This map is a basic map with two rooms, single door and a button either side.}
 \item{\emph{Pathfinding} This map is the same as level1.txt but without the \emph{Doors} and \emph{Buttons}. This was to test the \emph{Agent's} ability to solve the simplest problem.}
@@
 }}
-Have clarified the definition of GGP with reference to this paper\cite{genesereth2005general} and the terminology used to define MCTS's use of knowledge.
+Have clarified the definition of GGP and the terminology used to define MCTS's use of knowledge.
+
+``GGP is the field of writing AI agents that can play a multitude of games without being written specifically for each one individually \cite{genesereth2005general}.''
+
+``Standard MCTS plays best when it is able to search far enough to locate states that provide a reward.
+MCTS tends to stumble when the time or search depth limit given to it isn't sufficient to allow it to locate any sequence of actions that provides a reward in order to differentiate the root's children \cite{perez2012monte}.
+When MCTS can't find any single state that contained a reward, all children of the node will contain identical values and the algorithm will be forced to make a random choice.''
 \paragraph*{\textit{The authors claim that MCTS works best when it is given rewards frequently. What is the evidence for this claim?}}
@@
 
-11This indicates that the challenge of the task is high ...''
+``This indicates that the challenge of the task is high ...''
 \paragraph*{\textit{"The shockingly good results...": too casual and subjective, overstating the case.}}
@@
 \hline
-level5.txt & Airlock & \\
+level5.txt & Airlock & 12469\\
 \hline
-level6.txt & Butterfly & \\
+level6.txt & Butterfly & 10246\\
 \hline
 \end{tabular}
+
+These times are far too long for real time environment (40ms per tick gives an average solution time of nearly 7 minutes for Butterfly)
 
@@
 \paragraph*{\textit{The early segments fail to really discuss the MCTS algorithm.  The abbreviation for this is also found in the abstract and should really be in the introductory paragraph.}}
-The MCTS algorithm was given some background in the literature as to its previous applications and a summary of its typical behaviour.
-Have added a small section describing its creation and referenced the key papers for that.
+We have added a subsection in the Introduction that describes the MCTS algorithm much more fully than before.
 Have removed the abbreviation for MCTS from the abstract.
+
+``MCTS is a tree search algorithm originally designed by R{\'e}mi Coulom \cite{coulom2007efficient} and the major modification of UCT was defined by Kocsis and Szepesv{\'a}ri \cite{kocsis2006bandit} and improved by Kocsis et al \cite{kocsis2006improved}.
+
+MCTS is a tree search algorithm that in games is typically applied directly to the action space.
+MCTS requires the ability to simulate action sequences and retrieve at least some form of reward (or lack of) from the results of these simulations.
+The basic steps for MCTS are:
+
+\begin{enumerate}
+\item{\emph{Selection} - Selection is the stage where the algorithm navigates the search tree, selecting optimal nodes(Based on the tree policy) until it reaches a leaf node.}
+\item{\emph{Expansion} - Expansion is the stage whereby the leaf node is expanded by adding one of the remaining child states if it is not a terminal node.}
+\item{\emph{Simulation} - Simulation is the stage where the algorithm forwards the model until a result is achieved.
+Their is usually a policy that defines how the simulation is made, with the simplest being random possible moves.}
+\item{\emph{Backpropagation} - Backpropagation is the stage where the results of the simulation are propagated up the tree, so that they can influence the selection phase.}
+\end{enumerate}
+
+MCTS \cite{browne2012survey} has been applied to a wealth of domains and is one of the primary algorithms in use for GGP \cite{finnsson2008simulation}.
+Primary advantages are that, when given a sufficient forward model, MCTS doesn't require any strategic knowledge about the game itself in order to play.
+
+Standard MCTS plays best when it is able to search far enough to locate states that provide a reward.
+MCTS tends to stumble when the time or search depth limit given to it isn't sufficient to allow it to locate any sequence of actions that provides a reward in order to differentiate the root's children \cite{perez2012monte}.
+When MCTS can't find any single state that contained a reward, all children of the node will contain identical values and the algorithm will be forced to make a random choice.''
 \paragraph*{\textit{Section II covering preliminary tests is light on technical details and seem ill placed when you consider the subsequent studies later on in the paper.}}
@@
 Figure 10 should be shown much earlier in the paper.}}
+The description of each level has had an image of the initial starting state added, as well as being renamed. What was once Figure 10 has been removed due to that image now appearing earlier.
+
 \paragraph*{\textit{The selection of controller types does strike me as odd.
@@
 \paragraph*{\textit{More than once the idea of a language through which to communicate is discussed, but it has no real impact on this paper and should really be saved for when it is explored}}
+This has been removed.
 

### 2015-08-06 Report/ceec.tex
Finished loads

@@
 \section{Introduction}
-This research problem that this paper will asses is how \gls{ggp} agents perform when trying to solve a simple co-operative problem, with a focus on \gls{mcts}.
+This research problem that this paper will asses is how \gls{ggp} agents perform when trying to solve a simple co-operative problem without co-operative abilities, with a focus on \gls{mcts}.
 
@@
 This experiment tests how well current techniques can cope without specifically co-operating with each other.
-Agents that communicate slowly using a form of Natural Language, should in theory be able to work with human players equally well as they do with other Agents.
 
@@
 \includegraphics[width=\linewidth]{scores-allmaps}
-\caption{Average score of each AI Agent over all the Maps}
+\caption{Average score of each AI Agent over all pairings over all the Maps}
 \label{avgScoreAllMaps}
@@
 \includegraphics[width=\linewidth]{ticks-allmaps}
-\caption{Average Ticks taken for each AI Agent over all the Maps}
+\caption{Average Ticks taken for each AI Agent over all pairings over all the Maps}
 \label{avgTicksAllMaps}
@@
 \centering
-\includegraphics[scale=0.5]{level5}
-\caption{The initial starting state for \emph{SideBySide}}
-\label{Level5State}
-\end{figure}
-
-\begin{figure}[!ht]
-\centering
 \includegraphics[width = \linewidth]{level5-txt-scores}
-\caption{Average Score for each AI Agent over \emph{SideBySide}}
+\caption{Average Score for each AI Agent paired with itself over \emph{Airlock}}
 \label{avgScoreMap5}
@@
 
-Level 5 - shown in Figure \ref{Level5State} - poses a particular problem for many of the agents (see Figure \ref{avgScoreMap5}).
+Level 5 - shown in Figure \ref{Airlock} - poses a particular problem for many of the agents (see Figure \ref{avgScoreMap5}).
 The asymmetric nature of the level, and the delayed reward caused great difficulty for the Agents.

### 2015-08-14 Report/ceec.tex
Final version started

@@
 
-%\author{Piers R. Williams, \and Joseph Walton-Rivers}
+\author{Piers R. Williams, \and Joseph Walton-Rivers}
 
-\title{MCTS Applied to Co-operative Problems}
+\title{Monte Carlo Tree Search Applied to Co-operative Problems}
 
@@
 
-\newacronym{mcts}{MCTS}{Monte-Carlo Tree Search}
+\newacronym{mcts}{MCTS}{Monte Carlo Tree Search}
 \newacronym{uct}{UCT}{Upper Confidence bound applied to Trees}
@@
 \begin{abstract}
-This paper highlights an experiment to see how standard MCTS handles simple co-operative problems with no prior or provided knowledge.
+This paper highlights an experiment to see how standard Monte Carlo Tree Search handles simple co-operative problems with no prior or provided knowledge.
 These problems are formed from a simple grid world that has a set of goals, doors and buttons as well as walls that cannot be walked through.
@@
 When laid out correctly, the world requires each agent to do certain things at certain times in order to achieve the goal.
-With no modification to allow communication between the two Agents - MCTS performs well and performs very 'purposefully' when given enough computational time.
+With no modification to allow communication between the two Agents - Monte Carlo Tress Search performs well and performs very 'purposefully' when given enough computational time.
 \end{abstract}
@@
 \section{Introduction}
-This research problem that this paper will asses is how \gls{ggp} agents perform when trying to solve a simple co-operative problem without co-operative abilities, with a focus on \gls{mcts}.
+This research problem assessed in this paper is how \gls{ggp} agents perform when trying to solve a simple co-operative problem without co-operative abilities, with a focus on \gls{mcts}.
 
 \gls{ggp} is the field of writing \gls{ai} agents that can play a multitude of games without being written specifically for each one individually \cite{genesereth2005general}.
-\gls{ggp} in real time video games is a popular competition \cite{perez2014}.
+\gls{ggp} in real time video games has a popular competition \cite{perez2014} run frequently.
 
@@
 \gls{mcts} \cite{browne2012survey} has been applied to a wealth of domains and is one of the primary algorithms in use for \gls{ggp} \cite{finnsson2008simulation}.
-Primary advantages are that, when given a sufficient forward model, \gls{mcts} doesn't require any strategic knowledge about the game itself in order to play.
+Primary advantages are that, when given a sufficient forward model, \gls{mcts} does not require any strategic knowledge about the game itself in order to play.
 
 Standard \gls{mcts} plays best when it is able to search far enough to locate states that provide a reward.
-\gls{mcts} tends to stumble when the time or search depth limit given to it isn't sufficient to allow it to locate any sequence of actions that provides a reward in order to differentiate the root's children \cite{perez2012monte}.
-When \gls{mcts} can't find any single state that contained a reward, all children of the node will contain identical values and the algorithm will be forced to make a random choice.
+\gls{mcts} tends to stumble when the time or search depth limit given to it is not sufficient to allow it to locate any sequence of actions that provides a reward in order to differentiate the root's children \cite{perez2012monte}.
+When \gls{mcts} can not find any single state that contained a reward, all children of the node will contain identical values and the algorithm will be forced to make a random choice.
 
@@
 \footnotetext{Displayed numbers are the ID numbers - \emph{Button} ID 0 will open \emph{Door} ID 0 but not \emph{Door} ID 1}
-\paragraph{\emph{Pathfinding}} This map is the same as level1.txt but without the \emph{Doors} and \emph{Buttons}. This was to test the \emph{Agent's} ability to solve the simplest problem.
+\paragraph{\emph{Pathfinding}} This map is the same as \emph{SingleDoor} but without the \emph{Doors} and \emph{Buttons}. This was to test the \emph{Agent's} ability to solve the simplest problem.
 \begin{figure}[H]
@@
 \end{figure}
-\paragraph{\emph{SymmetricSingleDoor}} This map was a modification of the level1.txt - making the map more symmetric and the action parts closer together.
+\paragraph{\emph{SymmetricSingleDoor}} This map was a modification of the \emph{SingleDoor} - making the map more symmetric and the action parts closer together.
 \begin{figure}[H]
@@
 \end{figure}
-\paragraph{\emph{ExtendedSide}} This map was an extension of level1.txt with a second \emph{Goal} and some extra walls in the game.
+\paragraph{\emph{ExtendedSide}} This map was an extension of \emph{SingleDoor} with a second \emph{Goal} and some extra walls in the game.
 Spreading the action parts away from the door and buttons was the main purpose of this one.
@@
 \end{figure}
-\paragraph{\emph{SideBySide}} This map was a modification of level1.txt - putting a second \emph{Goal} in and making the map partly mirrored.
+\paragraph{\emph{SideBySide}} This map was a modification of \emph{SingleDoor} - putting a second \emph{Goal} in and making the map partly mirrored.
 Each \emph{Agent} began in a separate room to each other instead of together.
@@
 This greatly improves the ability of \gls{mcts} to make informed decisions.
-The score at the end of a rollout is taken from the game state - so if \gls{mcts} doesn't see any player reach a goal, all branches will be equal.
+The score at the end of a rollout is taken from the game state - so if \gls{mcts} does not see any player reach a goal, all branches will be equal.
 
@@
 It is discarded if it is not an improvement.
-ES's are often much simpler than full gls{ga} algorithms to create, often require much less memory and due to performing less within each iteration is able to use more of the available time budget than a full \gls{ga}.
+ES's are often much simpler than full \gls{ga} algorithms to create, often require much less memory and due to performing less within each iteration is able to use more of the available time budget than a full \gls{ga}.
 The algorithm was bounded by a number of parameters that are shown in Table \ref{vmagaTable}.
@@
 
-Level 5 - shown in Figure \ref{Airlock} - poses a particular problem for many of the agents (see Figure \ref{avgScoreMap5}).
+Airlock - shown in Figure \ref{Airlock} - poses a particular problem for many of the agents (see Figure \ref{avgScoreMap5}).
 The asymmetric nature of the level, and the delayed reward caused great difficulty for the Agents.
@@
 
-\subsection{Discussion}
-\subsubsection{MCTS}
+\section{Discussion}
+\subsection{MCTS}
 \gls{mcts} performed very well in this problem domain.
@@
 Eventually, most other \gls{ai} \emph{Agents} would cross through the open door.
-\subsubsection{GA}
+\subsection{GA}
 The two \gls{ga} algorithms did not perform very well in this problem domain.
@@
 As seen in Figure \ref{avgScorePairAllMaps} and Figure \ref{avgTicksPairAllMaps}, when tasked with solving the problem domain with another identical agent, neither the \emph{GAController} or \emph{VariGA} performed well at all.
-The \emph{VariGA} only performed significantly better than either \emph{RandomController} or \emph{GAController} in \emph{level1E.txt}.
+The \emph{VariGA} only performed significantly better than either \emph{RandomController} or \emph{GAController} in \emph{Pathfinding}.
 In all other cases, \emph{VariGA} performed similarly to the standard \emph{GAController}.
@@
 
-The \gls{ga} algorithms don't have the stored tree structure of \gls{mcts} with which to gain the statistical model for what happens when they pursue certain actions.
+The \gls{ga} algorithms do not have the stored tree structure of \gls{mcts} with which to gain the statistical model for what happens when they pursue certain actions.
 This leads to a seemingly poor performance for the \gls{ga} despite \gls{ga} and \gls{mcts} typically performing equally well in other domains.
-\subsubsection{Random}
+\subsection{Random}
 The \emph{RandomController} performed poorly in this problem domain. On average, the \emph{RandomController} finished under the 2000 tick limit and scored less than half the maximum on average.
@@
 The \emph{High MCTS} performed well - showing the power of having the correct parameters compared to the \emph{Low MCTS}.
-The \emph{VariGA} has 7 parameters that we simply didn't have time to correctly optimise for this experiment.
+The \emph{VariGA} has 7 parameters that we simply did not have time to correctly optimise for this experiment.
 

### 2015-10-04 report/abstract.tex
renamed folder to lowercase for linux

--- 2015-08-06 Report/ceec.tex
@@
 
-%\author{Piers R. Williams, \and Joseph Walton-Rivers}
+\author{Piers R. Williams, \and Joseph Walton-Rivers}
 
-\title{MCTS Applied to Co-operative Problems}
-
-\usepackage{graphicx}
-\usepackage{glossaries}
-\usepackage{verbatim}
-\usepackage{array}
-\usepackage{caption}
-\usepackage{float}
-\captionsetup{belowskip=12pt,aboveskip=4pt}
-\graphicspath{{stats-processing/}{stats-processing/data/maps/}}
-
-\newacronym{mcts}{MCTS}{Monte-Carlo Tree Search}
-\newacronym{uct}{UCT}{Upper Confidence bound applied to Trees}
-\newacronym{ggp}{GGP}{General Game Playing}
-\newacronym{ga}{GA}{Genetic Algorithm}
-\newacronym{mas}{MAS}{Multi-Agent Systems}
-\newacronym{maga}{MAGA}{Macro Action Genetic Algorithm}
-\newacronym{ai}{AI}{Artificial Intelligence}
-\newacronym{fps}{FPS}{First-Person Shooter}
-\newacronym{rts}{RTS}{Real-Time Strategy}
-\newacronym{rpg}{RPG}{Role-Playing Game}
+\title{MCTS Applied To Co-operative Problems}
 
@@
 \begin{abstract}
-This paper highlights an experiment to see how standard MCTS handles simple co-operative problems with no prior or provided knowledge.
-These problems are formed from a simple grid world that has a set of goals, doors and buttons as well as walls that cannot be walked through.
+An experiment to see how standard MCTS handles simple co-operative problems.	These problems are formed from a simple grid world that has a set of goals, doors and buttons as well as walls that cannot be walked through.
 Two agents have to each reach every goal present on the map.
@@
 
-\section{Introduction}
-This research problem that this paper will asses is how \gls{ggp} agents perform when trying to solve a simple co-operative problem without co-operative abilities, with a focus on \gls{mcts}.
-
-\gls{ggp} is the field of writing \gls{ai} agents that can play a multitude of games without being written specifically for each one individually \cite{genesereth2005general}.
-\gls{ggp} in real time video games is a popular competition \cite{perez2014}.
-
-Games that feature co-operation of some form between human players and \gls{ai} agents are commonplace.
-Most however feature very limited forms of co-operation that are typically scripted such as in most \gls{fps} games.
-Typically \gls{fps} games give the mere impression of co-operation, though any player that looks carefully at it will see the tell tale signs of scripting.
-Where \gls{fps} games typically excel at co-operation is in online modes that enable teams of humans to play against each other.
-Some games even provide squad structures and communication allowing direct command for the purpose of better co-ordination as in Battlefield 2142 \cite{battlefield2142}.
-\gls{rts} games also often have a small number of features designed to facilitate communication in a bid to facilitate co-operation.
-Two games that stand out for co-operation are Microsoft's Rise of Nations \cite{riseofnations} and Mad Doc Software's Empire Earth 2 \cite{empireEarth2}.
-Rise of Nations allowed a human and \gls{ai} player to operate the same set of units and buildings, though no communication was possible at all.
-This allowed a form of co-operation but the \gls{ai} operated to its own agenda.
-Empire Earth 2 allowed for humans and \gls{ai} agents to co-operate by letting plans be drawn up between them that could also be followed by both the human and \gls{ai} agent.
-These allowed a fairly complex set of instructions to be created, despite the simple interface.
-
-A highly popular game that had an entire mode designed for co-operation between humans was Valve's Portal 2 \cite{portal2}.
-This featured human sized lab test mazes with elements that required players to work together by activating buttons, moving cubes and using intra-dimensional portals to get to the end goal.
-Both players were required to reach the goal in order to complete the level.
-
-Creating \gls{ggp} agents that can co-operate with other players would open the door for more flexible agents in games that can work together with human players.
-This experiment tests how well current techniques can cope without specifically co-operating with each other.
-
-\subsection{MCTS}
-
-\gls{mcts} is a tree search algorithm originally designed by R{\'e}mi Coulom \cite{coulom2007efficient} and the major modification of \gls{uct} was defined by Kocsis and Szepesv{\'a}ri \cite{kocsis2006bandit} and improved by Kocsis et al \cite{kocsis2006improved}.
-
-\gls{mcts} is a tree search algorithm that in games is typically applied directly to the action space.
-\gls{mcts} requires the ability to simulate action sequences and retrieve at least some form of reward (or lack of) from the results of these simulations.
-The basic steps for \gls{mcts} are:
-
-\begin{enumerate}
-\item{\emph{Selection} - Selection is the stage where the algorithm navigates the search tree, selecting optimal nodes(Based on the tree policy) until it reaches a leaf node.}
-\item{\emph{Expansion} - Expansion is the stage whereby the leaf node is expanded by adding one of the remaining child states if it is not a terminal node.}
-\item{\emph{Simulation} - Simulation is the stage where the algorithm forwards the model until a result is achieved.
-Their is usually a policy that defines how the simulation is made, with the simplest being random possible moves.}
-\item{\emph{Backpropagation} - Backpropagation is the stage where the results of the simulation are propagated up the tree, so that they can influence the selection phase.}
-\end{enumerate}
-
-\gls{mcts} \cite{browne2012survey} has been applied to a wealth of domains and is one of the primary algorithms in use for \gls{ggp} \cite{finnsson2008simulation}.
-Primary advantages are that, when given a sufficient forward model, \gls{mcts} doesn't require any strategic knowledge about the game itself in order to play.
-
-Standard \gls{mcts} plays best when it is able to search far enough to locate states that provide a reward.
-\gls{mcts} tends to stumble when the time or search depth limit given to it isn't sufficient to allow it to locate any sequence of actions that provides a reward in order to differentiate the root's children \cite{perez2012monte}.
-When \gls{mcts} can't find any single state that contained a reward, all children of the node will contain identical values and the algorithm will be forced to make a random choice.
-
-\section{The Experiment}
-The main premise was to put \gls{mcts} in a situation where it would rely on other AI Agents in order to achieve its objectives, as well as provide a code base for further work with communication between \emph{Agents}.
-In order to do this, a problem domain was created.
-\subsection{The Problem Domain}
-We created the following problem domain that is a simple grid world consisting of various objects:
-\begin{itemize}
-\item{\emph{Floor - } Floors are passable, and are rendered in Grey.}
-\item{\emph{Walls -} Walls are impassable, and are fixed in position. \emph{Walls} are rendered in Black.}
-\item{\emph{Agents -} Agents are the moving objects that can activate buttons and the goal. \emph{Agents} are rendered in dark Yellow}
-\item{\emph{Doors -} Doors can either be open or closed.
-When open, the door is passable.
-When closed, the door is impassable.
-Doors are open whilst an \emph{Agent} is activating a linked \emph{Button}.
-If the \emph{Agent} stops activating the \emph{Button} the \emph{Door} will close.
-\emph{Doors} are rendered in Blue when closed, and are invisible when open.}
-\item{\emph{Buttons -} Buttons are passable, and when an \emph{Agent} is on the \emph{Button} it will activate and open the linked \emph{Door}. \emph{Buttons} are rendered in Red}
-\item{\emph{Goals -} Goals are passable and reward all \emph{Agents} with a portion of the score.
-All \emph{Goals} are worth the same amount and the maximum score of $1$ is achieved when every \emph{Agent} has visited every \emph{Goal} at least once.
-Re-visiting a \emph{Goal} has no effect.
-All \emph{Agents} are aware of the current score achieved, and therefore can calculate if a \emph{Goal} is reached.
-\emph{Goals} are rendered in Bright Yellow}
-\end{itemize}
-
-The \emph{Agents} are provided with a forward model, that allows simulation of potential moves up to the end of the game.
-The \emph{Agents} are not allowed to directly query any information about the game state other than the score at any given state (current or simulated).
-
-Each \emph{Agent} is able to make a single action in each game tick.
-The actions are polled from each \emph{Agent} that is given the state of the game.
-When every \emph{Agent} has returned an action, the game is updated with these actions.
-The actions are implemented sequentially, if two \emph{Agents} return actions that result in occupying the same space, the \emph{Agent} with the lowest ID number will succeed while the other \emph{Agent} will fail and execute a \emph{No-Op}.
-The available 5 actions are:
-\begin{itemize}
-\item{\emph{Left} - This will move the \emph{Agent} one grid square to the left. (-1, 0)}
-\item{\emph{Right} - This will move the \emph{Agent} one grid square to the right. (1, 0)}
-\item{\emph{Up} - This will move the \emph{Agent} one grid square up. (0, -1)}
-\item{\emph{Down} - This will move the \emph{Agent} one grid square down. (0, 1)}
-\item{\emph{No-Op} - This will not move the \emph{Agent}. It will remain in the same location as the previous game state.}
-\end{itemize}
-
-All levels are defined by a simple text file format.
-
-The problems are designed to require \emph{Agents} to co-operate in order to achieve their goals.
-Unlike other domains where \gls{mcts} can solve tasks at its own pace and by itself, this domain requires the agents to sometimes sit patiently on a button for another \emph{Agent} to do something else.
-
-We feel that this creates a very interesting problem domain, due to the reward space for each \emph{Agent} being tied to the activities of other \emph{Agents}.
-\begin{comment}
-\subsection{Initial Testing}
-Initially, observations were made to see how \gls{mcts} handled the problem.
-At first, with a small computational budget it seemed like \gls{mcts} would perform poorly, with near random movement seeming to emerge.
-
-This changed, when an agent (Agent 1 say) got near a \emph{Button} or \emph{Door}.
-When Agent 1 reached an item like this - Agent 2 would seemingly gain some purpose and typically head for the other items.
-When Agent 1 got on the \emph{Button}, Agent 2 would head straight through the open \emph{Door} and to the \emph{Goal}.
-Behaviour would then typically go back towards a more random approach, unless the Agent 1 got near the \emph{Door} - typically causing Agent 2 to head more purposefully towards the \emph{Button} that would allow Agent 1 to reach the \emph{Goal}.
-
-With this observation made - the computational budget was increased ten-fold, and the \gls{mcts} agents performed significantly better.
-Typical behaviour would be near optimal with significantly less random sections of movement.
-This can likely be attributed to the increased rollout and \gls{uct} border depths allowing more foresight on such a small puzzle.
-\end{comment}
-\subsection{Tournament}
-For the main data collection, we ran a round robin tournament of maps and Agents. Each Agent was paired with all 7 Agents (including a copy of itself) and played 47 games on each of the 7 maps.
-
-\subsubsection{Maps}
-The 7 maps that were included in the tournament were as follows:
-
-\paragraph{\emph{SingleDoor}} This map is a basic map with two rooms, single door and a button either side.
-\begin{figure}[H]
-\centering
-\includegraphics[scale=0.35]{InitialState}
-\caption{Single Door \protect\footnotemark}
-\label{SingleDoor}
-\end{figure}
-\footnotetext{Displayed numbers are the ID numbers - \emph{Button} ID 0 will open \emph{Door} ID 0 but not \emph{Door} ID 1}
-\paragraph{\emph{Pathfinding}} This map is the same as level1.txt but without the \emph{Doors} and \emph{Buttons}. This was to test the \emph{Agent's} ability to solve the simplest problem.
-\begin{figure}[H]
-\centering
-\includegraphics[scale=0.35]{level1e}
-\caption{Pathfinding}
-\label{Pathfinding}
-\end{figure}
-\paragraph{\emph{SymmetricSingleDoor}} This map was a modification of the level1.txt - making the map more symmetric and the action parts closer together.
-\begin{figure}[H]
-\centering
-\includegraphics[scale=0.35]{level2}
-\caption{Symmetric Single Door}
-\label{SymmetricSingleDoor}
-\end{figure}
-\paragraph{\emph{ExtendedSide}} This map was an extension of level1.txt with a second \emph{Goal} and some extra walls in the game.
-Spreading the action parts away from the door and buttons was the main purpose of this one.
-\begin{figure}[H]
-\centering
-\includegraphics[scale=0.35]{level3}
-\caption{Extended Side}
-\label{ExtendedSide}
-\end{figure}
-\paragraph{\emph{SideBySide}} This map was a modification of level1.txt - putting a second \emph{Goal} in and making the map partly mirrored.
-Each \emph{Agent} began in a separate room to each other instead of together.
-\begin{figure}[H]
-\centering
-\includegraphics[scale=0.35]{level4}
-\caption{Side By Side}
-\label{SideBySide}
-\end{figure}
-\paragraph{\emph{Airlock}} This map was a new map, designed to give wildly different roles to each AI - the top Agent would have to travel through two doors (Like an airlock) that the bottom agent had access to the linked \emph{Buttons}.
-Then the top \emph{Agent} could collect the reward and allow the bottom \emph{Agent} access to the \emph{Goal}.
-\begin{figure}[H]
-\centering
-\includegraphics[scale=0.35]{level5}
-\caption{Airlock}
-\label{Airlock}
-\end{figure}
-\paragraph{\emph{Butterfly}} This map was a new map - with two rooms each with a \emph{Goal} and a door.
-This was designed to force each \emph{Agent} to be let into the \emph{Goal} room, and out of it again.
-\begin{figure}[H]
-\centering
-\includegraphics[scale=0.35]{level6}
-\caption{Butterfly}
-\label{Butterfly}
-\end{figure}
-
-\subsubsection{\gls{ai} Controllers}
-A set of \gls{ai} Controllers were created in order to attempt to solve the problem domain.
-None of the agents have the ability to communicate with another agent and each agent has a single controller.
-\paragraph{Random}
-The random controller simply chooses one of the possible 5 actions. This is one of the simplest to implement and run.
-\begin{comment}
-\paragraph{Keyboard}
-The keyboard controller takes input from the keyboard and translates that into a single Action. Once an action is polled, it is reset to the No Op action unless the keyboard is used again. 
-\end{comment}
-\paragraph{\gls{mcts}}
-The \gls{mcts} controller is a simple implementation of \gls{uct} - with a fixed number of rollouts, \gls{uct} tree search depth limit and rollout border.
-The rollout border is how far in total, the forward model will be allowed to progress before the game is evaluated.
-No knowledge about the game is provided and the assumption is made that the other player will play randomly.
-The fixed rollout border makes a significant improvement in iterations per decision (from 1-3 to 500-600 in 40ms \footnote{Intel Core i5-3570, 8GB RAM, Windows 7 Enterprise 64bit}).
-This greatly improves the ability of \gls{mcts} to make informed decisions.
-The score at the end of a rollout is taken from the game state - so if \gls{mcts} doesn't see any player reach a goal, all branches will be equal.
-
-For the tournament, three parameter sets were chosen for comparison and are shown in Table \ref{mctsTable}.
-\begin{table}[!t]
-\begin{center}
-\begin{tabular}{|p{2.0cm}|p{2.0cm}|m{1.4cm}|m{1.4cm}|}
-\hline
-\textbf{Budget} & \textbf{Rollouts} & \textbf{UCT Search Limit} & \textbf{Rollout Border} \\
-\hline
-Small & 75 & 3 & 15 \\
-Medium & 200 & 5 & 30 \\
-High & 500 & 10 & 45 \\
-\hline
-\end{tabular}
-\caption{Table of parameters for the 3 \gls{mcts} players}
-\label{mctsTable}
-\end{center}
-\end{table}
-
-\paragraph{Macro Action Genetic Algorithm}
-The \gls{ga} algorithm was selected for its simplicity and had Macro Actions added in order to improve the forward search capability as well as the amount of computation time per decision available to it.
-The \gls{maga} used a population size of 10 and tournament selection of 3.
-Each candidate was a string of 15 actions - with each action performed 3 times in a row.
-This meant the \gls{maga} could "see" 45 ticks in the future.
-The design of the \gls{maga} algorithm was inspired by \textit{Perez et al} \cite{perez2013rolling}
-\paragraph{Variable Macro Action Genetic Algorithm}
-The Variable Macro Action \gls{ga} was created to try to solve the shortcomings of \gls{maga}.
-The primary premise was to allow the \gls{ga} to evolve the individual macro action lengths and the length of the overall sequence (number of macro actions).
-The main technique used was a 1 + 1 Evolutionary Strategy \cite{t.back2000evolutionary-co}.
-A 1 + 1 ES is a very simple \gls{ga} that maintains a single candidate, and in each iteration a mutation is made and if it is an improvement it is saved as the new best candidate.
-It is discarded if it is not an improvement.
-ES's are often much simpler than full gls{ga} algorithms to create, often require much less memory and due to performing less within each iteration is able to use more of the available time budget than a full \gls{ga}.
-The algorithm was bounded by a number of parameters that are shown in Table \ref{vmagaTable}.
-\begin{table}[!t]
-\begin{center}
-\begin{tabular}{| l | l | l |}
-\hline
-\textbf{Param} & \textbf{Controls} & \textbf{Value} \\
-\hline
-minNum & Number of Macro Actions & 3 \\
-MaxNum & Number of Macro Actions & 10 \\
-minLength & Length of Macro Actions & 1 \\
-maxLength & Length of Macro Actions & 5 \\
-numChance & Chance of altering Number & 0.25 \\
-lengthChance & Chance of altering each length & 0.8 \\
-actionChance & Chance of altering each action & 0.75 \\
-\hline
-\end{tabular}
-\caption{Table of parameters for the Variable Macro Action Genetic Algorithm}
-\label{vmagaTable}
-\end{center}
-\end{table}
-These values need extensive tuning to realise the full potential of the algorithm and is a source of possible future work.
-\section{Results}
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\linewidth]{level1E-txt-pairs-ticks}
-\caption{Average ticks taken to complete \emph{Pathfinding} when paired only with identical Agents}
-\label{1epairedTicks}
-\end{figure}
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\linewidth]{level1-txt-pairs-ticks}
-\caption{Average ticks taken to complete \emph{SingleDoor} when paired only with identical Agents}
-\label{1pairedTicks}
-\end{figure}
-
-Figure \ref{1epairedTicks} shows the ability of each Agent to solve a simple path finding problem.
-The \emph{GAcontroller}, with its macro actions, is hindered by its inability to make single step moves and has trouble actually walking straight to the target.
-The \emph{VariGA} does significantly better, due to its ability to perform single step moves.
-Figure \ref{1pairedTicks} shows that most of the controllers really struggle when the \emph{Door} and \emph{Buttons} are added.
-This indicates that the challenge of the task is high, although perhaps remarkable that \gls{mcts} is able to solve the task.
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\linewidth]{scores-allmaps}
-\caption{Average score of each AI Agent over all pairings over all the Maps}
-\label{avgScoreAllMaps}
-\end{figure}
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\linewidth]{ticks-allmaps}
-\caption{Average Ticks taken for each AI Agent over all pairings over all the Maps}
-\label{avgTicksAllMaps}
-\end{figure}
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\linewidth]{scores-samepairs}
-\caption{Average Scores for each AI Agent paired with itself over all the Maps}
-\label{avgScorePairAllMaps}
-\end{figure}
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\linewidth]{ticks-samepairs}
-\caption{Average Ticks taken for each AI Agent paired with itself over all the Maps}
-\label{avgTicksPairAllMaps}
-\end{figure}
-
-Figure \ref{avgScoreAllMaps} shows the average score that each AI Agent achieved over all the maps.
-The two more powerful \gls{mcts} Agents performed the best, doing much better than the competition.
-Figure \ref{avgTicksAllMaps} shows a similar result, with the more powerful Agents typically completing the maps in fewer ticks.
-\emph{RandomController} is the only deviant here - it outperformed the GA's in score but was worse in average ticks.
-Comparing the \gls{ai} \emph{Agents} when paired only with themselves in Figure \ref{avgScorePairAllMaps} and Figure \ref{avgTicksPairAllMaps}.
-The good results for \emph{RandomController} are potentially due to the fact that the 3 \gls{mcts} controllers and 2 \gls{ga} algorithms all based their decisions on having Random as an accomplice.
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width = \linewidth]{level5-txt-scores}
-\caption{Average Score for each AI Agent paired with itself over \emph{Airlock}}
-\label{avgScoreMap5}
-\end{figure}
-
-Level 5 - shown in Figure \ref{Airlock} - poses a particular problem for many of the agents (see Figure \ref{avgScoreMap5}).
-The asymmetric nature of the level, and the delayed reward caused great difficulty for the Agents.
-Relying on two button presses and the other agent to get through the open doors - in order - greatly reduced performance.
-The top agent, \emph{High MCTS}, only managed an average score of $0.44$ compared to its total average of just over $0.8$.
-
-\subsection{Discussion}
-\subsubsection{MCTS}
-\gls{mcts} performed very well in this problem domain.
-
-As seen above, in Figure \ref{avgTicksPairAllMaps}, the medium and high budget implementations provided the two quickest completion times across all maps.
-The differences shown were significant as well as being the only two agents to complete on average in under 1000 ticks.
-Figure \ref{avgScorePairAllMaps} showed that the medium and high budget implementations scored significantly better than all other agents.
-
-One possible reason for \gls{mcts} scoring so well in this problem domain is its use of statistics over hundreds and thousands of simulations to provide it with the ability to act in such a way that it handles all eventualities.
-Statistically,  in certain situations \gls{mcts} would only see rewards in the tree when it was situated on a \emph{Button}.
-This tended to cause the \gls{mcts} to travle towards \emph{Buttons}, increasing the likelihood that its own simulations would cause it to be situated on the button.
-Eventually, most other \gls{ai} \emph{Agents} would cross through the open door.
-\subsubsection{GA}
-The two \gls{ga} algorithms did not perform very well in this problem domain.
-
-As seen in Figure \ref{avgScorePairAllMaps} and Figure \ref{avgTicksPairAllMaps}, when tasked with solving the problem domain with another identical agent, neither the \emph{GAController} or \emph{VariGA} performed well at all.
-The \emph{VariGA} only performed significantly better than either \emph{RandomController} or \emph{GAController} in \emph{level1E.txt}.
-In all other cases, \emph{VariGA} performed similarly to the standard \emph{GAController}.
-The ability to mutate the lengths of individual action sequences made the \emph{VariGA} a more flexible pathfinder that the \emph{GAController} but did not aid its ability to solve the co-operative problems present elsewhere in the experiment.
-
-The \gls{ga} algorithms don't have the stored tree structure of \gls{mcts} with which to gain the statistical model for what happens when they pursue certain actions.
-This leads to a seemingly poor performance for the \gls{ga} despite \gls{ga} and \gls{mcts} typically performing equally well in other domains.
-\subsubsection{Random}
-The \emph{RandomController} performed poorly in this problem domain. On average, the \emph{RandomController} finished under the 2000 tick limit and scored less than half the maximum on average.
-\section{Conclusions}
-In this paper, we found that a strong MCTS player can solve simple cooperative problems without requiring communication between agents.
-We also found that a number of other \gls{ai} techniques experienced difficulty when the problem became cooperative.
-Further work is required in this area.
-
-\subsection{Further Work}
-There is scope for more work in a number of areas.
-
-\subsubsection{Communication}
-More work can be conducted in the writing of AI's to use communication in order to complete these challenges better amongst themselves.
-A framework for communication would be devised - with the requirement for fairly \gls{ggp} like restrictions in mind.
-Use of the communication framework would need to likely be learned by the \emph{Agents} during play, posing a particular challenge for the future.
-
-\subsubsection{Optimisations}
-Future work should also include some work to ensure that the \gls{ai} Agents have their parameters set correctly.
-The \emph{High MCTS} performed well - showing the power of having the correct parameters compared to the \emph{Low MCTS}.
-The \emph{VariGA} has 7 parameters that we simply didn't have time to correctly optimise for this experiment.
-
-\subsubsection{Problem Domain}
-More work can also be done on experimenting with the problem domain itself.
-Expanding the object types to include different techniques such as pickup-able objects that can be placed on \emph{Buttons}, \emph{Buttons} that remain active for a period of time after vacating them as well as potentially \emph{Doors} that will open permanently if all it's \emph{Buttons} are activated.
-The scope here is fairly limitless.
-
-\bibliographystyle{IEEEtran}
-\bibliography{ceec}
-
 \end{document}

### 2015-10-12 Report/ceec.tex
End of the report

@@
 \usepackage{float}
-\captionsetup{belowskip=12pt,aboveskip=4pt}
+\captionsetup{belowskip=8pt,aboveskip=4pt}
 \graphicspath{{stats-processing/}{stats-processing/data/maps/}}
@@
 
+The rest of this paper is structured as follows.
+Section II describes the problem and the experiment, including the \gls{ai} controllers that were used.
+Section III describes the results of the experiment and Section IV provides a discussion of the results.
+Section V concludes and introduces avenues of future research.
 \section{The Experiment}
@@
 
-The \emph{Agents} are provided with a forward model, that allows simulation of potential moves up to the end of the game.
+The \emph{Agents} are provided with a forward model, that allows simulation of potential action pairs up to the end of the game.
 The \emph{Agents} are not allowed to directly query any information about the game state other than the score at any given state (current or simulated).
+There is no way to determine the presence of in-game objects other than potentially the \emph{Goal} due to its effect on score.
 
@@
 
-We feel that this creates a very interesting problem domain, due to the reward space for each \emph{Agent} being tied to the activities of other \emph{Agents}.
+We feel that this creates a very interesting problem domain, due to placing each \emph{Agent} that is typically designed to solve problems by themselves in an environment where they must rely on another \emph{Agent} performing certain sequences of actions without being able to communicate that sequence or anything else.
 \begin{comment}
@@
 \section{Discussion}
+\subsection{Random Assumptions}
+The \gls{mcts} and \gls{ai} algorithms are required to run simulations of the game state in order to function.
+Even just a single look ahead of this problem domain requires the algorithm to make a selection of what the other play would do.
+In all cases, the assumption of a random strategy was chosen due to the availability only of agents that could play generally.
+Whilst nesting these could enhance play, as explored by Tristan Cazenave \cite{cazenave2007reflexive}, it comes at a significant computational cost and must in the case of \gls{ggp} feature a very simple or Random player at the base of the stack.
+Random is exceedingly fast to calculate, and provides the ability for techniques like \gls{mcts} to sample how its behaviour works almost regardless of what the other agent does.
+This gives \gls{mcts} the ability to make moves that it believes would help a worst case scenario player - something that in this problem domain is likely to also help a more intelligent player.
+When \gls{mcts} is sitting on the button, an intelligent player would go through the open door and a random player would eventually go through the door.
+\gls{mcts} even has the option of locking the random player on the other side, forcing it to eventually complete some other task.
+
 \subsection{MCTS}
@@
 The \emph{RandomController} performed poorly in this problem domain. On average, the \emph{RandomController} finished under the 2000 tick limit and scored less than half the maximum on average.
+
+\subsection{A* Search}
+A* search was considered to be unsuitable for this domain, as searching across the action space of two \emph{Agents} was far too high a branching factor. 
 \section{Conclusions}
-In this paper, we found that a strong MCTS player can solve simple cooperative problems without requiring communication between agents.
+In this paper, we found that a strong \gls{mcts} player can solve simple cooperative problems without requiring communication between agents.
 We also found that a number of other \gls{ai} techniques experienced difficulty when the problem became cooperative.
-Further work is required in this area.
+We hypothesised that \gls{mcts}'s use of a stored tree guiding its explorations (Something that \gls{ga}'s lack) was a major advantage in solving problems that rely on the other agent.
+\gls{ga}'s were found to perform poorly in the experiment, despite being capable of goal finding without the co-operative obstacles.
+Further work is required in this area to determine exactly why \gls{mcts} performs well.
 

### 2015-10-12 src/FastGame/FastGameMain.java

@@ -21,9 +21,9 @@ public class FastGameMain {
 
 //        Controller c1 = new GAController(true);
 
-//        Controller c1 = new MCTS(true, 1000, 10, 45);
+        Controller c1 = new MCTS(true, 500, 10, 45);
 //        Controller c1 = new VariGA(true, 2000);
-        Controller c1 = new RandomController();
+//        Controller c1 = new RandomController();
 
 //        Controller c1 = new VariGA(true, 500);
 //        Controller c1 = new RandomController();
@@ -31,13 +31,13 @@ public class FastGameMain {
 
 //        Controller c1 = wasd;
 //        Controller c2 = new GAController(false);
-//        Controller c2 = new MCTS(false, 1000, 10, 45);
+        Controller c2 = new MCTS(false, 500, 10, 45);
 //            Controller c2 = new VariGA(false, 2000);
-        Controller c2 = new RandomController();
+//        Controller c2 = new RandomController();
 //        Controller c2 = arrows;
 //        Controller c2 = new NoOp();
 
-        CoopGame game = new CoopGame("data/maps/level1.txt");
+        CoopGame game = new CoopGame("data/maps/level6.txt");
 
         Viewer viewer = new Viewer(game);
         viewer.addKeyListener(wasd);
@@ -53,7 +53,7 @@ public class FastGameMain {
         while (!game.hasWon()) {
             game.update(c1.get(game.getClone()), c2.get(game.getClone()));
             ticks++;
-//            Thread.sleep(40);
+            Thread.sleep(40);
             viewer.repaint();
         }
         System.out.println(ticks);

### 2015-10-14 report/response.tex
TImedButtons

--- 2015-08-06 Report/response.tex
@@
 
-``Figure \ref{avgScoreAllMaps} shows the average score that each AI Agent achieved over all the maps.
+``Figure 10 shows the average score that each AI Agent achieved over all the maps.
 The two more powerful MCTS Agents performed the best, doing much better than the competition.
-Figure \ref{avgTicksAllMaps} shows a similar result, with the more powerful Agents typically completing the maps in fewer ticks.
+Figure 11 shows a similar result, with the more powerful Agents typically completing the maps in fewer ticks.
 \emph{RandomController} is the only deviant here - it outperformed the GA's in score but was worse in average ticks.
-Comparing the AI \emph{Agents} when paired only with themselves in Figure \ref{avgScorePairAllMaps} and Figure \ref{avgTicksPairAllMaps}.
+Comparing the AI \emph{Agents} when paired only with themselves in Figure 12 and Figure 13.
 The good results for \emph{RandomController} are potentially due to the fact that the 3 MCTS controllers and 2 GA algorithms all based their decisions on having Random as an accomplice.''
@@
 
-\paragraph*{\textit{"Doors are rendered in Black." -> "Walls are rendered in Black."}}
+\paragraph*{\textit{"Doors are rendered in Black." $\rightarrow$ "Walls are rendered in Black."}}
 We have corrected the typo in the definition of \emph{Walls} in the problem domain section.

### 2015-10-14 src/Controllers/AStar.java

@@ -1,218 +1,0 @@
-package Controllers;
-
-import java.awt.Point;
-import java.util.*;
-
-import FastGame.Action;
-import FastGame.CoopGame;
-import FastGame.ObjectTypes;
-
-/**
- * An implementation of A* for path finding
- */
-public class AStar extends Controller {
-
-    public static Queue<FastGame.Action> getPath(CoopGame game, ActionNode start, boolean isFirst) {
-        int maxExpands = 25;
-
-        List<Point> goals = getGoals(game);
-
-        List<ActionNode> closedSet = new ArrayList<ActionNode>();
-        Map<ActionNode, ActionNode> cameFrom = new HashMap<>();
-        Map<ActionNode, Double> gScores = new HashMap<>();
-        Map<ActionNode, Double> fScores = new HashMap<>();
-        List<ActionNode> openSet = new ArrayList<ActionNode>();
-        openSet.add(start);
-
-        while(!openSet.isEmpty()) {
-            ActionNode current = openSet.get(0);
-            //System.out.println("open: "+openSet);
-            //System.out.println("closed: "+closedSet);
-            if (current.game.hasWon() || current.game.getScore() == 0.5) {
-                return buildPath(current, cameFrom, isFirst);
-            }
-            openSet.remove(current);
-            closedSet.add(current);
-
-            for (ActionNode neighbor : getAvailableMoves(current, isFirst)) {
-                if (closedSet.contains(neighbor)) {
-                    continue;
-                }
-                Double gScore = gScores.getOrDefault(current, 0.0);
-                gScore += 1; // 'cost' to get to this state
-
-                if ( !openSet.contains(neighbor) || gScore > gScores.getOrDefault(neighbor, 0.0) ) {
-                    cameFrom.put(neighbor, current);
-                    gScores.put(neighbor, gScore);
-                    fScores.put(neighbor, gScore + getDistance(neighbor, goals, isFirst));
-                    if (!openSet.contains(neighbor)) {
-                        openSet.add(neighbor);
-                    }
-                }
-            }
-        }
-
-        // we didn't find a path
-        return new LinkedList<FastGame.Action>();
-    }
-
-    public static List<Point> getGoals(CoopGame cg) {
-        List<Point> goals = new ArrayList<Point>();
-
-        for (int x=0; x<cg.getWidth(); x++) {
-            for (int y=0; y<cg.getHeight(); y++) {
[…]

### 2015-10-14 src/Controllers/ArrowController.java

@@ -1,29 +1,0 @@
-package Controllers;
-
-import java.awt.event.KeyEvent;
-
-/**
- * Created by pwillic on 30/06/2015.
- */
-public class ArrowController extends WASDController{
-
-    @Override
-    public void keyPressed(KeyEvent e) {
-        int keyCode = e.getKeyCode();
-        switch(keyCode){
-            case KeyEvent.VK_UP:
-                actionID = 4;
-                break;
-            case KeyEvent.VK_DOWN:
-                actionID = 1;
-                break;
-            case KeyEvent.VK_LEFT:
-                actionID = 2;
-                break;
-            case KeyEvent.VK_RIGHT:
-                actionID = 3;
-                break;
-        }
-//        System.out.println("Action Arrows: " + actions[actionID]);
-    }
-}

### 2015-10-14 src/Controllers/Controller.java

@@ -1,20 +1,0 @@
-package Controllers;
-
-import FastGame.Action;
-import FastGame.CoopGame;
-
-/**
- * Created by pwillic on 23/06/2015.
- */
-public abstract class Controller {
-
-    public Controller getClone() { return this; }
-
-    public Action get(CoopGame game) {
-        return Action.NOOP;
-    }
-
-    public String getSimpleName(){
-        return this.getClass().getSimpleName();
-    }
-}

### 2015-10-14 src/Controllers/MCTS.java

@@ -1,239 +1,0 @@
-package Controllers;
-
-import FastGame.Action;
-import FastGame.CoopGame;
-
-import java.util.Random;
-
-/**
- * Created by pwillic on 23/06/2015.
- */
-public class MCTS extends Controller {
-
-    protected Random random = new Random();
-    private int maxUCTDepth = 5;
-    private int maxRolloutDepth = 30;
-    private int iterationLimit = 0;
-
-    private boolean first;
-
-    public MCTS(boolean first, int iterationLimit, int maxUCTDepth, int maxRolloutDepth) {
-        this.first = first;
-        this.iterationLimit = iterationLimit;
-        this.maxUCTDepth = maxUCTDepth;
-        this.maxRolloutDepth = maxRolloutDepth;
-    }
-
-    public MCTS(boolean first, int iterationLimit){
-        this.first = first;
-        this.iterationLimit = iterationLimit;
-    }
-
-    @Override
-    public Action get(CoopGame game) {
-        MCTSNode root = new MCTSNode(2.0, this);
-        MCTSNode travel;
-        CoopGame workingGame;
-        int iterations = 0;
-        while (iterations < iterationLimit) {
-            workingGame = game.getClone();
-            travel = root.select(workingGame);
-            double result = travel.rollout(workingGame);
-            travel.updateValues(result);
-            iterations++;
-        }
-//        System.out.println("Iterations : " + iterations);
-//        System.out.println(root.getBestAction());
-        return root.getBestAction();
-    }
-
-    public int getMaxUCTDepth() {
-        return maxUCTDepth;
-    }
-
-    public int getMaxRolloutDepth() {
-        return maxRolloutDepth;
-    }
-
-    public boolean isFirst() {
-        return first;
-    }
-
-    @Override
-    public String getSimpleName() {
-        return "MCTS: (" + iterationLimit + ";" + maxUCTDepth + ";" + maxRolloutDepth + ")";
-    }
-}
-
-class MCTSNode {
-
-    private static final double EPSILON = 1e-6;
-
-    private double explorationConstant;
-    private Action moveToThisState;
-
-    private double totalValue;
-    private int numberOfVisits;
-    private int currentDepth;
-    private int childrenExpandedSoFar = 0;
-
-    private MCTSNode parent;
-    private MCTSNode[] children;
-    private int childLength = Action.allActions.length;
-
-    private MCTS mcts;
-
-    // Root
[…]

### 2015-10-14 src/Controllers/RandomController.java

@@ -1,15 +1,0 @@
-package Controllers;
-
-import FastGame.Action;
-import FastGame.CoopGame;
-
-/**
- * Created by pwillic on 30/06/2015.
- */
-public class RandomController extends Controller {
-
-    @Override
-    public Action get(CoopGame game) {
-        return Action.getRandom();
-    }
-}

### 2015-10-14 src/Controllers/VariGA/VariGA.java

@@ -1,265 +1,0 @@
-package Controllers.VariGA;
-
-import Controllers.Controller;
-import FastGame.Action;
-import FastGame.CoopGame;
-
-import java.util.Random;
-
-/**
- * Do a 1 + 1 ES
- * Created by Piers on 01/07/2015.
- */
-public class VariGA extends Controller {
-
-    private boolean first;
-    private int iterations;
-    private double numChance = 0.25;
-    private double lengthChance = 0.8;
-    private double actionChance = 0.75;
-    private ActionSequence currentBest;
-    private int currentUsage = 0;
-    private ActionSequence parent = getNewParent();
-    private double parentFitness;
-    private CoopGame fastForwardedGame;
-
-    private int[] params;
-
-    public VariGA(boolean first, int iterations) {
-        this.first = first;
-        this.iterations = iterations;
-    }
-
-    public VariGA(boolean first, int iterations, double[] chances, int[] params){
-        this(first, iterations);
-        numChance = chances[0];
-        lengthChance = chances[1];
-        actionChance = chances[2];
-        this.params = params;
-    }
-
-    public VariGA getClone(){
-        VariGA other = new VariGA(this.first, this.iterations);
-        other.params = this.params;
-        other.actionChance = this.actionChance;
-        other.lengthChance = this.lengthChance;
-        other.numChance = this.numChance;
-        return other;
-    }
-    // int minNum, int maxNum, int minLength, int maxLength
-    private ActionSequence getNewParent(){
-        if(params == null)  return new ActionSequence(3, 10, 1, 5);
-        return new ActionSequence(params[0], params[1], params[2], params[3]);
-    }
-
-    @Override
-    public Action get(CoopGame game) {
-        if (currentBest == null || currentUsage >= currentBest.getFirstActionLength()) {
-            currentBest = parent;
-            parent = null;
-            // Fast forward the fast forward to the right place
-            fastForwardedGame = game.getClone();
-            for(int i = 0 ;!fastForwardedGame.hasWon() &&  i < currentBest.getFirstActionLength(); i++){
-                if(first){
-                    fastForwardedGame.update(currentBest.getActionAt(i), Action.getRandom());
-                }else{
-                    fastForwardedGame.update(Action.getRandom(), currentBest.getActionAt(i));
-                }
-            }
-            currentUsage = 0;
-        }
-        calculate(game);
-//        System.out.println(currentBest);
-        if (currentBest == null) return Action.NOOP;
[…]

### 2015-10-14 src/Controllers/WASDController.java

@@ -1,52 +1,0 @@
-package Controllers;
-
-import FastGame.Action;
-import FastGame.CoopGame;
-
-import java.awt.event.KeyEvent;
-import java.awt.event.KeyListener;
-
-/**
- * Created by pwillic on 23/06/2015.
- */
-public class WASDController extends Controller implements KeyListener {
-    Action[] actions = new Action[]{Action.NOOP, Action.DOWN, Action.LEFT, Action.RIGHT, Action.UP};
-
-    int actionID = 0;
-
-    @Override
-    public Action get(CoopGame game) {
-        int id = actionID;
-        actionID = 0;
-        return actions[id];
-    }
-
-    @Override
-    public void keyTyped(KeyEvent e) {
-
-    }
-
-    @Override
-    public void keyPressed(KeyEvent e) {
-        switch (e.getKeyChar()) {
-            case 'a':
-                actionID = 2;
-                break;
-            case 's':
-                actionID = 1;
-                break;
-            case 'd':
-                actionID = 3;
-                break;
-            case 'w':
-                actionID = 4;
-                break;
-        }
-//        System.out.println("Action: " + actions[actionID]);
-    }
-
-    @Override
-    public void keyReleased(KeyEvent e) {
-
-    }
-}

### 2015-10-14 src/Controllers/astar/AStarBetter.java

@@ -1,52 +1,0 @@
-package Controllers.astar;
-
-import Controllers.AStar;
-import Controllers.Controller;
-import FastGame.Action;
-import FastGame.CoopGame;
-
-import java.util.List;
-
-/**
- * Created by jwalto on 02/07/2015.
- */
-public class AStarBetter extends Controller {
-    private PathFind find;
-    private boolean isFirst;
-    private MovePair lastMove;
-
-    public AStarBetter(boolean isFirst) {
-        this.find = new PathFind(new GameScore());
-        this.isFirst = isFirst;
-        this.lastMove = new MovePair(Action.NOOP, Action.NOOP);
-    }
-
-    @Override
-    public Controller getClone() {
-        AStarBetter btr = new AStarBetter(isFirst);
-        btr.lastMove = lastMove;
-        return btr;
-    }
-
-    @Override
-    public Action get(CoopGame game) {
-        System.out.println("requested move");
-        GameNode start = new GameNode(game, lastMove);
-        List<MovePair> pairs = find.getPath(game, start);
-
-        if (pairs.isEmpty()) {
-            System.out.println("Unable to find path, perform random");
-            return Action.getRandom();
-        }
-
-        if (pairs.size() == 1) {
-            System.out.println();
-            return Action.NOOP;
-        }
-
-        System.out.println(pairs);
-        // this assumes the move the opponent played last was the "perfect" move, but it probably wasn't.
-        lastMove = pairs.get(1);
-        return isFirst?lastMove.p1Move:lastMove.p2Move;
-    }
-}

### 2015-10-14 src/Controllers/astar/GameNode.java

@@ -1,58 +1,0 @@
-package Controllers.astar;
-
-import Controllers.ga.GA;
-import FastGame.Action;
-import FastGame.CoopGame;
-
-/**
- * Created by jwalto on 02/07/2015.
- */
-public class GameNode implements Comparable<GameNode> {
-    protected CoopGame game;
-    protected MovePair actions;
-
-    public GameNode(CoopGame game, MovePair actions) {
-        this.game = game;
-        this.actions = actions;
-    }
-
-    public boolean isTerminal() {
-        return game.hasWon() || game.getScore() == 1;
-    }
-
-    @Override
-    public int compareTo(GameNode o) {
-        return Double.compare(o.game.getScore(), game.getScore());
-    }
-
-    public boolean gameEquals(CoopGame us, CoopGame them) {
-        if (us.getScore() != them.getScore()) return false;
-        if (!us.getPos(0).equals(them.getPos(0))) return false;
-        if (!us.getPos(1).equals(them.getPos(1))) return false;
-        return true;
-    }
-
-    @Override
-    public boolean equals(Object o) {
-        if (this == o) return true;
-        if (o == null || getClass() != o.getClass()) return false;
-
-        GameNode gameNode = (GameNode) o;
-
-        if (!actions.equals(gameNode.actions)) return false;
-        if (!gameEquals(game, gameNode.game)) return false;
-
-        return true;
-    }
-
-    @Override
-    public int hashCode() {
-        int result = game.hashCode();
-        result = 31 * result + actions.hashCode();
-        return result;
-    }
-
-    public String toString() {
-        return actions.toString()+" "+game.getScore()+","+game.getPos(0)+","+game.getPos(1);
-    }
-}

### 2015-10-14 src/Controllers/astar/GameScore.java

@@ -1,24 +1,0 @@
-package Controllers.astar;
-
-import java.util.function.Function;
-
-/**
- * Created by jwalto on 02/07/2015.
- */
-public class GameScore implements Function<GameNode,Double> {
-
-    @Override
-    public Double apply(GameNode gameNode) {
-        return gameNode.game.getScore();
-    }
-
-    @Override
-    public <V> Function<V, Double> compose(Function<? super V, ? extends GameNode> before) {
-        return null;
-    }
-
-    @Override
-    public <V> Function<GameNode, V> andThen(Function<? super Double, ? extends V> after) {
-        return null;
-    }
-}

### 2015-10-14 src/Controllers/astar/PathFind.java

@@ -1,97 +1,0 @@
-package Controllers.astar;
-
-        import FastGame.Action;
-        import FastGame.CoopGame;
-
-        import java.awt.Point;
-        import java.util.*;
-        import java.util.function.Function;
-
-/**
- * An implementation of A* for path finding
- */
-public class PathFind {
-    private Function<GameNode, Double> heristic;
-    Map<GameNode, GameNode> cameFrom = new HashMap<>();
-    Map<GameNode, Double> gScores = new HashMap<>();
-    Map<GameNode, Double> fScores = new HashMap<>();
-
-    public PathFind(Function<GameNode, Double> heristic) {
-        this.heristic = heristic;
-    }
-
-    public List<MovePair> getPath(CoopGame game, GameNode start) {
-        List<GameNode> closedSet = new ArrayList<GameNode>();
-        Queue<GameNode> openSet = new PriorityQueue<GameNode>(new Comparator<GameNode>() {
-
-            @Override
-            public int compare(GameNode o1, GameNode o2) {
-                System.out.println(o1);
-                System.out.println(o2);
-                return Double.compare(fScores.getOrDefault(o1, 0.0),fScores.getOrDefault(o2, 0.0)) * -1;
-            }
-        });
-        openSet.add(start);
-
-        while(!openSet.isEmpty()) {
-            GameNode current = openSet.poll();
-            System.out.println(current);
-            if (current.isTerminal()) {
-                return buildPath(current, cameFrom);
-            }
-            openSet.remove(current);
-            closedSet.add(current);
-
-            for (MovePair moves : getAvailableMoves(game)) {
-                CoopGame nState = current.game.getClone();
-                nState.update(moves.p1Move, moves.p2Move);
-                GameNode neighbor = new GameNode(nState, moves);
-
-                if (closedSet.contains(neighbor)) {
-                    continue;
-                }
-                Double gScore = gScores.get(current);
-                if (gScore == null) {
-                    gScore = 0.0;
-                }
-                gScore += 1;
-
-                if ( !openSet.contains(neighbor) || gScore > gScores.getOrDefault(neighbor, 0.0) ) {
-                    cameFrom.put(neighbor, current);
-                    gScores.put(neighbor, gScore);
-                    fScores.put(neighbor, gScore + heristic.apply(neighbor));
-                    if (!openSet.contains(neighbor)) {
-                        openSet.add(neighbor);
-                    }
-                }
[…]

### 2015-10-14 src/Controllers/ga/GA.java

@@ -1,163 +1,0 @@
-package Controllers.ga;
-
-import FastGame.Action;
-import FastGame.CoopGame;
-
-import java.util.ArrayList;
-import java.util.Random;
-
-/**
- * PTSP-Competition
- * Created by Diego Perez, University of Essex.
- * Date: 17/10/12
- */
-public class GA
-{
-    public final int NUM_INDIVIDUALS = 10;
-    static public int NUM_ACTIONS_INDIVIDUAL = 15;
-    static public int TOURNAMENT_SIZE = 3;
-    public final int ELITISM = 2;
-    public ArrayList<MacroAction> m_actionList;             //List of available actions to govern the ship.
-    public Random m_rnd;                                    //Random number generator
-    public int m_numGenerations;
-
-    public GAIndividual[] m_individuals;
-
-    public GA()
-    {
-        m_rnd = new Random();
-
-        m_actionList = new ArrayList<MacroAction>();
-        for (Action action : Action.allActions) {
-            m_actionList.add(new MacroAction(action, GAConstants.MACRO_ACTION_LENGTH));
-        }
-
-        m_individuals = new GAIndividual[NUM_INDIVIDUALS];
-        //init(a_gameState);
-    }
-
-    public void init(CoopGame a_gameState, boolean first)
-    {
-        //System.out.println(" --------- Starting GA --------- ");
-        m_numGenerations = 0;
-        for(int i = 0; i < NUM_INDIVIDUALS; ++i)
-        {
-            m_individuals[i] = new GAIndividual(NUM_ACTIONS_INDIVIDUAL);
-            m_individuals[i].randomize(m_rnd, m_actionList.size());
-            m_individuals[i].evaluate(a_gameState, first);
-            //System.out.format("individual i: " + i + ", fitness: %.3f, actions: %s \n", m_individuals[i].m_fitness, m_individuals[i].toString());
-        }
-
-        sortPopulationByFitness();
-    }
-
-    public MacroAction run(CoopGame a_gameState, int generations, boolean first)
-    {
-        int currGen = 0;
-        while(currGen < generations)
-        {
-            GAIndividual[] nextPop = new GAIndividual[m_individuals.length];
-            //System.out.println(" --------- New generation " + m_numGenerations + " --------- ");
-
-            int i;
-            for(i = 0; i < ELITISM; ++i)
-            {
-                nextPop[i] = m_individuals[i];
-            }
-
-            for(;i<m_individuals.length;++i)
-            {
-                //System.out.println("######################");
[…]

### 2015-10-14 src/Controllers/ga/GAController.java

@@ -1,72 +1,0 @@
-package Controllers.ga;
-
-import Controllers.Controller;
-import FastGame.Action;
-import FastGame.CoopGame;
-
-/**
- * GA controller for CoopGame, modified from PTSP.
- *
- * Created by jwalto on 01/07/2015.
- */
-public class GAController extends Controller {
-    private static final Integer GENERATIONS = 10;
-    private static final MacroAction NOOP = new MacroAction(Action.NOOP, GAConstants.MACRO_ACTION_LENGTH);
-
-    private GA ga;
-    private boolean first;
-    private MacroAction currentAction;
-    private int macroPos;
-    private boolean reset;
-    private boolean startOfGame;
-
-    public GAController(boolean first) {
-        this.ga = new GA();
-        this.first = first;
-        this.currentAction = NOOP;
-        this.macroPos = 0;
-        this.reset = true;
-        this.startOfGame = true;
-    }
-
-    @Override
-    public Controller getClone() {
-        GAController other = new GAController(first);
-        return other;
-    }
-
-    @Override
-    public Action get(CoopGame game) {
-        MacroAction nextAction = NOOP;
-
-        if (startOfGame) {
-            currentAction = NOOP;
-            nextAction = currentAction;
-            reset = true;
-            macroPos = GAConstants.MACRO_ACTION_LENGTH-1;
-            startOfGame = false;
-        } else {
-            if (macroPos > 0) {
-                if (reset) {
-                    ga.init(game, first);
-                }
-                ga.run(game, GENERATIONS, first);
-                macroPos--;
-            } else if (macroPos == 0) {
-                nextAction = currentAction;
-                MacroAction gaBestAction = ga.run(game, GENERATIONS, first);
-                if (gaBestAction != null) {
-                    currentAction = gaBestAction;
-                }
-
-                if (currentAction != null) {
-                    macroPos = GAConstants.MACRO_ACTION_LENGTH - 1;
-                }
-                reset = true;
-            }
-        }
-
-
-        return nextAction.getAction();
-    }
-}

### 2015-10-14 src/Controllers/ga/GAIndividual.java

@@ -1,104 +1,0 @@
-package Controllers.ga;
-
-import FastGame.Action;
-import FastGame.CoopGame;
-
-import java.util.Random;
-
-/**
- * PTSP-Competition
- * Created by Diego Perez, University of Essex.
- * Date: 17/10/12
- */
-public class GAIndividual
-{
-    public Action[] m_genome;
-    public double m_fitness;
-    public final double MUTATION_PROB = 0.2; //0.834=5/6   //0.2;
-
-    public GAIndividual(int a_genomeLength)
-    {
-        m_genome = new Action[a_genomeLength];
-        m_fitness = 0;
-    }
-
-    public void randomize(Random a_rnd, int a_numActions)
-    {
-        for(int i = 0; i < m_genome.length; ++i)
-        {
-            m_genome[i] = Action.getRandom();
-        }
-    }
-
-    public CoopGame evaluate(CoopGame a_gameState, boolean isFirst)
-    {
-        CoopGame thisGameCopy = a_gameState.getClone();
-        boolean end = false;
-        for(int i = 0; i < m_genome.length; ++i)
-        {
-            Action thisAction = m_genome[i];
-            for(int j =0; !end && j < GAConstants.MACRO_ACTION_LENGTH; ++j)
-            {
-                if (isFirst) {
-                    thisGameCopy.update(thisAction, Action.getRandom());
-                } else {
-                    thisGameCopy.update(Action.getRandom(), thisAction);
-                }
-                end = thisGameCopy.hasWon();
-            }
-        }
-        m_fitness = thisGameCopy.getScore();
-        return thisGameCopy;
-    }
-
-    public void mutate(Random a_rnd)
-    {
-        for (int i = 0; i < m_genome.length; i++) {
-            if(a_rnd.nextDouble() < MUTATION_PROB)
-            {
-                m_genome[i] = Action.getRandom();
-            }
-        }
-    }
-
-    /**
-     * Returns a NEW INDIVIDUAL, crossed uniformly from this and the received parent.
-     */
-    public GAIndividual uniformCross(GAIndividual ind, Random a_rnd)
-    {
-        GAIndividual newInd = new GAIndividual(this.m_genome.length);
-
-        for(int i = 0; i < this.m_genome.length; ++i)
-        {
-            if(a_rnd.nextFloat() < 0.5f)
-            {
-                newInd.m_genome[i] = this.m_genome[i];
-            }else{
-                newInd.m_genome[i] = ind.m_genome[i];
[…]

### 2015-10-14 src/FastGame/Action.java

@@ -1,59 +1,0 @@
-package FastGame;
-
-import java.util.Objects;
-import java.util.Random;
-
-/**
- * Created by pwillic on 23/06/2015.
- */
-public final class Action {
-    public static final Action UP = new Action(0, -1);
-    public static final Action DOWN = new Action(0, 1);
-    public static final Action LEFT = new Action(-1, 0);
-    public static final Action RIGHT = new Action(1, 0);
-    public static final Action NOOP = new Action(0, 0);
-    private static final Random random = new Random();
-    public static final Action[] allActions = {NOOP, UP, DOWN, LEFT, RIGHT};
-    private int x, y;
-
-    private Action(int x, int y) {
-        this.x = x;
-        this.y = y;
-    }
-
-    public static Action getRandom() {
-        return allActions[random.nextInt(allActions.length)];
-    }
-
-    public int getX() {
-        return x;
-    }
-
-    public int getY() {
-        return y;
-    }
-
-    @Override
-    public boolean equals(Object o) {
-        if (this == o) return true;
-        if (o == null || getClass() != o.getClass()) return false;
-        Action action = (Action) o;
-        return Objects.equals(getX(), action.getX()) &&
-                Objects.equals(getY(), action.getY());
-    }
-
-    @Override
-    public int hashCode() {
-        return Objects.hash(getX(), getY());
-    }
-
-    @Override
-    public String toString() {
-        if (this.equals(UP)) return "Action.UP";
-        if (this.equals(DOWN)) return "Action.DOWN";
-        if (this.equals(LEFT)) return "Action.LEFT";
-        if (this.equals(RIGHT)) return "Action.RIGHT";
-
-        return "Action(" + x + ":" + y + ")";
-    }
-}

### 2015-10-14 src/FastGame/CoopGame.java

@@ -1,326 +1,0 @@
-package FastGame;
-
-import java.awt.*;
-import java.io.FileInputStream;
-import java.io.FileNotFoundException;
-import java.util.Map;
-import java.util.Scanner;
-import java.util.TreeMap;
-
-import static FastGame.GroundTypes.WALKABLE;
-import static FastGame.ObjectTypes.*;
-
-/**
- * Created by pwillic on 25/06/2015.
- */
-public class CoopGame {
-
-    private int[] data;
-    private int width, height, layers;
-    // need to check that all agents reach all goals
-    private boolean[] goalSet = new boolean[1];
-    private int maxID;
-
-    private boolean[] encountered;
-    private boolean[] doorOpen;
-    private double score = 0;
-    private int[] maxIDs;
-    private int[] agentLocations;
-
-    // volatile, required for A*
-    private Map<Integer, Point> playerPos = new TreeMap<>();
-
-    /**
-     * Opens a file and generates the game from that
-     *
-     * @param fileName
-     */
-    public CoopGame(String fileName) {
-        initialiseData(fileName);
-    }
-
-    public CoopGame(int width, int height) {
-        initialiseData(width, height, NUMBER_OF_LAYERS);
-    }
-
-    public static int getItemTypeFromValue(int value) {
-        return (int) (Math.floor(value / 1000.0d));
-    }
-
-    public static int getIDFromValue(int value) {
-        return value - (getItemTypeFromValue(value) * 1000);
-    }
-
-    public static int getValueFromIdAndType(int type, int id) {
-        return (type * 1000) + id;
-    }
-
-    public CoopGame getClone() {
-        CoopGame other = new CoopGame(this.width, this.height);
-        System.arraycopy(this.data, 0, other.data, 0, this.data.length);
-        other.goalSet = new boolean[this.goalSet.length];
-        System.arraycopy(this.goalSet, 0, other.goalSet, 0, this.goalSet.length);
-        other.doorOpen = new boolean[this.maxID];
-        System.arraycopy(this.doorOpen, 0, other.doorOpen, 0, this.doorOpen.length);
-        other.maxID = this.maxID;
-        other.maxIDs = new int[this.maxIDs.length];
-        System.arraycopy(this.maxIDs, 0, other.maxIDs, 0, this.maxIDs.length);
-        other.score = this.score;
-        other.playerPos = new TreeMap<>(this.playerPos);
-        other.agentLocations = new int[this.agentLocations.length];
[…]

### 2015-10-14 src/FastGame/FastGameMain.java

@@ -1,61 +1,0 @@
-package FastGame;
-
-import Controllers.*;
-import Controllers.VariGA.VariGA;
-import Controllers.astar.AStarBetter;
-import Controllers.ga.GAController;
-
-import javax.swing.*;
-
-/**
- * Created by pwillic on 25/06/2015.
- */
-public class FastGameMain {
-
-    public static void main(String[] args) throws InterruptedException {
-
-        JFrame frame = new JFrame("Game");
-        frame.setDefaultCloseOperation(WindowConstants.EXIT_ON_CLOSE);
-        WASDController wasd = new WASDController();
-        ArrowController arrows = new ArrowController();
-
-//        Controller c1 = new GAController(true);
-
-        Controller c1 = new MCTS(true, 500, 10, 45);
-//        Controller c1 = new VariGA(true, 2000);
-//        Controller c1 = new RandomController();
-
-//        Controller c1 = new VariGA(true, 500);
-//        Controller c1 = new RandomController();
-//          Controller c1 = new NoOp();
-
-//        Controller c1 = wasd;
-//        Controller c2 = new GAController(false);
-        Controller c2 = new MCTS(false, 500, 10, 45);
-//            Controller c2 = new VariGA(false, 2000);
-//        Controller c2 = new RandomController();
-//        Controller c2 = arrows;
-//        Controller c2 = new NoOp();
-
-        CoopGame game = new CoopGame("data/maps/level6.txt");
-
-        Viewer viewer = new Viewer(game);
-        viewer.addKeyListener(wasd);
-        viewer.addKeyListener(arrows);
-        viewer.setFocusable(true);
-        viewer.requestFocus();
-
-        frame.add(viewer);
-        frame.pack();
-        frame.setVisible(true);
-
-        int ticks = 0;
-        while (!game.hasWon()) {
-            game.update(c1.get(game.getClone()), c2.get(game.getClone()));
-            ticks++;
-            Thread.sleep(40);
-            viewer.repaint();
-        }
-        System.out.println(ticks);
-    }
-}

### 2015-10-14 src/FastGame/GroundTypes.java

@@ -1,13 +1,0 @@
-package FastGame;
-
-/**
- * Created by pwillic on 25/06/2015.
- */
-public interface GroundTypes {
-    int GROUND = 0;
-    int WALL = 1;
-    int WATER = 2;
-
-    boolean[] WALKABLE = new boolean[]{true, false, true};
-    boolean[] DANGEROUS = new boolean[]{false, false, true};
-}

### 2015-10-14 src/FastGame/ObjectTypes.java

@@ -1,19 +1,0 @@
-package FastGame;
-
-import java.awt.*;
-
-/**
- * Created by pwillic on 25/06/2015.
- */
-public interface ObjectTypes {
-    int NO_OBJECT = 0;
-    int AGENT = 1;
-    int BUTTON = 2;
-    int DOOR = 3;
-    int GOAL = 4;
-
-    int NUMBER_OF_LAYERS = 5;
-
-    Color[] OBJECT_COLOURS = {Color.WHITE, Color.YELLOW.darker(), Color.RED, Color.BLUE,  Color.YELLOW};
-    Color[] TEXT_COLOURS = {Color.BLACK, Color.RED, Color.YELLOW, Color.GREEN, Color.RED};
-}

### 2015-10-14 src/FastGame/RoundRobinMT.java

@@ -1,157 +1,0 @@
-package FastGame;
-
-import Controllers.AStar;
-import Controllers.Controller;
-import Controllers.MCTS;
-import Controllers.RandomController;
-import Controllers.VariGA.VariGA;
-import Controllers.ga.GAController;
-import utils.GenerateCSV;
-
-import java.io.FileNotFoundException;
-import java.lang.reflect.Executable;
-import java.util.*;
-import java.util.concurrent.*;
-
-/**
- * Created by jwalto on 01/07/2015.
- */
-public class RoundRobinMT {
-    private final static Integer REPEATS = 1;
-    private final static Integer MAX_TICKS = 2000;
-
-    public static void main(String[] args) throws FileNotFoundException, InterruptedException, ExecutionException {
-
-        ExecutorService service = Executors.newFixedThreadPool(4);
-
-        String[] maps = {
-                "data/maps/level1.txt",
-                "data/maps/level2.txt",
-                "data/maps/level3.txt",
-                "data/maps/level4.txt",
-                "data/maps/level5.txt",
-                "data/maps/level6.txt",
-                "data/maps/level1E.txt"
-        };
-
-        Controller[] player1List = new Controller[]{
-                new MCTS(true, 500, 10, 45),
-                new MCTS(true, 75, 3, 15),
-                new MCTS(true, 200),
-                new VariGA(true, 500),
-                new GAController(true),
-                new RandomController()
-        };
-
-        Controller[] player2List = new Controller[] {
-                new MCTS(false, 500, 10, 45),
-                new MCTS(false, 75, 3, 15),
-                new MCTS(false, 200),
-                new VariGA(false, 500),
-                new GAController(true),
-                new RandomController()
-        };
-
-        while(!Thread.interrupted()) {
-            System.out.println("generating matchups");
-            List<Matchup> tasks = new ArrayList<>();
-            for (Controller p1 : player1List) {
-                for (Controller p2 : player2List) {
-                    for (String map : maps) {
-                        for (int trial = 0; trial < REPEATS; trial++) {
-                            tasks.add(new Matchup(p1, p2, map, trial));
-                        }
-                    }
-                }
-            }
-
-            System.out.println("calculating results (" + tasks.size() + " tasks)");
-            List<Future<Result>> results = service.invokeAll(tasks);
-
-            System.out.println("Processing results");
-            GenerateCSV csv = new GenerateCSV(System.getenv("COMPUTERNAME") + "-results-mtp.csv");
-            for (Future<Result> resultf : results) {
[…]

### 2015-10-14 src/FastGame/Test.java

@@ -1,54 +1,0 @@
-package FastGame;
-
-import Controllers.Controller;
-import Controllers.MCTS;
-import Controllers.RandomController;
-
-import java.util.ArrayList;
-import java.util.Arrays;
-
-/**
- * Created by pwillic on 30/06/2015.
- */
-public class Test {
-
-    public static void main(String[] args) {
-        Controller m1 = new MCTS(true, 500);
-        Controller m2 = new MCTS(false, 500);
-        Controller r1 = new RandomController();
-
-
-        Controller c1 = m1;
-//        Controller c1 = new RandomController();
-        //        Controller c2 = new MCTS(false);
-        Controller c2 = m2;
-
-
-
-        int gamesPerMatchup = 10;
-        double[] results1 = runGames(m1, m2, gamesPerMatchup);
-        System.out.println(Arrays.toString(results1));
-        double[] results2 = runGames(m1, r1, gamesPerMatchup);
-        System.out.println(Arrays.toString(results2));
-        double[] results3 = runGames(r1, r1, gamesPerMatchup);
-        System.out.println(Arrays.toString(results3));
-//        System.out.println(results2);
-//        System.out.println(results3);
-    }
-
-    public static double[] runGames(Controller c1, Controller c2, int gamesPerMatchup){
-        double[] results = new double[2];
-        for(int i = 0; i < gamesPerMatchup; i++) {
-            int ticksTaken = 0;
-            CoopGame game = new CoopGame("data/maps/level2.txt");
-            while (ticksTaken < 2000 && !game.hasWon()) {
-                game.update(c1.get(game.getClone()), c2.get(game.getClone()));
-                ticksTaken++;
-            }
-            results[0] += game.getScore();
-            results[1] += ticksTaken;
-            System.out.println("Game: " + i);
-        }
-        return results;
-    }
-}

### 2015-10-14 src/FastGame/ValueTest.java

@@ -1,15 +1,0 @@
-package FastGame;
-
-/**
- * Created by pwillic on 29/06/2015.
- */
-public class ValueTest {
-
-    public static void main(String[] args) {
-
-        int test = 5001;
-
-        System.out.println(CoopGame.getIDFromValue(test));
-        System.out.println(CoopGame.getItemTypeFromValue(test));
-    }
-}

### 2015-10-14 src/FastGame/Viewer.java

@@ -1,73 +1,0 @@
-package FastGame;
-
-import javax.swing.*;
-import java.awt.*;
-
-import static FastGame.GroundTypes.GROUND;
-import static FastGame.GroundTypes.WALL;
-import static FastGame.ObjectTypes.AGENT;
-import static FastGame.ObjectTypes.OBJECT_COLOURS;
-import static FastGame.ObjectTypes.TEXT_COLOURS;
-import static FastGame.ObjectTypes.DOOR;
-
-/**
- * Created by pwillic on 25/06/2015.
- */
-public class Viewer extends JComponent {
-
-    CoopGame game;
-
-    int gridSize = 50;
-
-    public Viewer(CoopGame game) {
-        this.game = game;
-    }
-
-    @Override
-    public void paint(Graphics g) {
-        for (int x = 0; x < game.getWidth(); x++) {
-            for (int y = 0; y < game.getHeight(); y++) {
-                int groundValue = game.get(x, y, 0);
-
-                switch (groundValue) {
-                    case GROUND:
-                        g.setColor(Color.LIGHT_GRAY);
-                        break;
-                    case WALL:
-                        g.setColor(Color.BLACK);
-                        break;
-                }
-                g.fillRect(x * gridSize, y * gridSize, gridSize, gridSize);
-                for (int layer = game.getLayers() - 1; layer >= 1; layer--) {
-                    int value = game.get(x, y, layer);
-                    if(value != 0) {
-                        int itemType = CoopGame.getItemTypeFromValue(value);
-                        if(itemType == DOOR && game.doorOpen(CoopGame.getIDFromValue(value))){
-                            continue;
-                        }
-
-                        g.setColor(OBJECT_COLOURS[itemType]);
-                        g.fillRect(x * gridSize, y * gridSize, gridSize, gridSize);
-
-                        g.setColor(TEXT_COLOURS[itemType]);
-                        g.drawString("" + CoopGame.getIDFromValue(value), x * gridSize + gridSize / 2, (y * gridSize) + gridSize / 2);
-                    }
-                }
-            }
-        }
-
-        // Draw the grid
-        g.setColor(Color.BLACK);
-        for (int x = 0; x < game.getWidth(); x++) {
-            for (int y = 0; y < game.getHeight(); y++) {
-                g.drawRect(x * gridSize, y * gridSize, gridSize, gridSize);
-            }
-        }
-        super.paint(g);
-    }
-
-    @Override
[…]

### 2015-10-14 src/main/java/Controllers/AStar.java

@@ -1,0 +1,222 @@
+package Controllers;
+
+import java.awt.Point;
+import java.util.*;
+
+import FastGame.Action;
+import FastGame.CoopGame;
+import FastGame.ObjectTypes;
+
+/**
+ * An implementation of A* for path finding
+ */
+public class AStar extends Controller {
+
+    public static Queue<FastGame.Action> getPath(CoopGame game, ActionNode start, boolean isFirst) {
+        int maxExpands = 25;
+
+        List<Point> goals = getGoals(game);
+
+        List<ActionNode> closedSet = new ArrayList<ActionNode>();
+        Map<ActionNode, ActionNode> cameFrom = new HashMap<>();
+        Map<ActionNode, Double> gScores = new HashMap<>();
+        Map<ActionNode, Double> fScores = new HashMap<>();
+        List<ActionNode> openSet = new ArrayList<ActionNode>();
+        openSet.add(start);
+
+        while(!openSet.isEmpty()) {
+            ActionNode current = openSet.get(0);
+            //System.out.println("open: "+openSet);
+            //System.out.println("closed: "+closedSet);
+            if (current.game.hasWon() || current.game.getScore() == 0.5) {
+                return buildPath(current, cameFrom, isFirst);
+            }
+            openSet.remove(current);
+            closedSet.add(current);
+
+            for (ActionNode neighbor : getAvailableMoves(current, isFirst)) {
+                if (closedSet.contains(neighbor)) {
+                    continue;
+                }
+                Double gScore = gScores.get(current);
+                gScore = gScore!=null?gScore:0;
+                gScore += 1; // 'cost' to get to this state
+
+                Double otherScore = gScores.get(neighbor);
+                otherScore = otherScore!=null?otherScore:0;
+                
+                if ( !openSet.contains(neighbor) || gScore > otherScore ) {
+                    cameFrom.put(neighbor, current);
+                    gScores.put(neighbor, gScore);
+                    fScores.put(neighbor, gScore + getDistance(neighbor, goals, isFirst));
+                    if (!openSet.contains(neighbor)) {
+                        openSet.add(neighbor);
+                    }
+                }
+            }
+        }
+
+        // we didn't find a path
+        return new LinkedList<FastGame.Action>();
+    }
+
+    public static List<Point> getGoals(CoopGame cg) {
+        List<Point> goals = new ArrayList<Point>();
+
+        for (int x=0; x<cg.getWidth(); x++) {
+            for (int y=0; y<cg.getHeight(); y++) {
[…]

### 2015-10-14 src/main/java/Controllers/ArrowController.java

@@ -1,0 +1,32 @@
+package Controllers;
+
+import java.awt.event.KeyEvent;
+
+/**
+ * Created by pwillic on 30/06/2015.
+ */
+public class ArrowController extends WASDController{
+
+    @Override
+    public void keyPressed(KeyEvent e) {
+        int keyCode = e.getKeyCode();
+        switch(keyCode){
+            case KeyEvent.VK_UP:
+                actionID = 4;
+                break;
+            case KeyEvent.VK_DOWN:
+                actionID = 1;
+                break;
+            case KeyEvent.VK_LEFT:
+                actionID = 2;
+                break;
+            case KeyEvent.VK_RIGHT:
+                actionID = 3;
+                break;
+            case KeyEvent.VK_CONTROL:
+                actionID = 5;
+                break;
+        }
+//        System.out.println("Action Arrows: " + actions[actionID]);
+    }
+}

### 2015-10-14 src/main/java/Controllers/Controller.java

@@ -1,0 +1,25 @@
+package Controllers;
+
+import FastGame.Action;
+import FastGame.CoopGame;
+import gamesrc.GameState;
+
+/**
+ * Created by pwillic on 23/06/2015.
+ */
+public abstract class Controller {
+
+    public Controller getClone() { return this; }
+    
+    public void startGame() {
+    	
+    }
+
+    public Action get(GameState game) {
+        return Action.NOOP;
+    }
+
+    public String getSimpleName(){
+        return this.getClass().getSimpleName();
+    }
+}

### 2015-10-14 src/main/java/Controllers/MCTS.java

@@ -1,0 +1,243 @@
+package Controllers;
+
+import FastGame.Action;
+import FastGame.CoopGame;
+import gamesrc.GameState;
+
+import java.util.Random;
+
+/**
+ * Created by pwillic on 23/06/2015.
+ */
+public class MCTS extends Controller {
+
+    protected Random random = new Random();
+    private int maxUCTDepth = 5;
+    private int maxRolloutDepth = 30;
+    private int iterationLimit = 0;
+
+    private boolean first;
+
+    public MCTS(boolean first, int iterationLimit, int maxUCTDepth, int maxRolloutDepth) {
+        this.first = first;
+        this.iterationLimit = iterationLimit;
+        this.maxUCTDepth = maxUCTDepth;
+        this.maxRolloutDepth = maxRolloutDepth;
+    }
+
+    public MCTS(boolean first, int iterationLimit){
+        this.first = first;
+        this.iterationLimit = iterationLimit;
+    }
+
+    @Override
+    public Action get(GameState game) {
+        MCTSNode root = new MCTSNode(2.0, this, game.getActionLength());
+        MCTSNode travel;
+        GameState workingGame;
+        int iterations = 0;
+        while (iterations < iterationLimit) {
+            workingGame = game.getClone();
+            travel = root.select(workingGame);
+            double result = travel.rollout(workingGame);
+            travel.updateValues(result);
+            iterations++;
+        }
+//        System.out.println("Iterations : " + iterations);
+//        System.out.println(root.getBestAction());
+        return root.getBestAction();
+    }
+
+    public int getMaxUCTDepth() {
+        return maxUCTDepth;
+    }
+
+    public int getMaxRolloutDepth() {
+        return maxRolloutDepth;
+    }
+
+    public boolean isFirst() {
+        return first;
+    }
+
+    @Override
+    public String getSimpleName() {
+        return "MCTS: (" + iterationLimit + ";" + maxUCTDepth + ";" + maxRolloutDepth + ")";
+    }
+}
+
+class MCTSNode {
+
+    private static final double EPSILON = 1e-6;
+
+    private double explorationConstant;
+    private Action moveToThisState;
+
+    private double totalValue;
+    private int numberOfVisits;
+    private int currentDepth;
+    private int childrenExpandedSoFar = 0;
+
+    private MCTSNode parent;
+    private MCTSNode[] children;
+    private int childLength;
+
+    private MCTS mcts;
+
+    // Root
[…]

### 2015-10-14 src/main/java/Controllers/RandomController.java

@@ -1,0 +1,16 @@
+package Controllers;
+
+import FastGame.Action;
+import FastGame.CoopGame;
+import gamesrc.GameState;
+
+/**
+ * Created by pwillic on 30/06/2015.
+ */
+public class RandomController extends Controller {
+
+    @Override
+    public Action get(GameState game) {
+        return Action.getRandom(-1, game);
+    }
+}

### 2015-10-14 src/main/java/Controllers/VariGA/VariGA.java

@@ -1,0 +1,271 @@
+package Controllers.VariGA;
+
+import Controllers.Controller;
+import FastGame.Action;
+import FastGame.CoopGame;
+import gamesrc.GameState;
+
+import java.util.Random;
+
+/**
+ * Do a 1 + 1 ES
+ * Created by Piers on 01/07/2015.
+ */
+public class VariGA extends Controller {
+
+    private boolean first;
+    private int iterations;
+    private double numChance = 0.25;
+    private double lengthChance = 0.8;
+    private double actionChance = 0.75;
+    private ActionSequence currentBest;
+    private int currentUsage = 0;
+    private ActionSequence parent;
+    private double parentFitness;
+    private GameState fastForwardedGame;
+
+    private int[] params;
+
+    public VariGA(boolean first, int iterations) {
+        this.first = first;
+        this.iterations = iterations;
+    }
+
+    public VariGA(boolean first, int iterations, double[] chances, int[] params){
+        this(first, iterations);
+        numChance = chances[0];
+        lengthChance = chances[1];
+        actionChance = chances[2];
+        this.params = params;
+    }
+
+    public VariGA getClone(){
+        VariGA other = new VariGA(this.first, this.iterations);
+        other.params = this.params;
+        other.actionChance = this.actionChance;
+        other.lengthChance = this.lengthChance;
+        other.numChance = this.numChance;
+        return other;
+    }
+    // int minNum, int maxNum, int minLength, int maxLength
+    private ActionSequence getNewParent(Action[] actionList){
+        if(params == null)  return new ActionSequence(3, 10, 1, 5, actionList);
+        return new ActionSequence(params[0], params[1], params[2], params[3], actionList);
+    }
+
+    @Override
+    public Action get(GameState game) {
+        if (currentBest == null || currentUsage >= currentBest.getFirstActionLength()) {
+            currentBest = parent;
+            parent = null;
+            // Fast forward the fast forward to the right place
+            fastForwardedGame = game.getClone();
+            for(int i = 0 ;!fastForwardedGame.hasWon() &&  i < currentBest.getFirstActionLength(); i++){
+                if(first){
+                	Action[] actionList = fastForwardedGame.getLegalActions(0);
+                    fastForwardedGame.update(currentBest.getActionAt(i, actionList), Action.getRandom(1, game));
+                }else{
+                	Action[] actionList = fastForwardedGame.getLegalActions(1);
+                    fastForwardedGame.update(Action.getRandom(0, game), currentBest.getActionAt(i, actionList));
[…]

### 2015-10-14 src/main/java/Controllers/WASDController.java

@@ -1,0 +1,56 @@
+package Controllers;
+
+import FastGame.Action;
+import FastGame.CoopGame;
+import gamesrc.GameState;
+
+import java.awt.event.KeyEvent;
+import java.awt.event.KeyListener;
+
+/**
+ * Created by pwillic on 23/06/2015.
+ */
+public class WASDController extends Controller implements KeyListener {
+    Action[] actions = new Action[]{Action.NOOP, Action.DOWN, Action.LEFT, Action.RIGHT, Action.UP, Action.BEEP};
+
+    int actionID = 0;
+
+    @Override
+    public Action get(GameState game) {
+        int id = actionID;
+        actionID = 0;
+        return actions[id];
+    }
+
+    @Override
+    public void keyTyped(KeyEvent e) {
+
+    }
+
+    @Override
+    public void keyPressed(KeyEvent e) {
+        switch (e.getKeyChar()) {
+            case 'a':
+                actionID = 2;
+                break;
+            case 's':
+                actionID = 1;
+                break;
+            case 'd':
+                actionID = 3;
+                break;
+            case 'w':
+                actionID = 4;
+                break;
+            case 'x':
+                actionID = 5;
+                break;
+        }
+//        System.out.println("Action: " + actions[actionID]);
+    }
+
+    @Override
+    public void keyReleased(KeyEvent e) {
+
+    }
+}

### 2015-10-14 src/main/java/Controllers/astar/AStarBetter.java

@@ -1,0 +1,54 @@
+package Controllers.astar;
+
+import Controllers.AStar;
+import Controllers.Controller;
+import FastGame.Action;
+import FastGame.CoopGame;
+import gamesrc.GameState;
+
+import java.util.List;
+
+/**
+ * Created by jwalto on 02/07/2015.
+ */
+public class AStarBetter extends Controller {
+    private PathFind find;
+    private boolean isFirst;
+    private MovePair lastMove;
+
+    public AStarBetter(boolean isFirst) {
+        this.find = new PathFind(new GameScore());
+        this.isFirst = isFirst;
+        this.lastMove = new MovePair(Action.NOOP, Action.NOOP);
+    }
+
+    @Override
+    public Controller getClone() {
+        AStarBetter btr = new AStarBetter(isFirst);
+        btr.lastMove = lastMove;
+        return btr;
+    }
+
+    @Override
+    public Action get(GameState game) {
+//        System.out.println("requested move");
+//        GameNode start = new GameNode(game, lastMove);
+//        List<MovePair> pairs = find.getPath(game, start);
+//
+//        if (pairs.isEmpty()) {
+//            System.out.println("Unable to find path, perform random");
+//            return Action.getRandom();
+//        }
+//
+//        if (pairs.size() == 1) {
+//            System.out.println();
+//            return Action.NOOP;
+//        }
+//
+//        System.out.println(pairs);
+//        // this assumes the move the opponent played last was the "perfect" move, but it probably wasn't.
+//        lastMove = pairs.get(1);
+//        return isFirst?lastMove.p1Move:lastMove.p2Move;
+        return null;
+    }
+}

### 2015-10-14 src/main/java/Controllers/astar/GameNode.java

@@ -1,0 +1,60 @@
+package Controllers.astar;
+
+import Controllers.ga.GA;
+import FastGame.Action;
+import FastGame.CoopGame;
+import gamesrc.GameState;
+
+/**
+ * Created by jwalto on 02/07/2015.
+ */
+public class GameNode implements Comparable<GameNode> {
+    protected GameState game;
+    protected MovePair actions;
+
+    public GameNode(GameState game, MovePair actions) {
+        this.game = game;
+        this.actions = actions;
+    }
+
+    public boolean isTerminal() {
+        return game.hasWon() || game.getScore() == 1;
+    }
+
+    @Override
+    public int compareTo(GameNode o) {
+        return Double.compare(o.game.getScore(), game.getScore());
+    }
+
+    public boolean gameEquals(GameState game2, GameState game3) {
+//        if (game2.getScore() != game3.getScore()) return false;
+//        if (!game2.getPos(0).equals(game3.getPos(0))) return false;
+//        if (!game2.getPos(1).equals(game3.getPos(1))) return false;
+        return true;
+    }
+
+    @Override
+    public boolean equals(Object o) {
+        if (this == o) return true;
+        if (o == null || getClass() != o.getClass()) return false;
+
+        GameNode gameNode = (GameNode) o;
+
+        if (!actions.equals(gameNode.actions)) return false;
+        if (!gameEquals(game, gameNode.game)) return false;
+
+        return true;
+    }
+
+    @Override
+    public int hashCode() {
+        int result = game.hashCode();
+        result = 31 * result + actions.hashCode();
+        return result;
+    }
+
+    public String toString() {
+        return null;
+//        return actions.toString()+" "+game.getScore()+",P1{"+game.getPos(0)+"},P2{"+game.getPos(1)+"}";
+    }
+}

### 2015-10-14 src/main/java/Controllers/astar/GameScore.java

@@ -1,0 +1,14 @@
+package Controllers.astar;
+
+
+/**
+ * Created by jwalto on 02/07/2015.
+ */
+public class GameScore implements Function<GameNode,Double> {
+
+    @Override
+    public Double apply(GameNode gameNode) {
+        return gameNode.game.getScore();
+    }
+
+}

### 2015-10-14 src/main/java/Controllers/astar/PathFind.java

@@ -1,0 +1,106 @@
+package Controllers.astar;
+
+        import FastGame.Action;
+        import FastGame.CoopGame;
+import gamesrc.GameState;
+
+import java.awt.Point;
+        import java.util.*;
+
+/**
+ * An implementation of A* for path finding
+ */
+public class PathFind {
+    private Function<GameNode, Double> heristic;
+    Map<GameNode, GameNode> cameFrom = new HashMap<>();
+    Map<GameNode, Double> gScores = new HashMap<>();
+    Map<GameNode, Double> fScores = new HashMap<>();
+
+    public PathFind(Function<GameNode, Double> heristic) {
+        this.heristic = heristic;
+    }
+
+    public List<MovePair> getPath(GameState game, GameNode start) {
+        List<GameNode> closedSet = new ArrayList<GameNode>();
+        Queue<GameNode> openSet = new PriorityQueue<GameNode>(10, new Comparator<GameNode>() {
+
+            @Override
+            public int compare(GameNode o1, GameNode o2) {
+                System.out.println(o1);
+                System.out.println(o2);
+                Double score1 = fScores.get(o1);
+                Double score2 = fScores.get(o2);
+                return Double.compare(score1,score2) * -1;
+            }
+        });
+        openSet.add(start);
+
+        while(!openSet.isEmpty()) {
+            GameNode current = openSet.poll();
+            System.out.println(current);
+            if (current.isTerminal()) {
+                return buildPath(current, cameFrom);
+            }
+            openSet.remove(current);
+            closedSet.add(current);
+
+            for (MovePair moves : getAvailableMoves(game)) {
+                GameState nState = current.game.getClone();
+                nState.update(moves.p1Move, moves.p2Move);
+                GameNode neighbor = new GameNode(nState, moves);
+
+                if (closedSet.contains(neighbor)) {
+                    continue;
+                }
+                Double gScore = gScores.get(current);
+                if (gScore == null) {
+                    gScore = 0.0;
+                }
+                gScore += 1;
+
+                Double gScoreOther = gScores.get(neighbor);
+                gScoreOther = gScoreOther==null?0:gScoreOther;
+                
+                if ( !openSet.contains(neighbor) || gScore > gScoreOther ) {
+                    cameFrom.put(neighbor, current);
+                    gScores.put(neighbor, gScore);
+                    fScores.put(neighbor, gScore + heristic.apply(neighbor));
[…]

### 2015-10-14 src/main/java/Controllers/ga/GA.java

@@ -1,0 +1,164 @@
+package Controllers.ga;
+
+import FastGame.Action;
+import FastGame.CoopGame;
+import gamesrc.GameState;
+
+import java.util.ArrayList;
+import java.util.Random;
+
+/**
+ * PTSP-Competition
+ * Created by Diego Perez, University of Essex.
+ * Date: 17/10/12
+ */
+public class GA
+{
+    public final int NUM_INDIVIDUALS = 10;
+    static public int NUM_ACTIONS_INDIVIDUAL = 15;
+    static public int TOURNAMENT_SIZE = 3;
+    public final int ELITISM = 2;
+    public ArrayList<MacroAction> m_actionList;             //List of available actions to govern the ship.
+    public Random m_rnd;                                    //Random number generator
+    public int m_numGenerations;
+
+    public GAIndividual[] m_individuals;
+
+    public GA(Action[] legalActions)
+    {
+        m_rnd = new Random();
+
+        m_actionList = new ArrayList<MacroAction>();
+        for (Action action : legalActions) {
+            m_actionList.add(new MacroAction(action, GAConstants.MACRO_ACTION_LENGTH));
+        }
+
+        m_individuals = new GAIndividual[NUM_INDIVIDUALS];
+        //init(a_gameState);
+    }
+
+    public void init(GameState a_gameState, boolean first)
+    {
+        //System.out.println(" --------- Starting GA --------- ");
+        m_numGenerations = 0;
+        for(int i = 0; i < NUM_INDIVIDUALS; ++i)
+        {
+            m_individuals[i] = new GAIndividual(NUM_ACTIONS_INDIVIDUAL);
+            m_individuals[i].randomize(m_rnd, a_gameState, m_actionList.size());
+            m_individuals[i].evaluate(a_gameState, first);
+            //System.out.format("individual i: " + i + ", fitness: %.3f, actions: %s \n", m_individuals[i].m_fitness, m_individuals[i].toString());
+        }
+
+        sortPopulationByFitness();
+    }
+
+    public MacroAction run(GameState a_gameState, int generations, boolean first)
+    {
+        int currGen = 0;
+        while(currGen < generations)
+        {
+            GAIndividual[] nextPop = new GAIndividual[m_individuals.length];
+            //System.out.println(" --------- New generation " + m_numGenerations + " --------- ");
+
+            int i;
+            for(i = 0; i < ELITISM; ++i)
+            {
+                nextPop[i] = m_individuals[i];
[…]

### 2015-10-14 src/main/java/Controllers/ga/GAController.java

@@ -1,0 +1,76 @@
+package Controllers.ga;
+
+import Controllers.Controller;
+import FastGame.Action;
+import FastGame.CoopGame;
+import gamesrc.GameState;
+
+/**
+ * GA controller for CoopGame, modified from PTSP.
+ *
+ * Created by jwalto on 01/07/2015.
+ */
+public class GAController extends Controller {
+    private static final Integer GENERATIONS = 10;
+    private static final MacroAction NOOP = new MacroAction(Action.NOOP, GAConstants.MACRO_ACTION_LENGTH);
+
+    private GA ga;
+    private boolean first;
+    private MacroAction currentAction;
+    private int macroPos;
+    private boolean reset;
+    private boolean startOfGame;
+
+    public GAController(boolean first) {
+        this.first = first;
+        this.currentAction = NOOP;
+        this.macroPos = 0;
+        this.reset = true;
+        this.startOfGame = true;
+    }
+
+    @Override
+    public Controller getClone() {
+        GAController other = new GAController(first);
+        return other;
+    }
+
+    @Override
+    public Action get(GameState game) {
+    	if (this.ga == null) {
+    		this.ga = new GA(game.getLegalActions(first?0:1));
+    	}
+    	
+        MacroAction nextAction = NOOP;
+
+        if (startOfGame) {
+            currentAction = NOOP;
+            nextAction = currentAction;
+            reset = true;
+            macroPos = GAConstants.MACRO_ACTION_LENGTH-1;
+            startOfGame = false;
+        } else {
+            if (macroPos > 0) {
+                if (reset) {
+                    ga.init(game, first);
+                }
+                ga.run(game, GENERATIONS, first);
+                macroPos--;
+            } else if (macroPos == 0) {
+                nextAction = currentAction;
+                MacroAction gaBestAction = ga.run(game, GENERATIONS, first);
+                if (gaBestAction != null) {
+                    currentAction = gaBestAction;
+                }
+
+                if (currentAction != null) {
+                    macroPos = GAConstants.MACRO_ACTION_LENGTH - 1;
+                }
+                reset = true;
+            }
+        }
+
+
+        return nextAction.getAction();
+    }
+}

### 2015-10-14 src/main/java/Controllers/ga/GAIndividual.java

@@ -1,0 +1,107 @@
+package Controllers.ga;
+
+import FastGame.Action;
+import FastGame.CoopGame;
+import gamesrc.GameState;
+
+import java.util.Random;
+
+/**
+ * PTSP-Competition
+ * Created by Diego Perez, University of Essex.
+ * Date: 17/10/12
+ */
+public class GAIndividual
+{
+    public Action[] m_genome;
+    public boolean isFirst;
+    public double m_fitness;
+    public final double MUTATION_PROB = 0.2; //0.834=5/6   //0.2;
+
+    public GAIndividual(int a_genomeLength)
+    {
+        m_genome = new Action[a_genomeLength];
+        m_fitness = 0;
+    }
+
+    public void randomize(Random a_rnd, GameState state, int a_numActions)
+    {
+        for(int i = 0; i < m_genome.length; ++i)
+        {
+            m_genome[i] = Action.getRandom(-1, state);
+        }
+    }
+
+    public GameState evaluate(GameState a_gameState, boolean isFirst)
+    {
+        GameState thisGameCopy = a_gameState.getClone();
+        this.isFirst = isFirst;
+        boolean end = false;
+        for(int i = 0; i < m_genome.length; ++i)
+        {
+            Action thisAction = m_genome[i];
+            for(int j =0; !end && j < GAConstants.MACRO_ACTION_LENGTH; ++j)
+            {
+                if (isFirst) {
+                    thisGameCopy.update(thisAction, Action.getRandom(isFirst?0:1, a_gameState));
+                } else {
+                    thisGameCopy.update(Action.getRandom(isFirst?0:1, a_gameState), thisAction);
+                }
+                end = thisGameCopy.hasWon();
+            }
+        }
+        m_fitness = thisGameCopy.getScore();
+        return thisGameCopy;
+    }
+
+    public void mutate(Random a_rnd, GameState state)
+    {
+        for (int i = 0; i < m_genome.length; i++) {
+            if(a_rnd.nextDouble() < MUTATION_PROB)
+            {
+                m_genome[i] = Action.getRandom(isFirst?0:1, state);
+            }
+        }
+    }
+
+    /**
+     * Returns a NEW INDIVIDUAL, crossed uniformly from this and the received parent.
+     */
+    public GAIndividual uniformCross(GAIndividual ind, Random a_rnd)
+    {
+        GAIndividual newInd = new GAIndividual(this.m_genome.length);
+
[…]

### 2015-10-14 src/main/java/FastGame/Action.java

@@ -1,0 +1,73 @@
+package FastGame;
+
+import java.util.Objects;
+import java.util.Random;
+
+import gamesrc.GameState;
+
+/**
+ * Created by pwillic on 23/06/2015.
+ */
+public class Action {
+    public static final Action UP = new MoveAction("UP", 0, -1);
+    public static final Action DOWN = new MoveAction("DOWN", 0, 1);
+    public static final Action LEFT = new MoveAction("LEFT", -1, 0);
+    public static final Action RIGHT = new MoveAction("RIGHT", 1, 0);
+    public static final Action NOOP = new Action("NOOP", 0, 0);
+    public static final Action BEEP = new TalkAction(0, 0, 0);
+    private static final Random random = new Random();
+    //public static final Action[] allActions = {NOOP, UP, DOWN, LEFT, RIGHT};
+
+    private int x, y;
+    private final String actionID;
+    
+    protected Action(String actionID, int x, int y) {
+    	this.actionID = actionID;
+        this.x = x;
+        this.y = y;
+    }
+
+    public static Action getRandom(int actionID, GameState state) {
+    	Action[] allActions = state.getLegalActions(actionID);
+        return allActions[random.nextInt(allActions.length)];
+    }
+
+    public int getX() {
+        return x;
+    }
+
+    public int getY() {
+        return y;
+    }
+    
+    public boolean isMovement() {
+    	return true;
+    }
+    
+    public boolean isNoop() {
+    	return "NOOP".equals(actionID);
+    }
+
+    @Override
+    public boolean equals(Object o) {
+        if (this == o) return true;
+        if (o == null || getClass() != o.getClass()) return false;
+        Action action = (Action) o;
+        return Objects.equals(getX(), action.getX()) &&
+                Objects.equals(getY(), action.getY());
+    }
+
+    @Override
+    public int hashCode() {
+        return Objects.hash(actionID, getX(), getY());
+    }
+
+    @Override
+    public String toString() {
+    	return actionID;
+    }
+
+	public boolean isTalk() {
+		return false;
+	}
+}

### 2015-10-14 src/main/java/FastGame/CoopGame.java

@@ -1,0 +1,340 @@
+package FastGame;
+
+import java.awt.*;
+import java.io.FileInputStream;
+import java.io.FileNotFoundException;
+import java.util.Map;
+import java.util.Scanner;
+import java.util.TreeMap;
+
+import gamesrc.GameState;
+
+import static FastGame.GroundTypes.WALKABLE;
+import static FastGame.ObjectTypes.*;
+
+/**
+ * Created by pwillic on 25/06/2015.
+ */
+public class CoopGame implements GameState {
+
+    private int[] data;
+    private int width, height, layers;
+    // need to check that all agents reach all goals
+    private boolean[] goalSet = new boolean[1];
+    private int maxID;
+
+    private boolean[] encountered;
+    private boolean[] doorOpen;
+    private double score = 0;
+    private int[] maxIDs;
+    private int[] agentLocations;
+
+    // volatile, required for A*
+    private Map<Integer, Point> playerPos = new TreeMap<>();
+
+    /**
+     * Opens a file and generates the game from that
+     *
+     * @param fileName
+     */
+    public CoopGame(String fileName) {
+        initialiseData(fileName);
+    }
+
+    public CoopGame(int width, int height) {
+        initialiseData(width, height, NUMBER_OF_LAYERS);
+    }
+
+    public static int getItemTypeFromValue(int value) {
+        return (int) (Math.floor(value / 1000.0d));
+    }
+
+    public static int getIDFromValue(int value) {
+        return value - (getItemTypeFromValue(value) * 1000);
+    }
+
+    public static int getValueFromIdAndType(int type, int id) {
+        return (type * 1000) + id;
+    }
+
+    public CoopGame getClone() {
+        CoopGame other = new CoopGame(this.width, this.height);
+        System.arraycopy(this.data, 0, other.data, 0, this.data.length);
+        other.goalSet = new boolean[this.goalSet.length];
+        System.arraycopy(this.goalSet, 0, other.goalSet, 0, this.goalSet.length);
+        other.doorOpen = new boolean[this.maxID];
+        System.arraycopy(this.doorOpen, 0, other.doorOpen, 0, this.doorOpen.length);
+        other.maxID = this.maxID;
+        other.maxIDs = new int[this.maxIDs.length];
+        System.arraycopy(this.maxIDs, 0, other.maxIDs, 0, this.maxIDs.length);
+        other.score = this.score;
+        other.playerPos = new TreeMap<>(this.playerPos);
[…]

### 2015-10-14 src/main/java/FastGame/FastGameMain.java

@@ -1,0 +1,62 @@
+package FastGame;
+
+import Controllers.*;
+import Controllers.VariGA.VariGA;
+import Controllers.astar.AStarBetter;
+import Controllers.ga.GAController;
+import gamesrc.GameState;
+
+import javax.swing.*;
+
+/**
+ * Created by pwillic on 25/06/2015.
+ */
+public class FastGameMain {
+
+    public static void main(String[] args) throws InterruptedException {
+
+        JFrame frame = new JFrame("Game");
+        frame.setDefaultCloseOperation(WindowConstants.EXIT_ON_CLOSE);
+        WASDController wasd = new WASDController();
+        ArrowController arrows = new ArrowController();
+
+//        Controller c1 = new GAController(true);
+
+//        Controller c1 = new MCTS(true, 1000, 10, 45);
+//        Controller c1 = new VariGA(true, 2000);
+        Controller c1 = new RandomController();
+
+//        Controller c1 = new VariGA(true, 500);
+//        Controller c1 = new RandomController();
+//          Controller c1 = new NoOp();
+
+//        Controller c1 = wasd;
+//        Controller c2 = new GAController(false);
+//        Controller c2 = new MCTS(false, 1000, 10, 45);
+//            Controller c2 = new VariGA(false, 2000);
+        Controller c2 = new RandomController();
+//        Controller c2 = arrows;
+//        Controller c2 = new NoOp();
+
+        CoopGame game = new CoopGame("data/maps/level1.txt");
+
+        Viewer viewer = new Viewer(game);
+        viewer.addKeyListener(wasd);
+        viewer.addKeyListener(arrows);
+        viewer.setFocusable(true);
+        viewer.requestFocus();
+
+        frame.add(viewer);
+        frame.pack();
+        frame.setVisible(true);
+
+        int ticks = 0;
+        while (!game.hasWon()) {
+            game.update(c1.get(game.getClone()), c2.get(game.getClone()));
+            ticks++;
+//            Thread.sleep(40);
+            viewer.repaint();
+        }
+        System.out.println(ticks);
+    }
+}

### 2015-10-14 src/main/java/FastGame/GroundTypes.java

@@ -1,0 +1,13 @@
+package FastGame;
+
+/**
+ * Created by pwillic on 25/06/2015.
+ */
+public interface GroundTypes {
+    int GROUND = 0;
+    int WALL = 1;
+    int WATER = 2;
+
+    boolean[] WALKABLE = new boolean[]{true, false, true};
+    boolean[] DANGEROUS = new boolean[]{false, false, true};
+}

### 2015-10-14 src/main/java/FastGame/ObjectTypes.java

@@ -1,0 +1,20 @@
+package FastGame;
+
+import java.awt.*;
+
+/**
+ * Created by pwillic on 25/06/2015.
+ */
+public interface ObjectTypes {
+    int NO_OBJECT = 0;
+    int AGENT = 1;
+    int BUTTON = 2;
+    int DOOR = 3;
+    int GOAL = 4;
+    int TIMEDBUTTON = 6;
+
+    int NUMBER_OF_LAYERS = 5;
+
+    Color[] OBJECT_COLOURS = {Color.WHITE, Color.YELLOW.darker(), Color.RED, Color.BLUE,  Color.YELLOW, Color.YELLOW, Color.RED.brighter()};
+    Color[] TEXT_COLOURS = {Color.BLACK, Color.RED, Color.YELLOW, Color.GREEN, Color.RED, Color.RED, Color.YELLOW};
+}

### 2015-10-14 src/main/java/FastGame/RoundRobinMT.java

@@ -1,0 +1,156 @@
+package FastGame;
+
+import Controllers.AStar;
+import Controllers.Controller;
+import Controllers.MCTS;
+import Controllers.RandomController;
+import Controllers.VariGA.VariGA;
+import Controllers.ga.GAController;
+import utils.GenerateCSV;
+
+import java.io.FileNotFoundException;
+import java.util.*;
+import java.util.concurrent.*;
+
+/**
+ * Created by jwalto on 01/07/2015.
+ */
+public class RoundRobinMT {
+    private final static Integer REPEATS = 1;
+    private final static Integer MAX_TICKS = 2000;
+
+    public static void main(String[] args) throws FileNotFoundException, InterruptedException, ExecutionException {
+
+        ExecutorService service = Executors.newFixedThreadPool(4);
+
+        String[] maps = {
+                "data/maps/level1.txt",
+                "data/maps/level2.txt",
+                "data/maps/level3.txt",
+                "data/maps/level4.txt",
+                "data/maps/level5.txt",
+                "data/maps/level6.txt",
+                "data/maps/level1E.txt"
+        };
+
+        Controller[] player1List = new Controller[]{
+                new MCTS(true, 500, 10, 45),
+                new MCTS(true, 75, 3, 15),
+                new MCTS(true, 200),
+                new VariGA(true, 500),
+                new GAController(true),
+                new RandomController()
+        };
+
+        Controller[] player2List = new Controller[] {
+                new MCTS(false, 500, 10, 45),
+                new MCTS(false, 75, 3, 15),
+                new MCTS(false, 200),
+                new VariGA(false, 500),
+                new GAController(true),
+                new RandomController()
+        };
+
+        while(!Thread.interrupted()) {
+            System.out.println("generating matchups");
+            List<Matchup> tasks = new ArrayList<>();
+            for (Controller p1 : player1List) {
+                for (Controller p2 : player2List) {
+                    for (String map : maps) {
+                        for (int trial = 0; trial < REPEATS; trial++) {
+                            tasks.add(new Matchup(p1, p2, map, trial));
+                        }
+                    }
+                }
+            }
+
+            System.out.println("calculating results (" + tasks.size() + " tasks)");
+            List<Future<Result>> results = service.invokeAll(tasks);
+
+            System.out.println("Processing results");
+            GenerateCSV csv = new GenerateCSV(System.getenv("COMPUTERNAME") + "-results-mtp.csv");
+            for (Future<Result> resultf : results) {
[…]

### 2015-10-14 src/main/java/FastGame/Test.java

@@ -1,0 +1,54 @@
+package FastGame;
+
+import Controllers.Controller;
+import Controllers.MCTS;
+import Controllers.RandomController;
+
+import java.util.ArrayList;
+import java.util.Arrays;
+
+/**
+ * Created by pwillic on 30/06/2015.
+ */
+public class Test {
+
+    public static void main(String[] args) {
+        //Controller m1 = new PlanningController();
+        Controller m2 = new MCTS(false, 500);
+        Controller r1 = new RandomController();
+
+
+        //Controller c1 = m1;
+//        Controller c1 = new RandomController();
+        //        Controller c2 = new MCTS(false);
+        Controller c2 = m2;
+
+
+
+        int gamesPerMatchup = 10;
+        //double[] results1 = runGames(m1, m2, gamesPerMatchup);
+        //System.out.println(Arrays.toString(results1));
+        //double[] results2 = runGames(m1, r1, gamesPerMatchup);
+        //System.out.println(Arrays.toString(results2));
+        double[] results3 = runGames(r1, r1, gamesPerMatchup);
+        System.out.println(Arrays.toString(results3));
+//        System.out.println(results2);
+//        System.out.println(results3);
+    }
+
+    public static double[] runGames(Controller c1, Controller c2, int gamesPerMatchup){
+        double[] results = new double[2];
+        for(int i = 0; i < gamesPerMatchup; i++) {
+            int ticksTaken = 0;
+            CoopGame game = new CoopGame("data/maps/level2.txt");
+            while (ticksTaken < 2000 && !game.hasWon()) {
+                game.update(c1.get(game.getClone()), c2.get(game.getClone()));
+                ticksTaken++;
+            }
+            results[0] += game.getScore();
+            results[1] += ticksTaken;
+            System.out.println("Game: " + i);
+        }
+        return results;
+    }
+}

### 2015-10-14 src/main/java/FastGame/Viewer.java

@@ -1,0 +1,73 @@
+package FastGame;
+
+import javax.swing.*;
+import java.awt.*;
+
+import static FastGame.GroundTypes.GROUND;
+import static FastGame.GroundTypes.WALL;
+import static FastGame.ObjectTypes.AGENT;
+import static FastGame.ObjectTypes.OBJECT_COLOURS;
+import static FastGame.ObjectTypes.TEXT_COLOURS;
+import static FastGame.ObjectTypes.DOOR;
+
+/**
+ * Created by pwillic on 25/06/2015.
+ */
+public class Viewer extends JComponent {
+
+    CoopGame game;
+
+    int gridSize = 50;
+
+    public Viewer(CoopGame game) {
+        this.game = game;
+    }
+
+    @Override
+    public void paint(Graphics g) {
+        for (int x = 0; x < game.getWidth(); x++) {
+            for (int y = 0; y < game.getHeight(); y++) {
+                int groundValue = game.get(x, y, 0);
+
+                switch (groundValue) {
+                    case GROUND:
+                        g.setColor(Color.LIGHT_GRAY);
+                        break;
+                    case WALL:
+                        g.setColor(Color.BLACK);
+                        break;
+                }
+                g.fillRect(x * gridSize, y * gridSize, gridSize, gridSize);
+                for (int layer = game.getLayers() - 1; layer >= 1; layer--) {
+                    int value = game.get(x, y, layer);
+                    if(value != 0) {
+                        int itemType = CoopGame.getItemTypeFromValue(value);
+                        if(itemType == DOOR && game.doorOpen(CoopGame.getIDFromValue(value))){
+                            continue;
+                        }
+
+                        g.setColor(OBJECT_COLOURS[itemType]);
+                        g.fillRect(x * gridSize, y * gridSize, gridSize, gridSize);
+
+                        g.setColor(TEXT_COLOURS[itemType]);
+                        g.drawString("" + CoopGame.getIDFromValue(value), x * gridSize + gridSize / 2, (y * gridSize) + gridSize / 2);
+                    }
+                }
+            }
+        }
+
+        // Draw the grid
+        g.setColor(Color.BLACK);
+        for (int x = 0; x < game.getWidth(); x++) {
+            for (int y = 0; y < game.getHeight(); y++) {
+                g.drawRect(x * gridSize, y * gridSize, gridSize, gridSize);
+            }
+        }
+        super.paint(g);
+    }
+
+    @Override
[…]

### 2015-10-14 src/main/java/gamesrc/Button.java

@@ -1,0 +1,36 @@
+package gamesrc;
+
+import java.awt.Graphics;
+
+import FastGame.ObjectTypes;
+
+public class Button extends GameObject {
+	private final Integer signal;
+	
+	public Button(int signal) {
+		this.signal = signal;
+	}
+
+	@Override
+	public void onContact(ObservableGameState state, int playerId) {
+		if (state.getSignalState(signal) >= 0) {
+			state.setSignalState(signal, true);
+		}
+	}
+
+	@Override
+	public void onContactEnd(ObservableGameState state, int pid) {
+		state.setSignalState(signal, false);
+	}
+
+	@Override
+	public int getSignal() {
+		return signal;
+	}
+
+	@Override
+	public int getType() {
+		return ObjectTypes.BUTTON;
+	}
+
+}

### 2015-10-14 src/main/java/gamesrc/ButtonTimed.java

@@ -1,0 +1,31 @@
+package gamesrc;
+
+
+import FastGame.ObjectTypes;
+
+/**
+ * Created by pwillic on 13/10/2015.
+ */
+public class ButtonTimed extends Button {
+    Integer index;
+
+    public ButtonTimed(Integer signal, Integer index) {
+        super(signal);
+        this.index = index;
+    }
+
+    @Override
+    public void onContact(ObservableGameState state, int playerId) {
+        state.activateTimedSignal(this.getSignal(), index);
+
+    }
+
+    @Override
+    public void onContactEnd(ObservableGameState state, int pid) {
+    }
+
+    @Override
+    public int getType() {
+        return ObjectTypes.TIMEDBUTTON;
+    }
+}

### 2015-10-14 src/main/java/gamesrc/GameLevel.java

@@ -1,0 +1,112 @@
+package gamesrc;
+
+import java.awt.Point;
+
+public class GameLevel {
+	private int width;
+	private int height;
+	private Point[] spawnLocations;
+	private int[] floors;
+	private GameObject[] objects;
+	private int goalCount = 0;
+	
+	public GameLevel(int width, int height) {
+		this.width = width;
+		this.height = height;
+		this.spawnLocations = new Point[2];
+		this.floors = new int[width*height];
+		this.objects = new GameObject[width*height];
+		this.goalCount = 0;
+	}
+
+	public boolean isWalkable(int pid, Point pos, SimpleGame state) {
+		if (pos.getX() < 0 || pos.getY() < 0 || pos.getX() >= width || pos.getY() >= height) {
+			return false;
+		}
+		
+		assert pos.getX() >= 0 && pos.getY() >= 0 : "player "+pos+" position is negative!";
+		assert pos.getX() < width && pos.getY() < height : "player "+pos+" position is too high!";
+		
+		GameObject object = state.getObject(pos.x, pos.y);
+		
+		return floors[pos.x * height + pos.y] == 0 && (object == null || object.isWalkable(state, pid));
+	}
+
+	public int getGoalCount() {
+		return goalCount;
+	}
+
+	/**
+	 * Get the number of players in this level
+	 * 
+	 * @return the numbers of players which have spawn locations in this level
+	 */
+	public int getPlayerCount() {
+		return spawnLocations.length;
+	}
+
+	/**
+	 * Marks a position as a starting point for the player
+	 * 
+	 * @param point the player's starting position
+	 * @param playerId the player's ID
+	 */
+	public void setSpawnPoint(Point point, int playerId) {
+		spawnLocations[playerId] = point;		
+	}
+
+
+	/**
+	 * A goal must be visited by agents in order to increase their score.
+	 * 
+	 * @param point the x,y position for the goal
+	 */
+	public void setGoal(Point point) {
+		setObject(point.x, point.y, new Goal(goalCount++));
+	}
+	
+	/**
+	 * Set the object data.
+	 * 
+	 * @param x x position of the object
+	 * @param y y position of the object
+	 * @param object the object to store
+	 */
+	protected void setObject(int x, int y, GameObject object){
+		assert objects[x * height + y] == null : "object already set!";
+		objects[x * height + y] = object;
+	}
+	
[…]

### 2015-10-14 src/main/java/gamesrc/GameObject.java

@@ -1,0 +1,28 @@
+package gamesrc;
+
+import static FastGame.ObjectTypes.OBJECT_COLOURS;
+import static FastGame.ObjectTypes.TEXT_COLOURS;
+
+import java.awt.Graphics;
+
+public abstract class GameObject {
+
+	public boolean isWalkable(ObservableGameState state, int playerId) {
+		return true;
+	}
+	
+	public abstract void onContact(ObservableGameState state, int playerId);
+
+	public void onContactEnd(ObservableGameState state, int pid) {}
+
+	public abstract int getSignal();
+	public abstract int getType();
+	
+	public void paint(int x, int y, int gridSize, ObservableGameState game, Graphics g) {
+		g.setColor(OBJECT_COLOURS[getType()]);
+        g.fillRect(x * gridSize, y * gridSize, gridSize, gridSize);
+    	
+    	g.setColor(TEXT_COLOURS[getType()]);
+        g.drawString("" + getSignal(), x * gridSize + gridSize / 2, (y * gridSize) + gridSize / 2);
+	}
+}

### 2015-10-14 src/main/java/gamesrc/GameState.java

@@ -1,0 +1,19 @@
+package gamesrc;
+
+import FastGame.Action;
+
+public interface GameState {
+	
+	public GameState getClone();
+	public double getScore();
+	public boolean hasWon();
+	public void update(Action p1, Action p2);
+	
+	
+	public Action[] getLegalActions(int playerID);
+	public int getActionLength();
+	
+	public int getWidth();
+	public int getHeight();
+
+}

### 2015-10-14 src/main/java/gamesrc/LevelParser.java

@@ -1,0 +1,83 @@
+package gamesrc;
+
+import java.awt.Point;
+import java.io.FileInputStream;
+import java.io.FileNotFoundException;
+import java.io.IOException;
+import java.util.Arrays;
+import java.util.Scanner;
+
+public class LevelParser {
+	
+	public static GameLevel buildParser(String filename) throws IOException {
+		Scanner scanner = new Scanner(new FileInputStream(filename));
+		
+		int width = scanner.nextInt();
+		int height = scanner.nextInt();
+		
+		GameLevel level = new GameLevel(width, height);
+		
+		for (int row=0; row<height; row++) {
+			for (int col=0; col<width; col++) {
+				int val = scanner.nextInt();
+				level.setFloor(col, row, val);
+			}
+		}
+		
+		boolean isObjects = false;
+		scanner.nextLine();
+		String objectStr = scanner.nextLine();
+		if ("BEGIN OBJECTS".equals(objectStr)) isObjects = true;
+		
+		while(isObjects) {
+			objectStr = scanner.nextLine().split("//")[0];
+			System.out.println("String: " + objectStr);
+			if ("END OBJECTS".equals(objectStr)) {
+				isObjects = true;
+				break;
+			}
+			
+			Scanner lineScanner = new Scanner(objectStr);
+			int length = objectStr.split(" ").length - 3;
+			int type = lineScanner.nextInt();
+			int x = lineScanner.nextInt();
+			int y = lineScanner.nextInt();
+			int[] extra = new int[length];
+			for(int i = 0; i < length; i++){
+				extra[i] = lineScanner.nextInt();
+			}
+
+			parseObject(level, type, x, y, extra);
+			lineScanner.close();
+		}
+		scanner.close();
+		
+		return level;
+	}
+	
+	public static void parseObject(GameLevel level, int type, int x, int y, int... extra) {
+		
+		switch(type) {
+			case 1:
+				level.setSpawnPoint(new Point(x,y), extra[0]);
+				break;
+			case 6:
+				level.setObject(x, y, new ButtonTimed(extra[0], extra[1]));
+				break;
+			case 4:
+				level.setGoal(new Point(x, y));
+				break;
+			case 2:
+				level.setObject(x, y, new Button(extra[0]));
+				break;
+			case 3:
+				level.setObject(x, y, new Door(extra[0]));
+				break;
+			case 5:
+				level.setObject(x, y, new TrapDoor(extra[0]));
+				break;
+		}
+		
+	}
+
+}

### 2015-10-14 src/main/java/gamesrc/ObservableGameState.java

@@ -1,0 +1,22 @@
+package gamesrc;
+
+import java.awt.Point;
+
+public interface ObservableGameState extends GameState {
+	
+	public boolean isSignalHigh(int signal);
+	public boolean hasVisited(int agent, int goalID);
+	public GameObject getObject(int x, int y);
+	public Point getPos(int i);
+	public int getFloor(int x, int y);
+	public int getSignalState(int signal);
+	public int getGoalsCount();
+	
+	public boolean getBeep(int agent);
+	public Point getFlare(int agent);
+
+	public void setVisited(int agent, int goalID);
+	public void setSignalState(int signal, boolean state);
+	public void activateTimedSignal(int signal, int index);
+
+}

### 2015-10-14 src/main/java/gamesrc/ReadableGame.java

@@ -1,0 +1,136 @@
+package gamesrc;
+
+import Controllers.ArrowController;
+import Controllers.Controller;
+import Controllers.WASDController;
+import FastGame.Action;
+
+import javax.swing.*;
+import java.awt.*;
+import java.awt.event.KeyListener;
+import java.io.IOException;
+import java.util.ArrayList;
+import java.util.List;
+
+public class ReadableGame {
+
+    public static void main(String[] args) throws IOException, InterruptedException {
+        String[] levels = new String[]{
+                "maps/level9.txt",
+                "maps/level8.txt",
+                "maps/level1.txt",
+                "maps/level2.txt",
+                "maps/level3.txt",
+                "maps/level4.txt",
+                "maps/level5.txt",
+                "maps/level6.txt",
+                "maps/level7.txt"
+        };
+
+        GameLevel[] levelList = new GameLevel[levels.length];
+        for (int i = 0; i < levelList.length; i++) {
+            levelList[i] = buildLevel(levels[i]);
+        }
+
+        System.out.println("graphical game");
+        JFrame frame = new JFrame("TinyCoop - GRIDWORLD");
+        frame.setPreferredSize(new Dimension(800, 600));
+        frame.setDefaultCloseOperation(JFrame.EXIT_ON_CLOSE);
+
+        Viewer viewer = new Viewer(null);
+        viewer.setFocusable(true);
+        frame.add(viewer);
+
+        frame.pack();
+        frame.setVisible(true);
+
+		/*List<Controller> controllers = Arrays.asList(
+				new MCTS(true, 500),
+				new MCTS(true, 250),
+				new RandomController(),
+				new WASDController()
+				);*/
+
+        Controller c1 = new WASDController();
+        for (GameLevel level : levelList) {
+            GameState initalStateS = new SimpleGame(level);
+
+            //for (Controller c1 : controllers) {
+            Controller c2 = new ArrowController();
+
+            frame.setTitle("TinyCoop " + c1.getSimpleName() + " and " + c2.getSimpleName());
+
+            runGraphicalGame(initalStateS, viewer, c1, c2);
+            //}
+        }
+    }
+
+    public static void runGraphicalGame(GameState initial, Viewer viewer, Controller p1, Controller p2) throws InterruptedException {
+
+        ObservableGameState state = (ObservableGameState) initial.getClone();
+
+        viewer.setState(state);
+
+        viewer.setFocusable(true);
+        if (p1 instanceof KeyListener) {
+            viewer.setFocusable(true);
[…]

### 2015-10-14 src/main/java/gamesrc/SimpleGame.java

@@ -1,0 +1,236 @@
+package gamesrc;
+
+import FastGame.Action;
+
+import java.awt.*;
+import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.Map;
+import java.util.TreeMap;
+
+/**
+ * TinyCoop implementation designed for planners.
+ * <p>
+ * This implementation puts readablity of the code and exensiablity over speed.
+ * It is likely to be much slower than the FastGame implementation so use that
+ * one if you want speed.
+ */
+public class SimpleGame implements ObservableGameState {
+    private GameLevel level;
+    private boolean[] beeps;
+    private Point[] flares;
+    private Point[] positions;
+    private boolean[] visitList;
+    private Map<Integer, Integer> signals;
+    private Map<Integer, ArrayList<Integer>> timers;
+
+    public SimpleGame(GameLevel level) {
+        this.level = level;
+        this.beeps = new boolean[level.getPlayerCount()];
+        this.flares = new Point[level.getPlayerCount()];
+        this.positions = new Point[level.getPlayerCount()];
+        this.visitList = new boolean[level.getGoalCount() * level.getPlayerCount()];
+        this.signals = new TreeMap<Integer, Integer>();
+        this.timers = new TreeMap<>();
+
+        for (int i = 0; i < positions.length; i++) {
+            positions[i] = level.getSpawnLocation(i);
+        }
+    }
+
+    public SimpleGame(SimpleGame game) {
+        this.level = game.level;
+        this.beeps = Arrays.copyOf(game.beeps, game.beeps.length);
+        this.flares = Arrays.copyOf(game.flares, game.flares.length);
+        this.positions = Arrays.copyOf(game.positions, game.positions.length);
+        this.visitList = Arrays.copyOf(game.visitList, game.visitList.length);
+        this.signals = new TreeMap<Integer, Integer>(game.signals);
+        this.timers = new TreeMap<>(game.timers);
+    }
+
+    @Override
+    public GameState getClone() {
+        return new SimpleGame(this);
+    }
+
+    @Override
+    public double getScore() {
+        double score = 0;
+        for (boolean goal : visitList) {
+            if (goal) {
+                score += 1;
+            }
+        }
+
+        return score / visitList.length;
+    }
+
+    @Override
+    public boolean hasWon() {
+        for (boolean b : visitList) {
+            if (!b) {
+                return false;
+            }
+        }
+        return true;
+    }
+
+    @Override
[…]

### 2015-10-14 src/main/java/gamesrc/TrapDoor.java

@@ -1,0 +1,54 @@
+package gamesrc;
+
+import static FastGame.ObjectTypes.OBJECT_COLOURS;
+import static FastGame.ObjectTypes.TEXT_COLOURS;
+
+import java.awt.Graphics;
+
+import FastGame.ObjectTypes;
+
+/**
+ * Trap door object.
+ * 
+ * Once someone walks though the trap door object, the door will subtract 1 from the signal
+ * state (disabling it).
+ */
+public class TrapDoor extends GameObject {
+	private final Integer signal;
+	
+	public TrapDoor(int signal) {
+		this.signal = signal;
+	}
+
+	@Override
+	public boolean isWalkable(ObservableGameState state, int playerId) {
+		return state.isSignalHigh(signal);
+	}
+	
+	@Override
+	public void onContact(ObservableGameState state, int playerId) {
+		state.setSignalState(signal, false);
+	}
+
+	@Override
+	public int getSignal() {
+		return signal;
+	}
+
+	@Override
+	public int getType() {
+		return ObjectTypes.DOOR;
+	}
+	
+	public void paint(int x, int y, int gridSize, ObservableGameState game, Graphics g) {
+		g.setColor(OBJECT_COLOURS[getType()]);
+    	if (game.isSignalHigh(getSignal())) {
+            g.drawRect(x * gridSize, y * gridSize, gridSize, gridSize);
+    	} else{
+            g.fillRect(x * gridSize, y * gridSize, gridSize, gridSize);
+    	}
+    	
+    	g.setColor(TEXT_COLOURS[getType()]);
+        g.drawString("" + getSignal(), x * gridSize + gridSize / 2, (y * gridSize) + gridSize / 2);
+	}
+}

### 2015-10-14 src/main/java/gamesrc/Viewer.java

@@ -1,0 +1,112 @@
+package gamesrc;
+
+import javax.swing.*;
+import java.awt.*;
+
+import static FastGame.GroundTypes.GROUND;
+import static FastGame.GroundTypes.WALL;
+import static FastGame.ObjectTypes.AGENT;
+import static FastGame.ObjectTypes.OBJECT_COLOURS;
+import static FastGame.ObjectTypes.TEXT_COLOURS;
+import static FastGame.ObjectTypes.DOOR;
+
+/**
+ * Created by pwillic on 25/06/2015.
+ */
+public class Viewer extends JComponent {
+
+    private ObservableGameState game;
+    private final Integer gridSize = 50;
+
+    public Viewer(ObservableGameState game) {
+        this.game = game;
+    }
+
+    public void setState(ObservableGameState game) {
+    	this.game = game;
+    }
+    
+    @Override
+    public void paintComponent(Graphics g) {
+        super.paintComponent(g);
+        
+        if (game == null) {
+        	return;
+        }
+    	
+        for (int x = 0; x < game.getWidth(); x++) {
+            for (int y = 0; y < game.getHeight(); y++) {
+                int groundValue = game.getFloor(x, y);
+
+                switch (groundValue) {
+                    case GROUND:
+                        g.setColor(Color.LIGHT_GRAY);
+                        break;
+                    case WALL:
+                        g.setColor(Color.BLACK);
+                        break;
+                }
+                g.fillRect(x * gridSize, y * gridSize, gridSize, gridSize);
+                
+                GameObject object = game.getObject(x, y);
+                if (object != null) {
+                	object.paint(x, y, gridSize, game, g);
+                }
+            }
+        }
+        
+        for (int i=0; i<2; i++) {
+        	Point p = game.getPos(i);
+        	g.setColor(Color.WHITE);
+        	g.fillOval(p.x * gridSize, p.y * gridSize, gridSize, gridSize);
+        	g.setColor(Color.BLACK);
+        	g.drawString("" + i, p.x * gridSize + gridSize / 2, (p.y * gridSize) + gridSize / 2);
+        }
+
+        // Draw the grid
+        g.setColor(Color.BLACK);
+        for (int x = 0; x < game.getWidth(); x++) {
+            for (int y = 0; y < game.getHeight(); y++) {
[…]

### 2015-10-14 src/test/java/FastGame/ActionTest.java

@@ -1,0 +1,31 @@
+package FastGame;
+
+import static org.junit.Assert.*;
+
+import org.junit.After;
+import org.junit.Before;
+import org.junit.Test;
+
+public class ActionTest {
+
+	@Before
+	public void setUp() throws Exception {
+	}
+
+	@After
+	public void tearDown() throws Exception {
+	}
+	
+	@Test
+	public void testNoOpEquals() {
+		int x = 0;
+		int y = 0;
+		
+		Action action = new Action(x, y);
+		
+		assertEquals(x, action.getX());
+		assertEquals(y, action.getY());
+	}
+
+	
+}

### 2015-10-27 report/ceec.tex
Report

--- 2015-10-12 Report/ceec.tex
@@
 
-\author{Piers R. Williams, \and Joseph Walton-Rivers}
+\author{Piers R. Williams,  Joseph Walton-Rivers, Diego Perez-Liebana, Simon M. Lucas}
 
-\title{Monte Carlo Tree Search Applied to Co-operative Problems}
+\title{Monte Carlo Tree Search\\ Applied to Co-operative Problems \thanks{All authors are with the School of Computer Science and Electronic Engineering, University of Essex, Colchester CO4 3SQ, UK; email: {\tt \{pwillic,jwalto,dperez,sml\}@essex.ac.uk}).} }
 
@@
 \usepackage{float}
-\captionsetup{belowskip=8pt,aboveskip=4pt}
+\captionsetup{belowskip=12pt,aboveskip=4pt}
 \graphicspath{{stats-processing/}{stats-processing/data/maps/}}
@@
 These problems are formed from a simple grid world that has a set of goals, doors and buttons as well as walls that cannot be walked through.
-Two agents have to each reach every goal present on the map.
-For a door to be open, an Agent must be present on at least one of the buttons that is linked to it.
-
+Two agents have to reach every goal present on the map.
+For a door to be open, an agent must be present on at least one of the buttons that is linked to it.
 When laid out correctly, the world requires each agent to do certain things at certain times in order to achieve the goal.
-With no modification to allow communication between the two Agents - Monte Carlo Tress Search performs well and performs very 'purposefully' when given enough computational time.
+With no modification to allow communication between the two agents, Monte Carlo Tress Search performs well and very ``purposefully'' when given enough computational time.
 \end{abstract}
@@
 \section{Introduction}
-This research problem assessed in this paper is how \gls{ggp} agents perform when trying to solve a simple co-operative problem without co-operative abilities, with a focus on \gls{mcts}.
-
+The research problem studied in this paper consists of how \gls{ggp} agents perform when trying to solve a simple co-operative problem without co-operative abilities, with a focus on \gls{mcts}.
 \gls{ggp} is the field of writing \gls{ai} agents that can play a multitude of games without being written specifically for each one individually \cite{genesereth2005general}.
@@
 Where \gls{fps} games typically excel at co-operation is in online modes that enable teams of humans to play against each other.
-Some games even provide squad structures and communication allowing direct command for the purpose of better co-ordination as in Battlefield 2142 \cite{battlefield2142}.
+Some games even provide squad structures and communication allowing direct command for the purpose of better co-ordination as in \textit{Battlefield 2142} (EA Digital Illusions CE, 2006).
 \gls{rts} games also often have a small number of features designed to facilitate communication in a bid to facilitate co-operation.
-Two games that stand out for co-operation are Microsoft's Rise of Nations \cite{riseofnations} and Mad Doc Software's Empire Earth 2 \cite{empireEarth2}.
+Two games that stand out for co-operation are \textit{Rise of Nations} (Big Huge Games, 2003) and \textit{Empire Earth II} (Mad Doc Software, 2005).
 Rise of Nations allowed a human and \gls{ai} player to operate the same set of units and buildings, though no communication was possible at all.
@@
 
-A highly popular game that had an entire mode designed for co-operation between humans was Valve's Portal 2 \cite{portal2}.
+A highly popular game that had an entire mode designed for co-operation between humans was \textit{Portal 2} (Valve, 2011).
 This featured human sized lab test mazes with elements that required players to work together by activating buttons, moving cubes and using intra-dimensional portals to get to the end goal.
@@
 
-\subsection{MCTS}
+\subsection{Monte Carlo Tree Search}
 
-\gls{mcts} is a tree search algorithm originally designed by R{\'e}mi Coulom \cite{coulom2007efficient} and the major modification of \gls{uct} was defined by Kocsis and Szepesv{\'a}ri \cite{kocsis2006bandit} and improved by Kocsis et al \cite{kocsis2006improved}.
-
-\gls{mcts} is a tree search algorithm that in games is typically applied directly to the action space.
-\gls{mcts} requires the ability to simulate action sequences and retrieve at least some form of reward (or lack of) from the results of these simulations.
+\gls{mcts} is a Tree Search algorithm originally proposed in 2006~\cite{coulom2007efficient, kocsis2006bandit, kocsis2006improved}.
+\gls{mcts} operates in the action space, building an asymmetric tree in memory that biases the search towards the most promising parts of the search space.
+\gls{mcts} estimates the theoretic value of the visited states by performing self-play from the state in the node, to the end of the game.
 The basic steps for \gls{mcts} are:
@@
 \begin{enumerate}
-\item{\emph{Selection} - Selection is the stage where the algorithm navigates the search tree, selecting optimal nodes(Based on the tree policy) until it reaches a leaf node.}
-\item{\emph{Expansion} - Expansion is the stage whereby the leaf node is expanded by adding one of the remaining child states if it is not a terminal node.}
+\item{\emph{Selection} - Selection is the stage where the algorithm navigates the search tree, selecting optimal nodes (based on the Tree Policy) until it reaches a leaf node.}
+\item{\emph{Expansion} - Expansion is the stage whereby the leaf node is expanded by adding one of the remaining child states if it is not a terminal node (game end state).}
 \item{\emph{Simulation} - Simulation is the stage where the algorithm forwards the model until a result is achieved.
@@
 Each \emph{Agent} is able to make a single action in each game tick.
-The actions are polled from each \emph{Agent} that is given the state of the game.
-When every \emph{Agent} has returned an action, the game is updated with these actions.
-The actions are implemented sequentially, if two \emph{Agents} return actions that result in occupying the same space, the \emph{Agent} with the lowest ID number will succeed while the other \emph{Agent} will fail and execute a \emph{No-Op}.
+Each agent, after receiving the state of the game, must return a valid action.
+Once all \emph{Agents} have returned an action, the game is updated with these moves.
+
+The actions are implemented sequentially: if two \emph{Agents} return actions that result in occupying the same space, the \emph{Agent} with the lowest ID number will succeed while the other \emph{Agent} will fail and execute a \emph{No-Op}.
 The available 5 actions are:
@@
 We feel that this creates a very interesting problem domain, due to placing each \emph{Agent} that is typically designed to solve problems by themselves in an environment where they must rely on another \emph{Agent} performing certain sequences of actions without being able to communicate that sequence or anything else.
+
 \begin{comment}
@@
 
-This changed, when an agent (Agent 1 say) got near a \emph{Button} or \emph{Door}.
+This changed, when an agent (say Agent 1 say) got near a \emph{Button} or \emph{Door}.
 When Agent 1 reached an item like this - Agent 2 would seemingly gain some purpose and typically head for the other items.
@@
 \end{comment}
+
 \subsection{Tournament}
-For the main data collection, we ran a round robin tournament of maps and Agents. Each Agent was paired with all 7 Agents (including a copy of itself) and played 47 games on each of the 7 maps.
+For the main data collection, we ran a round robin tournament of maps and Agents. Each Agent was paired with all $7$ Agents (including a copy of itself) and played $47$ games on each of the $7$ maps.
 
 \subsubsection{Maps}
-The 7 maps that were included in the tournament were as follows:
+The $7$ maps that were included in the tournament were as follows:
 
-\paragraph{\emph{SingleDoor}} This map is a basic map with two rooms, single door and a button either side.
-\begin{figure}[H]
+\paragraph{\emph{SingleDoor}} This map, depicted in Figure~\ref{SingleDoor}, is a basic map with two rooms, a single door and a button on either side.
+
+\begin{figure}[!t]
 \centering
 \includegraphics[scale=0.35]{InitialState}
-\caption{Single Door \protect\footnotemark}
+\caption{Map \textit{Single Door} \protect\footnotemark}
 \label{SingleDoor}
@@
 \footnotetext{Displayed numbers are the ID numbers - \emph{Button} ID 0 will open \emph{Door} ID 0 but not \emph{Door} ID 1}
-\paragraph{\emph{Pathfinding}} This map is the same as \emph{SingleDoor} but without the \emph{Doors} and \emph{Buttons}. This was to test the \emph{Agent's} ability to solve the simplest problem.
-\begin{figure}[H]
+
+\paragraph{\emph{Pathfinding}} This map, depicted in Figure~\ref{Pathfinding}, is the same as \emph{SingleDoor} but without the \emph{Doors} and \emph{Buttons}.
+This has the aim of testing the \emph{Agent's} ability to solve the simplest problem.
+\begin{figure}[!t]
 \centering
 \includegraphics[scale=0.35]{level1e}
-\caption{Pathfinding}
+\caption{Map \textit{Pathfinding}}
 \label{Pathfinding}
 \end{figure}
-\paragraph{\emph{SymmetricSingleDoor}} This map was a modification of the \emph{SingleDoor} - making the map more symmetric and the action parts closer together.
-\begin{figure}[H]
+
+\paragraph{\emph{SymmetricSingleDoor}} This map, shown in Figure~\ref{SymmetricSingleDoor}, is a modification of the \emph{SingleDoor} - making the map more symmetric and the action parts closer together.
+\begin{figure}[!t]
 \centering
 \includegraphics[scale=0.35]{level2}
-\caption{Symmetric Single Door}
+\caption{Map \textit{Symmetric Single Door}}
 \label{SymmetricSingleDoor}
 \end{figure}
-\paragraph{\emph{ExtendedSide}} This map was an extension of \emph{SingleDoor} with a second \emph{Goal} and some extra walls in the game.
-Spreading the action parts away from the door and buttons was the main purpose of this one.
-\begin{figure}[H]
+
+\paragraph{\emph{ExtendedSide}} This map, shown in Figure~\ref{ExtendedSide}, is an extension of \emph{SingleDoor} with a second \emph{Goal} and some extra walls in the game.
+Spreading the action parts away from the door and buttons is the design after this one.
+\begin{figure}[!t]
 \centering
 \includegraphics[scale=0.35]{level3}
-\caption{Extended Side}
+\caption{Map \textit{Extended Side}}
 \label{ExtendedSide}
 \end{figure}
-\paragraph{\emph{SideBySide}} This map was a modification of \emph{SingleDoor} - putting a second \emph{Goal} in and making the map partly mirrored.
-Each \emph{Agent} began in a separate room to each other instead of together.
-\begin{figure}[H]
+
+\paragraph{\emph{SideBySide}} This map, illustrated in Figure~\ref{SideBySide}, is a modification of \emph{SingleDoor}, including a second \emph{Goal} and making the map partly mirrored.
+Each \emph{Agent} begins in a separate room to each other instead of together.
+\begin{figure}[!t]
 \centering
 \includegraphics[scale=0.35]{level4}
-\caption{Side By Side}
+\caption{Map \textit{Side By Side}}
 \label{SideBySide}
 \end{figure}
-\paragraph{\emph{Airlock}} This map was a new map, designed to give wildly different roles to each AI - the top Agent would have to travel through two doors (Like an airlock) that the bottom agent had access to the linked \emph{Buttons}.
+
+\paragraph{\emph{Airlock}} This map (see Figure~\ref{Airlock}) is designed to give wildly different roles to each AI: the top Agent would have to travel through two doors (like an airlock) that the bottom agent had access to the linked \emph{Buttons}.
 Then the top \emph{Agent} could collect the reward and allow the bottom \emph{Agent} access to the \emph{Goal}.
-\begin{figure}[H]
+\begin{figure}[!t]
 \centering
 \includegraphics[scale=0.35]{level5}
-\caption{Airlock}
+\caption{Map \textit{Airlock}}
 \label{Airlock}
 \end{figure}
-\paragraph{\emph{Butterfly}} This map was a new map - with two rooms each with a \emph{Goal} and a door.
+
+\paragraph{\emph{Butterfly}} This map (see Figure~\ref{Butterfly}) is a map with two rooms each, with a \emph{Goal} and a door.
 This was designed to force each \emph{Agent} to be let into the \emph{Goal} room, and out of it again.
-\begin{figure}[H]
+
+\begin{figure}[!t]
 \centering
 \includegraphics[scale=0.35]{level6}
-\caption{Butterfly}
+\caption{Map \textit{Butterfly}}
 \label{Butterfly}
@@
 A set of \gls{ai} Controllers were created in order to attempt to solve the problem domain.
-None of the agents have the ability to communicate with another agent and each agent has a single controller.
+None of the agents have the ability to communicate with another agent and each agent is managed by a single controller.
+
 \paragraph{Random}
-The random controller simply chooses one of the possible 5 actions. This is one of the simplest to implement and run.
+The random controller simply chooses one of the possible $5$ actions. This is one of the simplest to implement and run.
+
 \begin{comment}
@@
 \end{comment}
+
 \paragraph{\gls{mcts}}
-The \gls{mcts} controller is a simple implementation of \gls{uct} - with a fixed number of rollouts, \gls{uct} tree search depth limit and rollout border.
-The rollout border is how far in total, the forward model will be allowed to progress before the game is evaluated.
+The \gls{mcts} controller is a simple implementation of \gls{uct}, with a fixed number of rollouts, \gls{uct} tree search depth limit and rollout border.
+The rollout border is how far in total the forward model will be allowed to progress before the game state is evaluated.
 No knowledge about the game is provided and the assumption is made that the other player will play randomly.
-The fixed rollout border makes a significant improvement in iterations per decision (from 1-3 to 500-600 in 40ms \footnote{Intel Core i5-3570, 8GB RAM, Windows 7 Enterprise 64bit}).
+The fixed rollout border makes a significant improvement in iterations per decision (from $1$-$3$ to $500$-$600$ in $40$ms \footnote{Intel Core i5-3570, 8GB RAM, Windows 7 Enterprise 64bit}).
 This greatly improves the ability of \gls{mcts} to make informed decisions.
 The score at the end of a rollout is taken from the game state - so if \gls{mcts} does not see any player reach a goal, all branches will be equal.
-
 For the tournament, three parameter sets were chosen for comparison and are shown in Table \ref{mctsTable}.
@@
 
-\paragraph{Macro Action Genetic Algorithm}
+\paragraph{Macro Action Genetic Algorithm (GAController)}
 The \gls{ga} algorithm was selected for its simplicity and had Macro Actions added in order to improve the forward search capability as well as the amount of computation time per decision available to it.
-The \gls{maga} used a population size of 10 and tournament selection of 3.
-Each candidate was a string of 15 actions - with each action performed 3 times in a row.
-This meant the \gls{maga} could "see" 45 ticks in the future.
-The design of the \gls{maga} algorithm was inspired by \textit{Perez et al} \cite{perez2013rolling}
-\paragraph{Variable Macro Action Genetic Algorithm}
+The \gls{maga} used a population size of $10$ and tournament selection of $3$.
+Each candidate was a string of $15$ actions - with each action performed $3$ times in a row.
+This meant the \gls{maga} could "see" $45$ ticks in the future.
+The design of the \gls{maga} algorithm was inspired by \textit{Perez et al} \cite{perez2013rolling}.
+
+\paragraph{Variable Macro Action Genetic Algorithm (VarGA)}
 The Variable Macro Action \gls{ga} was created to try to solve the shortcomings of \gls{maga}.
 The primary premise was to allow the \gls{ga} to evolve the individual macro action lengths and the length of the overall sequence (number of macro actions).
-The main technique used was a 1 + 1 Evolutionary Strategy \cite{t.back2000evolutionary-co}.
-A 1 + 1 ES is a very simple \gls{ga} that maintains a single candidate, and in each iteration a mutation is made and if it is an improvement it is saved as the new best candidate.
-It is discarded if it is not an improvement.
-ES's are often much simpler than full \gls{ga} algorithms to create, often require much less memory and due to performing less within each iteration is able to use more of the available time budget than a full \gls{ga}.
-The algorithm was bounded by a number of parameters that are shown in Table \ref{vmagaTable}.
+The main technique used was a $1 + 1$ Evolutionary Strategy (ES) \cite{t.back2000evolutionary-co}.
+A $1 + 1$ ES is a very simple \gls{ga} that maintains a single candidate.
+On each iteration, the mutation operator is applied to this individual, and it is saved as the new best candidate in case of an improvement in fitness (and discarded otherwise).
+This kind of ES is much simpler than a full \gls{ga}, requires much less memory and due to a small computational cost within each iteration, is able to use more of the available time budget.
+
+The algorithm was bounded by a number of parameters (shown in Table \ref{vmagaTable}), and a further tuning of these is a source of possible future work in order to explore the potential of this algorithm.
+
 \begin{table}[!t]
@@
 \end{table}
-These values need extensive tuning to realise the full potential of the algorithm and is a source of possible future work.
+
 \section{Results}
 
-\begin{figure}[!ht]
+\begin{figure}[!t]
 \centering
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!t]
 \centering
@@
 The \gls{mcts} and \gls{ai} algorithms are required to run simulations of the game state in order to function.
-Even just a single look ahead of this problem domain requires the algorithm to make a selection of what the other play would do.
+Even just a single look ahead of this problem domain requires the algorithm to make a selection of what the other player would do.
 In all cases, the assumption of a random strategy was chosen due to the availability only of agents that could play generally.
@@
 This gives \gls{mcts} the ability to make moves that it believes would help a worst case scenario player - something that in this problem domain is likely to also help a more intelligent player.
-When \gls{mcts} is sitting on the button, an intelligent player would go through the open door and a random player would eventually go through the door.
+When \gls{mcts} is sitting on the button, an intelligent player would go through the open door and a random player would eventually go through it.
 \gls{mcts} even has the option of locking the random player on the other side, forcing it to eventually complete some other task.
@@
 \gls{mcts} performed very well in this problem domain.
-
 As seen above, in Figure \ref{avgTicksPairAllMaps}, the medium and high budget implementations provided the two quickest completion times across all maps.
-The differences shown were significant as well as being the only two agents to complete on average in under 1000 ticks.
+The differences shown were significant as well as being the only two agents to complete on average in under $1000$ ticks.
 Figure \ref{avgScorePairAllMaps} showed that the medium and high budget implementations scored significantly better than all other agents.
@@
 Statistically,  in certain situations \gls{mcts} would only see rewards in the tree when it was situated on a \emph{Button}.
-This tended to cause the \gls{mcts} to travle towards \emph{Buttons}, increasing the likelihood that its own simulations would cause it to be situated on the button.
+This tended to cause the \gls{mcts} to travel towards \emph{Buttons}, increasing the possibility that its own simulations would cause it to be situated on the button.
 Eventually, most other \gls{ai} \emph{Agents} would cross through the open door.
+
 \subsection{GA}
 The two \gls{ga} algorithms did not perform very well in this problem domain.
-
 As seen in Figure \ref{avgScorePairAllMaps} and Figure \ref{avgTicksPairAllMaps}, when tasked with solving the problem domain with another identical agent, neither the \emph{GAController} or \emph{VariGA} performed well at all.
@@
 \subsection{Random}
-The \emph{RandomController} performed poorly in this problem domain. On average, the \emph{RandomController} finished under the 2000 tick limit and scored less than half the maximum on average.
+The \emph{RandomController} performed poorly in this problem domain. On average, the \emph{RandomController} finished under the $2000$ tick limit and scored less than half the maximum on average.
 
@@
 A* search was considered to be unsuitable for this domain, as searching across the action space of two \emph{Agents} was far too high a branching factor.
+
 \section{Conclusions}
@@
 We also found that a number of other \gls{ai} techniques experienced difficulty when the problem became cooperative.
-We hypothesised that \gls{mcts}'s use of a stored tree guiding its explorations (Something that \gls{ga}'s lack) was a major advantage in solving problems that rely on the other agent.
-\gls{ga}'s were found to perform poorly in the experiment, despite being capable of goal finding without the co-operative obstacles.
+We hypothesised that \gls{mcts}'s use of a stored tree guiding its explorations (something that genetic algorithms lack) was a major advantage in solving problems that rely on the other agent.
+Genetic algorithms were found to perform poorly in the experiment, despite being capable of finding the goal without the co-operative obstacles.
 Further work is required in this area to determine exactly why \gls{mcts} performs well.
@@
 The \emph{High MCTS} performed well - showing the power of having the correct parameters compared to the \emph{Low MCTS}.
-The \emph{VariGA} has 7 parameters that we simply did not have time to correctly optimise for this experiment.
+The \emph{VariGA} has $7$ parameters, and it is possible that by fine tuning their values, a higher performance could be found.
 
@@
 More work can also be done on experimenting with the problem domain itself.
-Expanding the object types to include different techniques such as pickup-able objects that can be placed on \emph{Buttons}, \emph{Buttons} that remain active for a period of time after vacating them as well as potentially \emph{Doors} that will open permanently if all it's \emph{Buttons} are activated.
-The scope here is fairly limitless.
+Expanding the object types to include different techniques such as pickup-able objects that can be placed on \emph{Buttons}, \emph{Buttons} that remain active for a period of time after vacating them, as well as \emph{Doors} that will be open permanently if all (or a subset of) \emph{Buttons} are activated.
+The achievable scope modifying the problem domain is fairly limitless.
 
